### 2013-10-10 documents/plm.tex
start the paper

\documentclass[12pt, preprint]{aastex}

\newcommand{\Kepler}{\textsl{Kepler}}
\newcommand{\name}{PLM}

\begin{document}

\begin{abstract}
The precision of \Kepler\ photometry%
  ---the most precise photometric measurements of stars ever made---%
  appears to be limited by unknown or untracked variations
  in spacecraft pointing, point-spread function, stellar motions and parallaxes, and temperature.
Here we present \name,
  a data-driven model of these variations in \Kepler\ data (or really of their impact on the photometry).
Importantly (and uniquely),
  \name\ works at the pixel level (not the photometric measurement level);
  it can capture more fine-grained information about the variation of the spacecraft than is available in the photometry.
\name\ is extreme in that it has enormous flexibility and it only uses data (and meta-data) to model data:
\name\ provides a prediction for each readout pixel built from a linear combination of the readouts
  from very large numbers of nearby pixels (plus some spacecraft information);
  the choice of nearby pixels is guided by ideas from causal inference.
\name\ avoids over-fitting by employing a train-and-test formalism
  designed to ensure that transit-like photometric events and short-timescale stellar variability
  cannot be captured or distorted by the model;
  it is designed to remove spacecraft-induced variability but not intrinsic stellar variability.
We show that \name\ outperforms the \Kepler\ Presearch Data Conditioning method on a set of example stars.
We release open-source code that provides \name\ output for any star in the existing \Kepler\ Archive,
  and we discuss applications for other missions,
  including any possible \Kepler\ two-wheel mission.
\end{abstract}

The photometric measurements of stars made by the \Kepler\ Satellite are precise enough
  to permit discovery of exoplanet transits with depths smaller than $10^{-4}$.
This precision results from great spacecraft stability,
  supplemented by various methods for removing small residual spacecraft-induced and stellar-variability trends in the brightnesses,
  either filtering the data (with things like median filters; CITE)
  or fitting the data with flexible models (like polynomials or splines or Gaussian Processes; CITE).
When employed in the service of exoplanet search and characterization,
  these methods are usually agnostic about whether photometric variations originate in the spacecraft or in the star itself;
  that is, they obliterate intrinsic stellar variability along with spacecraft issues.

One method that is designed to model spacecraft-induced problems
  but \emph{not} interfere with measurements of stellar variability
  is the \Kepler\ Presearch Data Conditioning (PDC) method (CITE).
The PDC ``de-trends’’ the \Kepler\ lightcurves by fitting them with a small set of basis lightcurves
  generated from a principal components analysis (PCA) of filtered lightcurves.
That is, it uses data to model data,
  regularizing the fit (and avoiding over-fitting) by filtering and restricting the dimensionality (through PCA).
The method proposed here, \name, is similar in spirit to the PDC.
The main differences are
  (1)~that it works in the pixel domain, not the lightcurve domain, so it has access to more fine-grained information,
  (2)~that it has far more freedom (far more parameters)
  but it strictly avoids over-fitting the lightcurves on exoplanet-transit time-scales through a train-and-test framework, and
  (3)~that when it fits a star, there is no possibility of any contribution of the star itself to the fit basis vectors.

\end{document}

### 2013-10-11 documents/plm.tex
authors and affils

@@
+% This file is part of the causal-kepler project
+% Copyright 2013 the authors.
+
 \documentclass[12pt, preprint]{aastex}
 
-\newcommand{\Kepler}{\textsl{Kepler}}
-\newcommand{\name}{PLM}
+\newcommand{\notenglish}[1]{\textit{#1}}
+\newcommand{\sic}{\notenglish{sic}}
+\newcommand{\project}[1]{\textsl{#1}}
+\newcommand{\Kepler}{\project{Kepler}}
+\newcommand{\name}{KPLM}
 
 \begin{document}
+
+\title{%
+  A data-driven, pixel-level model to improve the precision of \Kepler\ photometry%
+}
+\author{%
+  Dan~Foreman-Mackey\altaffilmark{\ref{CCPP}},
+  David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{MPIA},\ref{email}},
+  Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}},
+  others%
+}
+
+\newcounter{address}
+\setcounter{address}{1}
+\altaffiltext{\theaddress}{\stepcounter{address}\label{CCPP}%
+  Center for Cosmology and Particle Physics, Department of Physics, New York University}
+\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIA}%
+  Max-Planck-Institut f\"ur Astronomie, Heidelberg, Germany}
+\altaffiltext{\theaddress}{\stepcounter{address}\label{email}%
+  To whom correspondence should be addressed; \texttt{<david.hogg@nyu.edu>}.}
+\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIIS}%
+  Max-Planck-Institut f\"ur Intelligente Systeme, T\"ubingen}
+%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Oxford}%
+%%   Department of Physics, Oxford University}
+%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Ames}%
+%%   NASA Ames Research Center}
+%% \altaffiltext{\theaddress}{\stepcounter{address}\label{CfA}%
+%%   Harvard--Smithsonian Center for Astrophysics}
+%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Courant}%
+%%   Courant Institute of Mathematical Sciences, New York University}
+%% \altaffiltext{\theaddress}{\stepcounter{address}\label{UCL}%
+%%   Department of Physics and Astronomy, University College London}
+%% \altaffiltext{\theaddress}{\stepcounter{address}\label{CMU}%
+%%   McWilliams Center for Cosmology, Carnegie Mellon University}
+%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Caltech}%
+%%   Department of Astronomy, California Institute of Technology}
+%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Columbia}%
+%%   Department of Astronomy, Columbia University}
 
@@
   \name\ works at the pixel level (not the photometric measurement level);
-  it can capture more fine-grained information about the variation of the spacecraft than is available in the photometry.
+  it can capture more fine-grained information about the variation of the spacecraft
+  (especially regarding pointing and point-spread function)
+  than is available in the pixel-summed photometry.
 \name\ is extreme in that it has enormous flexibility and it only uses data (and meta-data) to model data:
@@
   it is designed to remove spacecraft-induced variability but not intrinsic stellar variability.
-We show that \name\ outperforms the \Kepler\ Presearch Data Conditioning method on a set of example stars.
+We show that \name\ outperforms the \Kepler\ Presearch (\sic) Data Conditioning method on a set of example stars.
 We release open-source code that provides \name\ output for any star in the existing \Kepler\ Archive,
@@
 
+Reminder:  \Kepler\ performs photometry very naively...
+
 One method that is designed to model spacecraft-induced problems
   but \emph{not} interfere with measurements of stellar variability
-  is the \Kepler\ Presearch Data Conditioning (PDC) method (CITE).
-The PDC ``de-trends’’ the \Kepler\ lightcurves by fitting them with a small set of basis lightcurves
+  is the \Kepler\ Presearch (\sic) Data Conditioning (PDC) method (CITE).
+The PDC ``de-trends'' the \Kepler\ lightcurves by fitting them with a small set of basis lightcurves
   generated from a principal components analysis (PCA) of filtered lightcurves.
@@
   (2)~that it has far more freedom (far more parameters)
-  but it strictly avoids over-fitting the lightcurves on exoplanet-transit time-scales through a train-and-test framework, and
+  but it strictly avoids over-fitting the lightcurves on exoplanet-transit time-scales
+  through strong regularization and a train-and-test framework, and
   (3)~that when it fits a star, there is no possibility of any contribution of the star itself to the fit basis vectors.
+The two methods are similar however,
+  in that they both make the assumption that whatever spacecraft effects are imprinting variability on a stellar lightcurve
+  must also be imprinting similar or related variability on other lightcurves.
+By going to the pixel level, \name\ makes it easier for the model to capture variability
+  that is coming through variations in the point-spread function
+  or spacecraft roll or pointing.
+
+\section{Generalities: Causality and data-driven models}
+
+\section{Specifics: PLM and it's hyper-parameters}
+
+\section{Examples and results}
+
+\section{Discussion}
 

### 2013-10-11 documents/plm.tex
introduction and acks

@@
 \newcommand{\Kepler}{\project{Kepler}}
-\newcommand{\name}{KPLM}
+\newcommand{\name}{PLM}
 
@@
   David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{MPIA},\ref{email}},
+  Rob~Fergus\altaffilmark{\ref{Courant}},
+  Stefan Harmeling\altaffilmark{\ref{MPIIS}},
   Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}},
@@
   Max-Planck-Institut f\"ur Intelligente Systeme, T\"ubingen}
+\altaffiltext{\theaddress}{\stepcounter{address}\label{Courant}%
+  Courant Institute of Mathematical Sciences, New York University}
 %% \altaffiltext{\theaddress}{\stepcounter{address}\label{Oxford}%
@@
 %%   Harvard--Smithsonian Center for Astrophysics}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Courant}%
-%%   Courant Institute of Mathematical Sciences, New York University}
 %% \altaffiltext{\theaddress}{\stepcounter{address}\label{UCL}%
@@
 
+\section{Ultra-precise photometry}
+
 The photometric measurements of stars made by the \Kepler\ Satellite are precise enough
@@
 
-Reminder:  \Kepler\ performs photometry very naively...
+In general, there are many reasons for apparent photometric variability in a \Kepler\ source.
+There is intrinsic stellar variability,
+  which is of interest to some and a nuisance to others.
+There is also variability of overlapping fainter stars;
+  that is, confusion noise combined with variability of the confusing sources.
+There are small changes in spacecraft pointing,
+  which leads to slightly different illumination of the focal-plane pixels,
+  and thus different sensitivity to errors (problems) in the device flat-field or sensitivity map.
+There are also \emph{intra-pixel} sensitivity variations that can contribute (CITE WHITEPAPER, SPITZER).
+There are small changes in spacecraft temperature,
+  which lead to point-spread function (PSF) and differential (across the focal plane) pointing changes.
+These also lead to changes in pixel and intra-pixel illumination.
+Stellar proper motion and parallaxes must do the same, at some level.
+There is electronic cross-talk between detectors and charge-transfer inefficiency,
+  that can effectively transfer variability from one source to another.
+There are also possible changes to the detector sensitivity over time,
+  and possibly sources of variability not yet considered.
+The remarkable thing about \Kepler\ is that it is trying to measure stars at a level of precision
+  much higher than ever previously attempted;
+  new effects really \emph{must} appear at some point.
+In \figurename~HOGG, we show the pixel-level variability in the \Kepler\ data
+  near one bright, non-variable star.
 
-One method that is designed to model spacecraft-induced problems
-  but \emph{not} interfere with measurements of stellar variability
+We propose and advise dealing with these variations in \Kepler\ light-curves by \emph{modeling} them.
+This model can be a physical model (of the spacecraft PSF, pointing, temperature, and so on)
+  or it can be a flexible, effective model that has no direct interpretation in terms of physical spacecraft parameters.
+In principle a physical model will do a better job,
+  because it necessarily embodies more prior information,
+  but it requires research and intuition about dominant effects,
+  and this research and intuition is often wrong or incomplete.
+The model we propose here is in the non-physical, effective category.
+The \Kepler\ community is familiar with these kinds of models;
+  to our knowledge, \emph{all} successful light-curve ``de-trending'' methods
+  are flexible, effective models.
+
+One such method---one that is designed to model spacecraft-induced problems
+  but \emph{not} interfere with measurements of stellar variability---%
   is the \Kepler\ Presearch (\sic) Data Conditioning (PDC) method (CITE).
@@
   regularizing the fit (and avoiding over-fitting) by filtering and restricting the dimensionality (through PCA).
-The method proposed here, \name, is similar in spirit to the PDC.
+The method proposed here, \name, is very similar in spirit to the PDC.
 The main differences are
-  (1)~that it works in the pixel domain, not the lightcurve domain, so it has access to more fine-grained information,
-  (2)~that it has far more freedom (far more parameters)
+  (1)~that \name\ works in the pixel domain, not the lightcurve domain, so it has access to more fine-grained information,
+  (2)~that \name\ has far more freedom (far more parameters) than the PDC
   but it strictly avoids over-fitting the lightcurves on exoplanet-transit time-scales
   through strong regularization and a train-and-test framework, and
-  (3)~that when it fits a star, there is no possibility of any contribution of the star itself to the fit basis vectors.
-The two methods are similar however,
+  (3)~that when \name\ fits a star, there is no possibility of any contribution of the star itself to the fit basis vectors.
+The two methods (\name\ and PDC) are similar however,
   in that they both make the assumption that whatever spacecraft effects are imprinting variability on a stellar lightcurve
@@
 By going to the pixel level, \name\ makes it easier for the model to capture variability
-  that is coming through variations in the point-spread function
-  or spacecraft roll or pointing.
+  that is coming through variations in the centroids and point-spread function
+  from spacecraft pointing, roll, and temperature.
+
+Before we start, a few reminders about the \Kepler\ data are in order:
+The satellite always observes precisely the same field, at fixed pointing (as closely as possible).
+The satellite is rolled by 90~deg every 90-ish days (for Solar Angle constraints).
+The PSF varies strongly across the field and is badly sampled.
+The stars span a huge range in brightness;
+  some of \Kepler's most important targets even saturate the device and bleed charge.
+The stellar photometry returned by the \Kepler\ SAP and PDC pipelines is based on
+  straight, \emph{unweighted} sums of pixels in small patches centered on the stellar centroid.
+We will return to this latter point at the end;
+  this kind of photometry cannot be optimal;
+  it must be possible to do a better job with the photometric measurements.
+That's beyond the scope of this paper but a place for a valuable intervention on the \Kepler\ data.
+
+The scope of this paper is an intervention---\name---that makes the \Kepler\ photometry more precise.
+We also provide an interface to the \Kepler\ data that delivers improved ``\name\ photometry'' for every \Kepler\ target,
+  and all the relevant code in public, open-source repositories.
 
@@
 
+HOGG: Return to the SAP photometry ``unweighted sum'' issue here.
+
+\acknowledgements
+It is a pleasure to thank the whole \Kepler\ Team
+  for designing, delivering, and operating a great facility,
+  and for making all of the data public, in all its rawest forms, through the MAST interface.
+We are also pleased to thank
+  Ruth~Angus (Oxford),
+  Bekki~Dawson (Berkeley),
+  Michael~Hirsch (UCL),
+  Dustin~Lang (CMU),
+  Benjamin~T.~Montet (Caltech),
+  and
+  David~Schiminovich (Columbia)
+for valuable discussions, input, encouragement, and advice.
+
+WHITEPAPER AUTHORS:  FEEL FREE TO CONTRIBUTE TO THIS PAPER AND MOVE FROM THE ACK LIST TO THE AUTHOR LIST.
+
 \end{document}

### 2013-10-11 documents/plm.tex
outline points
barclay author and comments

@@
   David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{MPIA},\ref{email}},
+  Tom~Barclay\altaffilmark{\ref{Ames}},
   Rob~Fergus\altaffilmark{\ref{Courant}},
@@
   To whom correspondence should be addressed; \texttt{<david.hogg@nyu.edu>}.}
+\altaffiltext{\theaddress}{\stepcounter{address}\label{Ames}%
+  NASA Ames Research Center}
+\altaffiltext{\theaddress}{\stepcounter{address}\label{Courant}%
+  Courant Institute of Mathematical Sciences, New York University}
 \altaffiltext{\theaddress}{\stepcounter{address}\label{MPIIS}%
   Max-Planck-Institut f\"ur Intelligente Systeme, T\"ubingen}
-\altaffiltext{\theaddress}{\stepcounter{address}\label{Courant}%
-  Courant Institute of Mathematical Sciences, New York University}
 %% \altaffiltext{\theaddress}{\stepcounter{address}\label{Oxford}%
 %%   Department of Physics, Oxford University}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Ames}%
-%%   NASA Ames Research Center}
 %% \altaffiltext{\theaddress}{\stepcounter{address}\label{CfA}%
@@
 These also lead to changes in pixel and intra-pixel illumination.
-Stellar proper motion and parallaxes must do the same, at some level.
+Stellar proper motion, geometric parallaxes, and differential stellar aberration as the spacecraft orbits all do more of the same.
 There is electronic cross-talk between detectors and charge-transfer inefficiency,
   that can effectively transfer variability from one source to another.
+There are additional electronics effects like ``rolling bands'' that put additional features into lightcurves.
 There are also possible changes to the detector sensitivity over time,
@@
 The scope of this paper is an intervention---\name---that makes the \Kepler\ photometry more precise.
-We also provide an interface to the \Kepler\ data that delivers improved ``\name\ photometry'' for every \Kepler\ target,
-  and all the relevant code in public, open-source repositories.
+We describe the method and deliver all the relevant code in a public, open-source repository.
+We also provide an interface to the \Kepler\ data that delivers improved ``\name\ photometry''
+  for every \Kepler\ target.
 
-\section{Generalities: Causality and data-driven models}
+\section{Generalities: Data-driven models}
+
+First idea: data modeled with data... huge models, regularization...
+
+Second idea: causality restricts the choice of data to use...
+
+Third idea: train-and-test framework...
+
+Fourth idea: predict; residuals are our signal...
+
+Fifth idea: no way to know if we are \emph{right}...
 

### 2013-10-13 documents/plm.tex
generalities text, notes to self

@@
 Stellar proper motion, geometric parallaxes, and differential stellar aberration as the spacecraft orbits all do more of the same.
-There is electronic cross-talk between detectors and charge-transfer inefficiency,
-  that can effectively transfer variability from one source to another.
+There is electronic cross-talk between detectors and charge-transfer inefficiency;
+  these can effectively transfer variability from one source to another.
 There are additional electronics effects like ``rolling bands'' that put additional features into lightcurves.
-There are also possible changes to the detector sensitivity over time,
+There are also probably changes to the detector sensitivity with temperature and time,
+  possibly illimunation-history effects,
   and possibly sources of variability not yet considered.
@@
 In \figurename~HOGG, we show the pixel-level variability in the \Kepler\ data
-  near one bright, non-variable star.
+  near one bright star that shows minimal intrinsic variability;
+  this figure highlights the spacecraft-induced effects.
 
 We propose and advise dealing with these variations in \Kepler\ light-curves by \emph{modeling} them.
-This model can be a physical model (of the spacecraft PSF, pointing, temperature, and so on)
+In this context, a model is (at least) a parameterized function that can predict data, given parameter settings,
+  and an objective function that can be optimized or sampled to choose or set those parameters.
+Ideally the objective function is probabilistic, or has a probabilistic justification,
+  as with a likelihood or a posterior pdf.
+The model can be a physical model (of the spacecraft PSF, pointing, temperature, and so on)
   or it can be a flexible, effective model that has no direct interpretation in terms of physical spacecraft parameters.
@@
   must also be imprinting similar or related variability on other lightcurves.
-By going to the pixel level, \name\ makes it easier for the model to capture variability
+They also assume that the relationships can be captured with linear models.
+By going to the pixel level (unlike the PDC, which works at the photometry level),
+  \name\ makes it easier for the model to capture variability
   that is coming through variations in the centroids and point-spread function
@@
 
+The first general idea about data-driven modeling of the kind used here
+  is that each data point or data source is going to be modeled
+  (or really \emph{predicted})
+  with a parameterized mathematical function of \emph{other data}.
+That is, given a choice of some \emph{target} \Kepler\ data,
+  we are going to find parameters of a function that takes as input some of the other \Kepler\ data,
+  and provides as output predictions of the target data.
+The simplest models are \emph{linear models},
+  in which predictions for the target data are built from linear combinations of the other data,
+  and in which the objective functions are quadratic in the prediction residual.
+Examples of quadratic objective functions include Gaussian likelihoods, mean-squared-error, and chi-square statistics.
+These models are simple,
+  not just because they are easy to express and compute,
+  but because optimization is convex:
+There is only one optimum for the objective function.
+
+The point of these models is to be \emph{flexible},
+  so the usual approach is to make the input data set very large,
+  and the number of parameters large,
+  often as large as---or larger than---the target data available.
+Such fits require \emph{regularization} to break degeneracies
+  and control ill-constrained parameters.
+These regularizations do for optimizations what priors do for posterior probability inferences;
+  they express the desired behavior of the fit in the absence of data
+  or along directions in parameter space in which the data are not constraining.
+General regularizations or priors will break the convexity of linear models;
+  if convexity is to be maintained, these regularizations also have to be quadratic,
+  or else one of a small number of other known forms (one of which is L1-regularization).
+Given these considerations, it makes sense to try to build our pixel-level model
+  using a linear model with a quadratic objective function and a quadratic regularization.
+
 First idea: data modeled with data... huge models, regularization...
@@
 
-\section{Specifics: PLM and it's hyper-parameters}
+\section{Specifics: PLM and model hyper-parameters}
 
@@
 
-HOGG: Return to the SAP photometry ``unweighted sum'' issue here.
+Return to the SAP photometry ``unweighted sum'' issue here.
+
+Didn't do anything about short-cadence data; suck it up.
+
+Lots of quantitative and qualitative choices that ought to be explored.
+
+Not the least of these is linearity.
+
+Interesting whether the output of the model can be interrogated to provide value for those building physical models.
 

### 2013-10-13 documents/plm.tex
causal structure

@@
 
-First idea: data modeled with data... huge models, regularization...
+[General formula here for a pixel predicted using a linear combination of other pixels.
+  And the objective function, generally?]
 
-Second idea: causality restricts the choice of data to use...
+The second general idea about data-driven modeling is the investigator's beliefs
+  about the causal processes that generate the data
+  are crucial in restricting the kinds of data that can be used as input to the model.
+That is, different assumptions about the physical properties of the data
+  and the data-taking system
+  lead to different structures for the data-driven model.
+For example, in the case of \Kepler\ data,
+  if we believe that different stars in the \Kepler\ field vary independently
+  (that is, are not physically synchronized in any way),
+  then the only reason that one star might show variability that is \emph{predictive}
+  (useful for prediction) of another star's variability
+  is that both stars are being observed by the same device or spacecraft.
+That is, one star's pixels can be used to predict another star's pixels
+  inasmuch as spacecraft issues imprint on both stars in related ways;
+  they share a common cause.
+For another example, if we think the spacecraft is being affected by
+  processes that take place over time-scales longer than a single read-out
+  (for example, thermal processes),
+  then it would be sensible to model the data at time $t$ using not just simultaneous data,
+  but also data from a range of times around $t$.
+For another example, if an investigator doesn't care about preserving stellar variability,
+  and just wants to detect exoplanet transits (say),
+  pixels from the target star can be used to predict pixels from the target star,
+  provided they are at large-enough time lags that they don't overlap (in time)
+  the signals of interest.
+That is, if the model is designed to fit not just spacecraft variability
+  but also intrinsic stellar variability,
+  the predictive model will be permitted to use as input pixels that \emph{do} overlap the target star.
+In what follows, we are only going to use input data that do not overlap that target star pixels.
+These models ought to remove spacecraft variability but not intrinsic stellar variability.
 

### 2013-10-13 documents/plm.tex
train-and-test

@@
   (that is, are not physically synchronized in any way),
-  then the only reason that one star might show variability that is \emph{predictive}
+  then the only reason that one star might show variability that is strongly \emph{predictive}
   (useful for prediction) of another star's variability
@@
 
-Third idea: train-and-test framework...
+The third general idea to mention is that we need to control for over-fitting.
+That is, once you have a flexible-enough model you can in principle fit \emph{anything},
+  whether it was caused by the spacecraft, intrinsic stellar variability, or a transiting exoplanet.
+How do you prevent a very flexible model from using small noise-induced fluctuations in all the input data
+  from being carefully combined linearly into models for every nook and cranny in the target data?
+In most projects in astrophysics, over-fitting is controlled for by limiting model freedom.
+The model is restricted in the number of parameters
+  (as in ``you can't have more parameters than data points'')
+  or by limiting the dimensionality
+  (as in principal components analysis)
+  or by applying strong priors
+  (as with smoothness priors, that effectively reduce freedom without explicitly reducing the number of parameters).
+In each case, the restriction on the model can be set with tools like cross-validation,
+  the fully marginalized likelihood (Bayes factor or evidence),
+  chi-squared statistical criteria,
+  or intuition or heuristics.
+Here we take a different and more general approach, which is to use a train-and-test framework.
+
+In this framework, the data used to \emph{train} the model%
+  ---meaning set the values of the parameters of the model---%
+  are disjoint from the \emph{test} data
+  ---meaning the data that are being predicted (the target data).
+Because we are extremely concerned with detecting Earth-analog exoplanet transits,
+  which take about ten hours,
+  we adopt an extreme version of the train-and-test framework,
+  in which the training data are always separated from the test data by at least ten hours.
+That is, when we are using the model to predict a particular pixel in the target data taken at time $t$,
+  we use parameters obtained by an optimization that makes use of only data
+  that comes either at times prior to $t-\Delta t$ or after $t+\Delta t$,
+  where $\Delta t$ is a tunable parameter but which we will set to roughly $10$~h.
+This ensures that no information about any exoplanet transit itself
+  can be entering into the prediction of the pixels contributing to the stellar photometry.
+In general, if there is a scientific goal of preserving intrinsic stellar variability,
+  or transit signals,
+  on time-scales of $\tau$,
+  the parameter optimization ought to be based on training data taken with a time-exclusion zone of width $\Delta > \tau$.
+
+In addition, each training data set within which we set the parameters (by optimization) has a finite total time extent $t_{\max}$.
+The train-and-test framework, which includes data out to time $t_{\max}$ but excludes data within $\Delta t$ of the test data,
+  effectively assumes that the signals worth preserving have time-scales less than $\Delta t$ but don't recur on time-scales
+  shorter than $t_{\max}$.
+Those assumptions are good for our purposes but not necessarily ideal for all users:
+Short-period exoplanets and certain kinds of stellar variability
+  could be wiped out by a model with these settings of the training-data regime.
 

### 2013-10-15 documents/plm.tex
crazy generalities and philosophy

@@
 Given these considerations, it makes sense to try to build our pixel-level model
-  using a linear model with a quadratic objective function and a quadratic regularization.
+  using a linear model with a quadratic objective function and a quadratic regularization;
+  this is what \name\ will be.
 
@@
 
-The third general idea to mention is that we need to control for over-fitting.
+The third general idea is that we need to control for over-fitting.
 That is, once you have a flexible-enough model you can in principle fit \emph{anything},
@@
 
-Fourth idea: predict; residuals are our signal...
+The fourth general idea involved in this kind of data-driven modeling is that the models aren't \emph{interpretable}.
+This means, in particular, that although the model might do a good job of \emph{predicting} the target pixels,
+  using a linear (or more complex) combination ofthe input pixel data,
+  it won't deliver anything that can be unambiguously interpreted as the \emph{flux} of the star in question,
+  or any other signal we care about.
+The data-driven model \emph{effectively} describes the pointing, point-spread function, and flat-field
+  of the telescope and camera,
+  plus the variability of every star and every exoplanet transit,
+  but it does so without ever \emph{explicitly} creating any of those objects.
+We have to make some kind of heuristic or interpretive move to extract from the data-driven model the quanitites of interest.
 
-Fifth idea: no way to know if we are \emph{right}...
+In the context of this project, the quantities of interest are the light-curves
+  (photometry as a function of time or apparent flux as a function of time)
+  for every star.
+What we get, for every star, from the data-driven model, is a train-and-test prediction
+  for the brightness of every pixel in the patch of the detector relevant to the star,
+  along with the residual, or the difference between the measured read-out pixel value and the prediction (data minus model).
+What will be called the ``\name\ photometry'' in what follows is constructed from what will be called the ``\name\ images''.
+The \name\ photometry is constructed from the \name\ images just as the \Kepler\ official SAP photometry is constructed from the XXX images;
+  that is, by summing pre-defined sets of pixels (with unit weights; see above and below for criticism of this).
+The \name\ images are constructed from the data-driven model predictions by taking,
+  for each pixel in each contiguous data segment (see below),
+  the \emph{mean} predicted pixel value (mean over time),
+  and adding to it the residuals (data minus model) away from the data-driven model prediction.
+These \name\ images are ``calibrated'' images,
+  in that the data-driven model has been used to fit out all the variability it can,
+  subject to the restrictions imposed by its finite freedom and the train-and-test specification.
+The signal---in which exoplanet transits will be found---is fundamentally the observed residual away from this prediction,
+  but it has to be added back into the mean prediction to have the right ``baseline'' or zero level.
+In short, \name\ will produce prediction images, residual images, \name\ images (mean prediction plus residual),
+  and aperture-based \name\ photometry analogous to the SAP photometry.
 
-\section{Specifics: PLM and model hyper-parameters}
+Finally, the fifth general idea is that there is no objective \emph{ground truth} against which we can tell
+  that any particular data-driven model is better or worse than any other.
+This problem is a problem for \name, and for the \Kepler\ PDC, and any other data-driven calibration models.
+One might think that the ``best'' model is the one that predicts data with lowest variance;
+  this would be true if all models adhered to the same train-and-test framework, which they don't.
+Besides, a model that can predict not just the spacecraft-induced variability,
+  but also variability caused by exoplanet transits of interest,
+  will effectively over-fit and distort the most important information in the light-curves.
+That is, what is considered best for modeling the data depends on the objectives of the user.
+For us, who are interested (in the long term) in finding and characterizing Earth analogs,
+  the ``best'' data-driven model is the one that produces the most success in finding and characterizing Earth analogs!
+What we will show in what follows is that the \name\ photometry does not distort
+  artificially exoplanet transit signals injected into real \Kepler\ pixel-level data.
+We can also show that it produces stellar light-curves that look sensible for known variable stars.
+We cannot yet show that it is optimal for our long-term goals,
+  nor can we show that it produces images or light-curves that are more accurately calibrated;
+  we will only show promising properties of the \name\ outputs.
+In the end, the value of the \name\ will be demonstrated by the scientific projects it enables.
+
+\section{Specifics: \name\ specification and hyper-parameters}
 

### 2013-10-15 documents/plm.tex
tweaks

@@
   whether it was caused by the spacecraft, intrinsic stellar variability, or a transiting exoplanet.
-How do you prevent a very flexible model from using small noise-induced fluctuations in all the input data
-  from being carefully combined linearly into models for every nook and cranny in the target data?
+How do you prevent a very flexible model from taking small noise-induced fluctuations in all the input data
+  and carefully combining them linearly into detailed models for every nook and cranny in the target data?
 In most projects in astrophysics, over-fitting is controlled for by limiting model freedom.
@@
   (as with smoothness priors, that effectively reduce freedom without explicitly reducing the number of parameters).
-In each case, the restriction on the model can be set with tools like cross-validation,
+In each case, the restriction on the model is controlled by some \emph{hyper-parameter}
+  (such as the number of inputs, or number of principal components, or the strength of the smoothness prior).
+The hyper-parameters can be set or tested with tools like cross-validation,
   the fully marginalized likelihood (Bayes factor or evidence),
@@
   on time-scales of $\tau$,
-  the parameter optimization ought to be based on training data taken with a time-exclusion zone of width $\Delta > \tau$.
+  the parameter optimization ought to be based on training data taken with a time-exclusion zone of half-width $\Delta t > \tau$.
+
+% need to choose consistent notation or terminology about the contiguous data chunks.
 
@@
 This means, in particular, that although the model might do a good job of \emph{predicting} the target pixels,
-  using a linear (or more complex) combination ofthe input pixel data,
+  using a linear (or more complex) combination of the input pixel data,
   it won't deliver anything that can be unambiguously interpreted as the \emph{flux} of the star in question,
@@
 What we will show in what follows is that the \name\ photometry does not distort
-  artificially exoplanet transit signals injected into real \Kepler\ pixel-level data.
+  artificial exoplanet transit signals injected into real \Kepler\ pixel-level data.
 We can also show that it produces stellar light-curves that look sensible for known variable stars.

### 2013-10-15 documents/plm.tex
figure one; tweaks, notes to self

@@
 \newcommand{\name}{PLM}
+\newcommand{\todo}[1]{\textbf{#1}}
 
@@
   new effects really \emph{must} appear at some point.
-In \figurename~HOGG, we show the pixel-level variability in the \Kepler\ data
+In \figurename~\ref{fig:pixelpatch}, we show the pixel-level variability in the \Kepler\ data
   near one bright star that shows minimal intrinsic variability;
@@
 
-\section{Generalities: Data-driven models}
+\section{Data-driven models}
 
@@
 What will be called the ``\name\ photometry'' in what follows is constructed from what will be called the ``\name\ images''.
-The \name\ photometry is constructed from the \name\ images just as the \Kepler\ official SAP photometry is constructed from the XXX images;
+The \name\ photometry is constructed from the \name\ images
+  just as the \Kepler\ official SAP photometry is constructed from the \todo{XXX images};
   that is, by summing pre-defined sets of pixels (with unit weights; see above and below for criticism of this).
@@
 
-\section{Specifics: \name\ specification and hyper-parameters}
+\section{\name\ specification and hyper-parameters}
 
@@
 
-Not the least of these is linearity.
+Not the least of these is linearity; deep learning and so on.
 
-Interesting whether the output of the model can be interrogated to provide value for those building physical models.
+The weakest point is construction of photometry from the model plus residuals;
+  interesting whether the output of the model can be interrogated
+  to provide value for those building physical models.
 
@@
 
-WHITEPAPER AUTHORS:  FEEL FREE TO CONTRIBUTE TO THIS PAPER AND MOVE FROM THE ACK LIST TO THE AUTHOR LIST.
+\todo{White-paper Authors:  Feel free to contribute to this paper and move from the ack list to the author list.}
+
+\clearpage
+\begin{figure}
+~ % DFM: replace this ~ with a figure
+\caption{A patch of \Kepler\ imaging from \todo{XXX quarter}, centered on \todo{YYY target}.
+  In the top panel, each box represents a pixel.
+  Within each box is shown the light-curve of that pixel over the quarter.
+  In the bottom panel, the SAP photometry for this target is shown;
+  the SAP photometry is based on a straight sum of the pixels marked with darker borders.
+  Note that every pixel varies substantially but the total SAP photometry is better than any individual pixel.
+  Note also that the pixel variations are strongly inter-related.\label{fig:pixelpatch}}
+\end{figure}
 

### 2013-10-15 documents/plm.tex
todo items

@@
 
-[General formula here for a pixel predicted using a linear combination of other pixels.
-  And the objective function, generally?]
+\todo{Should we put general formula here for a pixel predicted using a linear combination of other pixels?
+  And the objective function, generally?}
 
@@
 
-% need to choose consistent notation or terminology about the contiguous data chunks.
+\todo{In what follows, we need to choose consistent notation or terminology about the contiguous data chunks, and other \Kepler\ entities.}
 

### 2013-10-15 documents/plm.tex
todos, tweak

@@
   supplemented by various methods for removing small residual spacecraft-induced and stellar-variability trends in the brightnesses,
-  either filtering the data (with things like median filters; CITE)
-  or fitting the data with flexible models (like polynomials or splines or Gaussian Processes; CITE).
+  either filtering the data (with things like median filters; \todo{citations})
+  or fitting the data with flexible models (like polynomials or splines or Gaussian Processes; \todo{citations}).
 When employed in the service of exoplanet search and characterization,
@@
   and thus different sensitivity to errors (problems) in the device flat-field or sensitivity map.
-There are also \emph{intra-pixel} sensitivity variations that can contribute (CITE WHITEPAPER, SPITZER).
+There are also \emph{intra-pixel} sensitivity variations that can contribute (\todo{cite white paper; Spitzer results}).
 There are small changes in spacecraft temperature,
@@
   but \emph{not} interfere with measurements of stellar variability---%
-  is the \Kepler\ Presearch (\sic) Data Conditioning (PDC) method (CITE).
+  is the \Kepler\ Presearch (\sic) Data Conditioning (PDC) method (\todo{citation}).
 The PDC ``de-trends'' the \Kepler\ lightcurves by fitting them with a small set of basis lightcurves
@@
 The satellite always observes precisely the same field, at fixed pointing (as closely as possible).
-The satellite is rolled by 90~deg every 90-ish days (for Solar Angle constraints).
+The satellite is rolled by 90~deg every 90-ish days (to satisfy Solar-Angle constraints).
 The PSF varies strongly across the field and is badly sampled.

### 2013-10-16 documents/plm.tex
tilde

@@
   Rob~Fergus\altaffilmark{\ref{Courant}},
-  Stefan Harmeling\altaffilmark{\ref{MPIIS}},
+  Stefan~Harmeling\altaffilmark{\ref{MPIIS}},
   Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}},

### 2013-10-16 documents/plm.tex
notes to self

@@
 
+For each pixel, we choose the set of basis-vector pixels how?
+
+For each time-step, we choose the set of training time steps how?
+
+We specify what likelihood and what regularization?
+
+We train the model how?
+
+We choose the strength of the regularization how?
+
+We do this for every pixel and every time step.
+Implementation issues.
+
+We construct the predicted images and the \name\ images how?
+
+What does the interface look like?  What are the run times and so on?
+
 \section{Examples and results}
+
+For each example, give the code and show the output and provide some discussion.
 
@@
 Lots of quantitative and qualitative choices that ought to be explored.
+These include what and what and what and what?
 

### 2013-10-17 documents/plm.tex
start terminology cray cray

@@
 \newcommand{\name}{PLM}
+\newcommand{\set}[1]{\mathcal{#1}}
 \newcommand{\todo}[1]{\textbf{#1}}
@@
 The satellite always observes precisely the same field, at fixed pointing (as closely as possible).
+Only a few percent of the 80 million pixels in the focal plane are telemetered down
+  to Earth from each 30-min exposure;
+  the telemetered pixels are associated with \Kepler\ target stars chosen for study by the \Kepler\ Team.
 The satellite is rolled by 90~deg every 90-ish days (to satisfy Solar-Angle constraints).
+The focal plane contains many CCDs;
+  this plus the 90-deg rotations means that each star is at a particular location
+  on a particular CCD for 90-ish-day contiguous periods of time.
 The PSF varies strongly across the field and is badly sampled.
@@
   that comes either at times prior to $t-\Delta t$ or after $t+\Delta t$,
-  where $\Delta t$ is a tunable parameter but which we will set to roughly $10$~h.
+  where $\Delta t$ is a tunable parameter but which we will set to roughly $12$~h.
 This ensures that no information about any exoplanet transit itself
@@
 
-For each pixel, we choose the set of basis-vector pixels how?
+Each individual \Kepler\ target star is, for each quarter (each 90-ish-day period),
+  on a particular CCD on the \Kepler\ focal plane.
+Associated with each target star is some set of pixels,
+  located in a small contiguous patch more-or-less centered on the target star,
+  and telemetered down once for every 30-min exposure.
+(Here we are ignoring all short-cadence data that is taken in a different mode with shorter exposures.)
+That is, each telemetered pixel in each CCD is associated with a particular \Kepler\ target star.
 
-For each time-step, we choose the set of training time steps how?
+Let's consider a particular pixel $m$ in the focal plane in one particular quarter.
+In that quarter, the spacecraft delivers $N\sim 4000$ measurements $I_{mn}$
+  of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the quarter.
+(For intensity measurements $I_{mn}$ here we are using pixels from the \todo{WHICH \Kepler\ image product?})
+We want to build a prediction for the intensity $I_{mn}$ in pixel $m$ at each time $t_n$
+  using the intensities $I_{m'n}$ of other pixels $m'$.
+The question is:  What other pixels to choose?
+There are many possible qualitatively and quantitatively different choices here.
+Somewhat arbitrarily,
+  we choose all the pixels $m'$ associated with the $Q=5$ stars on the same CCD in the same quarter
+  that are closest in magnitude
+  (\Kepler\ magnitude as reported in the \Kepler\ Input Catalog)
+  to the target star associated with pixel $m$.
+We call this set of pixels%
+  ---from the $Q$ stars on the same CCD---%
+  the \emph{pixel set} $\set{M}_m$ associated with pixel $m$.
+Note that because the set $\set{M}_m$ is of pixels associated with \emph{different} stars
+  than the star associated with pixel $m$,
+  the pixel $m$ will not be in the set $\set{M}_m$,
+  and nor will any of pixel $m$'s close neighbors.
+That is, there will be no (or almost no) overlap in stellar illumination of pixel $m$
+  and the pixels $m'\in\set{M}_m$.
+
+When we are predicting the measurement $I_{mn}$ from pixel $m$ at a particular time $t_n$,
+  we are going to use a train-and-test framework in which not only do we not use
+  data at time $t_n$ in optimizing the parameters of the regression or fit,
+  but we don't even use any times $t$ such that $|t-t_n| < \Delta t$,
+  where $\Delta t\sim 12$\,h.
+That is, we train (optimize fit parameters) using a set $\set{N}_n$ of time
+  indices $n'$ such that for all $n'\in\set{N}_n$,
+  $t_{n'}$ is in the same quarter as $t_n$,
+  and $|t_{n'} - t_n|>\Delta t$.
+The training set of time indices $\set{N}_n$ therefore does not overlap the time point $t_n$,
+  nor any of its neighbors in a time window of half-width $\Delta_t$.
+
+\begin{eqnarray}
+I_{mn}         &=& I^{\ast}_{mn} + \mbox{noise}
+\\
+I^{\ast}_{mn}  &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n}
+\\
+I^{\ast}_{mn'} &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n'}
+\\
+\chi^2_{mn}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{mn'} - I^{\ast}_{mn'}]^2}{\sigma^2_{mn'}}
+                 + \sum_{m'\in\set{M}_m} \frac{a_{mm'}^2}{\Sigma^2}
+\end{eqnarray}
 

### 2013-10-17 documents/plm.tex
some formulae for next time

@@
   to the target star associated with pixel $m$.
-We call this set of pixels%
+This set of pixels%
   ---from the $Q$ stars on the same CCD---%
-  the \emph{pixel set} $\set{M}_m$ associated with pixel $m$.
+  is the \emph{pixel set} $\set{M}_m$ associated with pixel $m$.
 Note that because the set $\set{M}_m$ is of pixels associated with \emph{different} stars
@@
   where $\Delta t\sim 12$\,h.
-That is, we train (optimize fit parameters) using a set $\set{N}_n$ of time
+That is, we train (optimize fit parameters) using the \emph{time set} $\set{N}_n$ of time
   indices $n'$ such that for all $n'\in\set{N}_n$,
@@
   and $|t_{n'} - t_n|>\Delta t$.
-The training set of time indices $\set{N}_n$ therefore does not overlap the time point $t_n$,
+The time set of indices $\set{N}_n$ therefore does not overlap the time point $t_n$,
   nor any of its neighbors in a time window of half-width $\Delta_t$.
 
+We specify what likelihood and what regularization?
+\todo{foo:}
 \begin{eqnarray}
@@
 I^{\ast}_{mn'} &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n'}
-\\
+\quad,
+\end{eqnarray}
+where \todo{bar}
+\begin{eqnarray}
 \chi^2_{mn}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{mn'} - I^{\ast}_{mn'}]^2}{\sigma^2_{mn'}}
                  + \sum_{m'\in\set{M}_m} \frac{a_{mm'}^2}{\Sigma^2}
+\quad,
 \end{eqnarray}
-
-We specify what likelihood and what regularization?
+where \todo{bar}
 

### 2013-10-18 documents/plm.tex
tweaks, careful about words model and predict

@@
   than is available in the pixel-summed photometry.
-\name\ is extreme in that it has enormous flexibility and it only uses data (and meta-data) to model data:
+\name\ is extreme in that it has enormous flexibility and it only uses data (and meta-data) to predict data:
 \name\ provides a prediction for each readout pixel built from a linear combination of the readouts
@@
 
-One such method---one that is designed to model spacecraft-induced problems
+One such method---one that is designed to describe or model spacecraft-induced problems
   but \emph{not} interfere with measurements of stellar variability---%
@@
   generated from a principal components analysis (PCA) of filtered lightcurves.
-That is, it uses data to model data,
+That is, it uses data to predict data,
   regularizing the fit (and avoiding over-fitting) by filtering and restricting the dimensionality (through PCA).
@@
 The first general idea about data-driven modeling of the kind used here
-  is that each data point or data source is going to be modeled
-  (or really \emph{predicted})
-  with a parameterized mathematical function of \emph{other data}.
+  is that each data point or data source is going to be 
+  \emph{predicted} with or using a parameterized mathematical function of \emph{other data}.
 That is, given a choice of some \emph{target} \Kepler\ data,
@@
   (as with smoothness priors, that effectively reduce freedom without explicitly reducing the number of parameters).
-In each case, the restriction on the model is controlled by some \emph{hyper-parameter}
+In each case, the restriction on model freedom is controlled by some \emph{hyper-parameter}
   (such as the number of inputs, or number of principal components, or the strength of the smoothness prior).
@@
   for the brightness of every pixel in the patch of the detector relevant to the star,
-  along with the residual, or the difference between the measured read-out pixel value and the prediction (data minus model).
+  along with the residual, or the difference between the measured read-out pixel value and the prediction (data minus prediction).
 What will be called the ``\name\ photometry'' in what follows is constructed from what will be called the ``\name\ images''.
@@
   the \emph{mean} predicted pixel value (mean over time),
-  and adding to it the residuals (data minus model) away from the data-driven model prediction.
+  and adding to it the residuals (data minus prediction) away from the data-driven model prediction.
 These \name\ images are ``calibrated'' images,
@@
 
+The model is
 We specify what likelihood and what regularization?
@@
 I^{\ast}_{mn}  &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n}
-\\
-I^{\ast}_{mn'} &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n'}
 \quad,
@@
                  + \sum_{m'\in\set{M}_m} \frac{a_{mm'}^2}{\Sigma^2}
+\\
+I^{\ast}_{mn'} &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n'}
 \quad,

### 2013-10-18 documents/plm.tex
metadata

@@
 \newcommand{\set}[1]{\mathcal{#1}}
+\newcommand{\given}{\,|\,}
 \newcommand{\todo}[1]{\textbf{#1}}
@@
 
-The model is
-We specify what likelihood and what regularization?
+In addition to the other data (from pixels $m'\in\set{M}_m$ and taken at time points $n'\in\set{N}_n$)
+  used to make each prediction, we will use also some \emph{meta-data};
+  these include the time itself $t_n$,
+  the sine and cosine of the parallactic angle $\theta(t_n)$,
+  and the dot product $\hat{n}\cdot v(t_n)$ of the spacecraft velocity $v(t_n)$
+  with the direction $\hat{n}$ towards the \Kepler\ field center.
+These additional meta-data variables permit the data-driven model
+  to capture easily variations induced in the data
+  by proper motions, parallaxes, and stellar aberration.
+Symbolically, we will denote these $K=4$ pieces of meta-data $d_{kn}$.
+
+As mentioned above, in the context of this project,
+  a model is something that can predict data given settings of some parameters,
+  and an objective function that can be used to find best values for those parameters.
+We prefer to work in a probabilistic mode in which the objective function can be justified
+  in terms of a likelihood (probability for the data given the model)
+  or a posterior probability density function (likelihood times a prior pdf).
+The PLM treats the noise in a \Kepler\ pixel $m$ at time $n$ as Gaussian (normally distributed)
+  with mean zero and known variance $\sigma^2_{mn}$,
+  and the expectation value for each \Kepler\ data point $I_{mn}$ as being
+  predictable from a linear combination of data points $I_{m'n}$,
+  where $m'$ is from the set of non-overlapping pixels $m'\in\set{M}_m$.
+This linear model has parameters (linear coefficients) $a_{mm'}$.
 \todo{foo:}
 \begin{eqnarray}
-I_{mn}         &=& I^{\ast}_{mn} + \mbox{noise}
+I_{mn}         &=& I^{\ast}_{mn} + e_{mn}
 \\
-I^{\ast}_{mn}  &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n}
+I^{\ast}_{mn}  &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n} + \sum_{k=1}^{K} b_{mk}\,d_{kn}
+\\
+p(e_{mn})      &=& N(e_{mn}\given 0,\sigma^2_{mn})
 \quad,
 \end{eqnarray}
-where \todo{bar}
+where HOGGGGGGGGGGGGGGGGGGGGGGGG
 \begin{eqnarray}

### 2013-10-18 documents/plm.tex
objective function, optimization, notes to self

@@
   or a posterior probability density function (likelihood times a prior pdf).
-The PLM treats the noise in a \Kepler\ pixel $m$ at time $n$ as Gaussian (normally distributed)
-  with mean zero and known variance $\sigma^2_{mn}$,
-  and the expectation value for each \Kepler\ data point $I_{mn}$ as being
+The PLM treats each \Kepler\ data point $I_{mn}$ as being
   predictable from a linear combination of data points $I_{m'n}$,
   where $m'$ is from the set of non-overlapping pixels $m'\in\set{M}_m$.
-This linear model has parameters (linear coefficients) $a_{mm'}$.
-\todo{foo:}
 \begin{eqnarray}
@@
 I^{\ast}_{mn}  &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n} + \sum_{k=1}^{K} b_{mk}\,d_{kn}
-\\
-p(e_{mn})      &=& N(e_{mn}\given 0,\sigma^2_{mn})
 \quad,
 \end{eqnarray}
-where HOGGGGGGGGGGGGGGGGGGGGGGGG
+where $I^{\ast}_{mn}$ is the prediction (by the model) for data point $I_{mn}$,
+  $e_{mn}$ is a noise contribution or residual away from the prediction,
+  and the $a_{mm'}$ and $b_{mk}$ are the parameters (linear coefficients of the prediction).
+If we presume that the residuals away from the prediction are normally distributed with zero mean
+  and known variance,
+  likelihood optimization reduces to chi-squared minimization.
+We add to the standard chi-squared definition a regularization term
+  (equivalent to multiplying the likelihood by a Gaussian prior pdf)
+  that penalizes large absolute values for the the coefficients $a_{mm'}$:
 \begin{eqnarray}
@@
 \\
-I^{\ast}_{mn'} &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n'}
+I^{\ast}_{mn'} &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n'} + \sum_{k=1}^{K} b_{mk}\,d_{kn'}
 \quad,
 \end{eqnarray}
-where \todo{bar}
+where the $\sigma^2_{mn'}$ are the (presumed known) individual-pixel noise variances,
+  and $\Sigma^2$ sets the strength of the regularization (or width of the prior pdf).
+\todo{DFM: We set or ``know'' the variances how?
+  I think we should use the inverse of the median of the reported inverse variances.
+  Also, we set the prior strength to what value?
+  Heuristic justification of the latter.}
 
-We train the model how?
+The train-and-test idea comes into the objective function $\chi^2_{mn}$:
+When we are computing the objective function $\chi^2_{mn}$,
+  we are using only time points $n'\in\set{N}_n$ that don't overlap the target (or test) time point $n$.
+We train the model---that is, set the parameters $a_{mm'}$ and $b_{mk}$---%
+  by choosing the full set of parameters that jointly minimize the objective function $\chi^2_{mn}$.
+Importantly, and perhaps surprisingly, this is a \emph{different objective function}
+  for every target data point (pixel value to be predicted) $I_{mn}$,
+  and we have to do a \emph{independent optimization} of the parameters for every pixel value we want to predict.
+Since there are about $10^{11}$ total pixel values in the \Kepler\ \todo{what imaging?} data archive,
+  this represents one fuck of a lot of optimizations.
 
-We choose the strength of the regularization how?
-
-We do this for every pixel and every time step.
-Implementation issues.
+For this reason---\emph{so many optimizations}---%
+  we do \todo{some crazy clever stuff} to make this work fast;
+  \todo{DFM implementation notes here}.
 
@@
 These include what and what and what and what?
+How \emph{ought we} make all these choices?
 

### 2013-10-18 documents/plm.tex
notes to self

@@
 
-\todo{Should we put general formula here for a pixel predicted using a linear combination of other pixels?
-  And the objective function, generally?}
-
 The second general idea about data-driven modeling is the investigator's beliefs
@@
 
-\todo{In what follows, we need to choose consistent notation or terminology about the contiguous data chunks, and other \Kepler\ entities.}
-
-In addition, each training data set within which we set the parameters (by optimization) has a finite total time extent $t_{\max}$.
+In addition, each training data set within which we set the parameters (by optimization) has a finite total time extent $t_{\max}\approx 90$\,d.
 The train-and-test framework, which includes data out to time $t_{\max}$ but excludes data within $\Delta t$ of the test data,
@@
   and we have to do a \emph{independent optimization} of the parameters for every pixel value we want to predict.
+That is, every pixel datum $I_{mn}$ we predict will have
+  \emph{different} settings of the parameters $a_{mm'}$ and $b_{mk}$.
 Since there are about $10^{11}$ total pixel values in the \Kepler\ \todo{what imaging?} data archive,
-  this represents one fuck of a lot of optimizations.
+  this represents one fuck of a lot of optimizations,
+  and a lot of parameters to obtain and record.
 
@@
 
-We construct the predicted images and the \name\ images how?
+\todo{HOGG: We construct the predicted images and the \name\ images how?}
 
-What does the interface look like?  What are the run times and so on?
+\todo{HOGG: We construct the \name\ photometry from the \name\ images how?}
+
+\todo{DFM: What does the interface look like?  What are the run times and so on?}
 

### 2013-10-18 documents/plm.tex
project

@@
   it must be possible to do a better job with the photometric measurements.
-That's beyond the scope of this paper but a place for a valuable intervention on the \Kepler\ data.
+That's beyond the scope of this project but a place for a valuable intervention on the \Kepler\ data.
 
-The scope of this paper is an intervention---\name---that makes the \Kepler\ photometry more precise.
+The scope of this project is an intervention---\name---that makes the \Kepler\ photometry more precise.
 We describe the method and deliver all the relevant code in a public, open-source repository.

### 2013-10-20 documents/plm.tex
notes to self

@@
 
+\todo{Issue arising: I have called (below) the coefficients $a_{mm'}$.
+However, they are different for every pixel $I_{mn}$.
+That is, we do a separate optimization for every read-out pixel.
+That means that really we should call the coefficients $a_{mnm'}$, right?
+DFM:  Comments?}
+
 As mentioned above, in the context of this project,
@@
 
+Once we have obtained the $a_{mm'}$ parameters corresponding to data point $I_{mn}$ by minimizing the training objective $\chi^2_{mn}$.
+
 \todo{HOGG: We construct the predicted images and the \name\ images how?}

### 2013-10-22 documents/plm.tex
issue for dfm
closing DFM-related issues

--- 2013-10-18 documents/plm.tex
@@
   along with the residual, or the difference between the measured read-out pixel value and the prediction (data minus prediction).
-What will be called the ``\name\ photometry'' in what follows is constructed from what will be called the ``\name\ images''.
-The \name\ photometry is constructed from the \name\ images
-  just as the \Kepler\ official SAP photometry is constructed from the \todo{XXX images};
+What will be called the ``\name\ photometry'' in what follows is constructed from what will be called the ``\name\ pixels''.
+The \name\ photometry is constructed from the \name\ pixels
+  just as the \Kepler\ official SAP photometry is constructed from the \Kepler\ Target Pixel Files;
   that is, by summing pre-defined sets of pixels (with unit weights; see above and below for criticism of this).
-The \name\ images are constructed from the data-driven model predictions by taking,
+The \name\ pixels are constructed from the data-driven model predictions by taking,
   for each pixel in each contiguous data segment (see below),
@@
   and adding to it the residuals (data minus prediction) away from the data-driven model prediction.
-These \name\ images are ``calibrated'' images,
+These \name\ pixels are ``calibrated'' pixels,
   in that the data-driven model has been used to fit out all the variability it can,
@@
   but it has to be added back into the mean prediction to have the right ``baseline'' or zero level.
-In short, \name\ will produce prediction images, residual images, \name\ images (mean prediction plus residual),
+In short, \name\ will produce prediction pixels, residual pixels, \name\ pixels (mean prediction plus residual),
   and aperture-based \name\ photometry analogous to the SAP photometry.
@@
 We cannot yet show that it is optimal for our long-term goals,
-  nor can we show that it produces images or light-curves that are more accurately calibrated;
+  nor can we show that it produces pixelss or light-curves that are more accurately calibrated;
   we will only show promising properties of the \name\ outputs.
@@
   of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the quarter.
-(For intensity measurements $I_{mn}$ here we are using pixels from the \todo{WHICH \Kepler\ image product?})
+(For intensity measurements $I_{mn}$ here we are using pixels from the Target Pixel Files.)
 We want to build a prediction for the intensity $I_{mn}$ in pixel $m$ at each time $t_n$
@@
 \\
-I^{\ast}_{mn}  &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n} + \sum_{k=1}^{K} b_{mk}\,d_{kn}
+I^{\ast}_{mn}  &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m'n} + \sum_{k=1}^{K} b_{mnk}\,d_{kn}
 \quad,
@@
   $e_{mn}$ is a noise contribution or residual away from the prediction,
-  and the $a_{mm'}$ and $b_{mk}$ are the parameters (linear coefficients of the prediction).
+  and the $a_{mnm'}$ and $b_{mnk}$ are the parameters (linear coefficients of the prediction).
+The parameters $a_{mnm'}$ and $b_{mnk}$ have indices $m$ because
+  they are different for every pixel $m$,
+  and they will even be different for every time step $n$;
+  that is, there will be a separate best-fit value for the parameters for every $I_{mn}$.
 If we presume that the residuals away from the prediction are normally distributed with zero mean
@@
   (equivalent to multiplying the likelihood by a Gaussian prior pdf)
-  that penalizes large absolute values for the the coefficients $a_{mm'}$:
+  that penalizes large absolute values for the the coefficients $a_{mnm'}$:
 \begin{eqnarray}
-\chi^2_{mn}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{mn'} - I^{\ast}_{mn'}]^2}{\sigma^2_{mn'}}
-                 + \sum_{m'\in\set{M}_m} \frac{a_{mm'}^2}{\Sigma^2}
+\chi^2_{mn}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{mn'} - I^{\ast}_{mnn'}]^2}{\sigma^2_{mn'}}
+                 + \sum_{m'\in\set{M}_m} \frac{a_{mnm'}^2}{\Sigma^2}
 \\
-I^{\ast}_{mn'} &=& \sum_{m'\in\set{M}_m} a_{mm'}\,I_{m'n'} + \sum_{k=1}^{K} b_{mk}\,d_{kn'}
+I^{\ast}_{mnn'} &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m'n'} + \sum_{k=1}^{K} b_{mnk}\,d_{kn'}
 \quad,
@@
   and $\Sigma^2$ sets the strength of the regularization (or width of the prior pdf).
-\todo{DFM: We set or ``know'' the variances how?
-  I think we should use the inverse of the median of the reported inverse variances.
-  Also, we set the prior strength to what value?
-  Heuristic justification of the latter.}
+Although the variances $\sigma^2_{mn'}$ are in principle different for every time step $n'$,
+  for nearly-constant stars in good data, there is not much variation;
+  in what follows, we treat these uncertainties as fixed at
+  \todo{DFM: some mean value (we can't ignore this,
+   because it ``plays off against'' the regularization)}
+The regularization variance $\Sigma^2$ we set to 0.3 (\todo{DFM TAKE NOTE})
+  because we expect almost all the coefficients $a_{mnm'}$ to be less than unity in magnitude.
+We do not regularize the meta-data coefficients $b_{mnk}$,
+  because we want the model to make use of the (easily interpretable) meta-data coefficients as much as possible.
 
@@
   we are using only time points $n'\in\set{N}_n$ that don't overlap the target (or test) time point $n$.
-We train the model---that is, set the parameters $a_{mm'}$ and $b_{mk}$---%
+We train the model---that is, set the parameters $a_{mnm'}$ and $b_{mnk}$---%
   by choosing the full set of parameters that jointly minimize the objective function $\chi^2_{mn}$.
@@
 That is, every pixel datum $I_{mn}$ we predict will have
-  \emph{different} settings of the parameters $a_{mm'}$ and $b_{mk}$.
-Since there are about $10^{11}$ total pixel values in the \Kepler\ \todo{what imaging?} data archive,
+  \emph{different} settings of the parameters $a_{mnm'}$ and $b_{mnk}$.
+Since there are about $10^{11}$ total pixel values in the \Kepler\ Target Pixel Files,
   this represents one fuck of a lot of optimizations,
@@
 
-\todo{HOGG: We construct the predicted images and the \name\ images how?}
+Once we have obtained the $a_{mnm'}$ parameters corresponding to data point $I_{mn}$ by minimizing the training objective $\chi^2_{mn}$.
 
-\todo{HOGG: We construct the \name\ photometry from the \name\ images how?}
+\todo{HOGG: We construct the predicted pixels and the \name\ pixels how?}
+
+\todo{HOGG: We construct the \name\ photometry from the \name\ pixels how?}
 
@@
 ~ % DFM: replace this ~ with a figure
-\caption{A patch of \Kepler\ imaging from \todo{XXX quarter}, centered on \todo{YYY target}.
+\caption{A patch of \Kepler\ pixels from the Target Pixel Files
+  from \todo{XXX quarter}, centered on \todo{YYY target}.
   In the top panel, each box represents a pixel.

### 2013-10-23 documents/plm.tex
language tweaks -- solving not optimizing

@@
   by choosing the full set of parameters that jointly minimize the objective function $\chi^2_{mn}$.
-Importantly, and perhaps surprisingly, this is a \emph{different objective function}
-  for every target data point (pixel value to be predicted) $I_{mn}$,
-  and we have to do a \emph{independent optimization} of the parameters for every pixel value we want to predict.
+Fortunately, given the form of the model,
+  this minimization is just a linear solve (linear operation on the data).
+Importantly however, and perhaps surprisingly, the objective function $\chi^2_{mn}$ is \emph{different}
+  for every target data point (pixel value to be predicted) $I_{mn}$;
+  we have to do an \emph{independent optimization} (or really linear solve)
+  of the parameters for every pixel value we want to predict.
 That is, every pixel datum $I_{mn}$ we predict will have
   \emph{different} settings of the parameters $a_{mnm'}$ and $b_{mnk}$.
-Since there are about $10^{11}$ total pixel values in the \Kepler\ Target Pixel Files,
-  this represents one fuck of a lot of optimizations,
+Since there are of order $10^{6}$ total pixel values in the \Kepler\ Target Pixel Files for \emph{each \Kepler\ target},
+  and of order $10^7$ data sources used as basis functions in the linear fitting,
+  this represents one fuck of a lot of linear solves,
   and a lot of parameters to obtain and record.
 
-For this reason---\emph{so many optimizations}---%
+For this reason---\emph{so many solves}---%
   we do \todo{some crazy clever stuff} to make this work fast;

### 2013-10-23 documents/plm.tex
predicted pixels

@@
 
-Once we have obtained the $a_{mnm'}$ parameters corresponding to data point $I_{mn}$ by minimizing the training objective $\chi^2_{mn}$.
+Once we have obtained the $a_{mnm'}$ parameters corresponding to a particular data point $I_{mn}$,
+  we can make a \emph{prediction} $I^{\ast}_{mnn}$ for the intensity at that pixel.
+By construction of our objective function, this is truly a prediction,
+  in the sense that the optimization (or solve) that produced the parameters
+  (and thus the prediction)
+  did not make use of $I_{mn}$ itself,
+  or even any of the pixel values that are nearby in angle or time
+  (as described above).
+In addition to the predicted pixel value $I^{\ast}_{mnn}$,
+  we can also construct a \emph{residual} $\Delta_{mn}$ (data minus prediction),
+  defined by
+\begin{eqnarray}
+\Delta_{mn} &\equiv& I_{mn} - I^{\ast}_{mnn}
+\quad .
+\end{eqnarray}
 

### 2013-10-23 documents/plm.tex
plm pixels

@@
 In addition to the predicted pixel value $I^{\ast}_{mnn}$,
-  we can also construct a \emph{residual} $\Delta_{mn}$ (data minus prediction),
+  we can also construct a \emph{residual} $\delta_{mn}$ (data minus prediction),
   defined by
 \begin{eqnarray}
-\Delta_{mn} &\equiv& I_{mn} - I^{\ast}_{mnn}
+\delta_{mn} &\equiv& I_{mn} - I^{\ast}_{mnn}
 \quad .
@@
 
-\todo{HOGG: We construct the predicted pixels and the \name\ pixels how?}
+In some sense, it is this residual that contains the exoplanet transit signals we seek.
+That is, a transit creates a negative residual away from the prediction.
+So far, however, the model is a model of \emph{pixels},
+  and we need to obtain from this model \emph{photometric measurements} of stars.
+In order to construct stellar photometry measurements out of the residual pixels $\delta_{mn}$,
+  we add into each pixel residual $\delta_{mn}$ the \emph{mean predicted intensity} $\bar{I}^{\ast}_m$
+\begin{eqnarray}
+\bar{I}^{\ast}_m &=& \frac{1}{N_m}\,\sum_n I^{\ast}_{mnn}
+\quad ,
+\end{eqnarray}
+where $N_m$ is the number of time steps in the quarter,
+  and the sum is over those time steps.
+We construct what we will call ``the \name\ photometry''
+  from what we will call ``the \name\ pixels'' $J_{mn}$,
+  which are the residuals plus the mean, or
+\begin{eqnarray}
+J_mn &=& \delta_{mn} + \bar{I}^{\ast}_m
+\quad .
+\end{eqnarray}
+That is, \todo{WTF}
 
 \todo{HOGG: We construct the \name\ photometry from the \name\ pixels how?}
+
+\todo{Hogg \& DFM:  Why does the above make no fucking sense?}
 

### 2013-10-26 documents/plm.tex
PLM pixels, PLM photometry, interpretation

@@
   and the sum is over those time steps.
-We construct what we will call ``the \name\ photometry''
-  from what we will call ``the \name\ pixels'' $J_{mn}$,
+We construct what we will call ``the \name\ pixels'' $J_{mn}$,
   which are the residuals plus the mean, or
 \begin{eqnarray}
-J_mn &=& \delta_{mn} + \bar{I}^{\ast}_m
+J_{mn} &=& \delta_{mn} + \bar{I}^{\ast}_m
 \quad .
 \end{eqnarray}
-That is, \todo{WTF}
+\todo{DFM: Should we use mean or median here?}
+That is, we treat each pixel as differing from constant intensity
+  only inasmuch as it has residuals away from the model prediction.
 
-\todo{HOGG: We construct the \name\ photometry from the \name\ pixels how?}
+Our new stellar flux estimates,
+  what we will call the ``\name\ photometry'',
+  is constructed from the \name\ pixels
+  in precisely the same way as the official \Kepler\ SAP photometry
+  is constructed from the Target Pixel Files.
+That is, we perform a weighted sum of \name\ pixels $J_{mn}$ with weights $w_m$,
+  all of which are either zero or unity,
+  and we adopt precisely the same weight assignments as are adopted in the SAP photometry;
+  in equations, the flux estimate $S_n$ at time $t_n$ of the target star is given by
+\begin{eqnarray}
+S_n = \frac{1}{N_m}\,\sum_n w_m\,J_{mn}
+\quad .
+\end{eqnarray}
+As we have noted above and below, these photometric estimators are not optimal for any purpose,
+  but improving them is beyond the scope of this project.
 
-\todo{Hogg \& DFM:  Why does the above make no fucking sense?}
+Some---or probably most---of the variations of the pixel intensities
+  are being caused by small changes to stellar positions relative to the detector,
+  in turn caused by pointing drifts, parallaxes, proper motions, aberration, and temperature changes.
+The \name\ pixels, being constructed from a mean prediction plus residuals,
+  represent some kind of mean image, averaged over these positional changes.
+  that is, the image constructed from the \name\ pixels would have a broader
+  point-spread function than any individual time-step,
+  and does not necessarily represent any true astronomical scene.
+This is another consequence of the point, discussed above,
+  that data-driven models do not in general provide interpretable results.
+This uninterpretability creates a small problem,
+  which is that the optimization by which the \Kepler\ team chose the pixel weights $w_m$
+  cannot be precisely appropriate for the \name\ pixels,
+  even if it \emph{is} appropriate for the \Kepler\ Target Pixel Files.
+That is, there could be a small sacrifice at this step in photometric estimator quality.
+This motivates future work on photometric estimation.
+That said, we don't expect this effect to be large,
+  because the positional drifts involved are orders of magnitude smaller than a pixel.
 

### 2013-10-27 documents/plm.tex
note tweaks

@@
    because it ``plays off against'' the regularization)}
-The regularization variance $\Sigma^2$ we set to 0.3 (\todo{DFM TAKE NOTE})
+The regularization variance $\Sigma^2$ we set to 0.3 (\todo{DFM TAKE NOTE; that's about 10 for the parameter you usually use.})
   because we expect almost all the coefficients $a_{mnm'}$ to be less than unity in magnitude.
@@
   and the sum is over those time steps.
+\todo{DFM: Should we use mean or median here?}
 We construct what we will call ``the \name\ pixels'' $J_{mn}$,
@@
 \end{eqnarray}
-\todo{DFM: Should we use mean or median here?}
 That is, we treat each pixel as differing from constant intensity

### 2013-11-13 documents/plm.tex
notes to self

@@
 
+\todo{DFM: Do we want a schematic figure or cartoon which illustrates all of this?}
+
 In addition to the other data (from pixels $m'\in\set{M}_m$ and taken at time points $n'\in\set{N}_n$)
@@
 
+We need a metric for comparing outputs.
+For now lets try plotting the power spectrum of the SAP, PDC, and PLM photometry for each star.
+
+So DWH is imagining multi-panel plots: SAP, PDC, and PLM vs time,
+  plus a power-spectrum plot vs frequency.
+
+Cases ought to include
+\begin{itemize}
+\item a bright, non-variable G star with an Earth injection,
+\item a significant variable like that shown in the white paper, and
+\item a star with a bad quarter or where \Kepler\ sucked it.
+\end{itemize}
+
+Then we want to show some kind of scatter plot, which is some variance estimate from us,
+  vs the same estimate from the PDC,
+  to show that we always or usually win.
+
 \section{Discussion}
@@
   Benjamin~T.~Montet (Caltech),
+  David~Schiminovich (Columbia),
   and
-  David~Schiminovich (Columbia)
+  Jake Vanderplas (UW)
 for valuable discussions, input, encouragement, and advice.

### 2013-11-13 documents/plm.tex
autoregressive
scalar
small typos

@@
 
-Once we have obtained the $a_{mnm'}$ parameters corresponding to a particular data point $I_{mn}$,
+Once we have obtained the parameters $a_{mnm'}$ corresponding to a particular data point $I_{mn}$,
   we can make a \emph{prediction} $I^{\ast}_{mnn}$ for the intensity at that pixel.
@@
 \begin{eqnarray}
-S_n = \frac{1}{N_m}\,\sum_n w_m\,J_{mn}
-\quad .
+S_n = \frac{1}{M}\,\sum_m w_m\,J_{mn}
+\quad ,
 \end{eqnarray}
+where the sum is over the $M$ pixels that are associated with the target star.
 As we have noted above and below, these photometric estimators are not optimal for any purpose,
@@
   to show that we always or usually win.
+This variance estimate should be something like the power in the residuals at frequencies
+  corresponding to 30-hour periods or maybe 50-hour periods or something like that.
 
@@
 Not the least of these is linearity; deep learning and so on.
+
+The potential for autoregressive models.  Cite the white paper.
 

### 2013-11-15 documents/plm.tex
acks; figure 2

@@
 for valuable discussions, input, encouragement, and advice.
+This project was partially supported by NSF grant IIS-1124794 and NASA grant NNX12AI50G.
+This research made use of the NASA Astrophysics Data System.
 
@@
 
+\clearpage
+\begin{figure}
+~ % DFM: replace this ~ with a figure
+\caption{One quarter of photometric data for star XXX.
+  The top panel shows the \Kepler\ SAP photometry.
+  The next panel shows the \Kepler\ PDC photometry.
+  The next shows the PDC photometry.
+  The bottom panel shows the power spectra of the three lightcurves.\label{fig:example1}}
+\end{figure}
+
 \end{document}

### 2013-11-15 documents/plm.tex
typo
the-method-who-shall-not-be-named

@@
   or a posterior probability density function (likelihood times a prior pdf).
-The PLM treats each \Kepler\ data point $I_{mn}$ as being
+The \name\ treats each \Kepler\ data point $I_{mn}$ as being
   predictable from a linear combination of data points $I_{m'n}$,
@@
 We need a metric for comparing outputs.
-For now lets try plotting the power spectrum of the SAP, PDC, and PLM photometry for each star.
+For now lets try plotting the power spectrum of the SAP, PDC, and \name\ photometry for each star.
 
-So DWH is imagining multi-panel plots: SAP, PDC, and PLM vs time,
+So DWH is imagining multi-panel plots: SAP, PDC, and \name\ vs time,
   plus a power-spectrum plot vs frequency.
@@
 ~ % DFM: replace this ~ with a figure
-\caption{One quarter of photometric data for star XXX.
-  The top panel shows the \Kepler\ SAP photometry.
+\caption{One quarter of photometric data for star \todo{KIC XXX}.
+  The top panel shows the \Kepler\ SAP photometry;
+    the vertical axis is \todo{something like median-divided brightness}
+    and the horizontal axis is \todo{something like KBJD}.
   The next panel shows the \Kepler\ PDC photometry.
-  The next shows the PDC photometry.
+  The next shows the \name\ photometry.
   The bottom panel shows the power spectra of the three lightcurves.\label{fig:example1}}

### 2014-08-13 plm/__init__.py
GP model

@@ -1,0 +1,5 @@
+# -*- coding: utf-8 -*-
+
+__all__ = ["find_predictors", "get_matrix"]
+
+from .data import find_predictors, get_matrix

### 2014-08-13 plm/_kernel.pyx

@@ -1,0 +1,33 @@
+from __future__ import division
+
+cimport cython
+from libc.math cimport exp
+
+import numpy as np
+cimport numpy as np
+
+DTYPE = np.float64
+ctypedef np.float64_t DTYPE_t
+
+
+@cython.boundscheck(False)
+def build_isotropic_kernel(double amp, double factor,
+                           np.ndarray[DTYPE_t, ndim=2] x1,
+                           np.ndarray[DTYPE_t, ndim=2] x2):
+    cdef double r2, d
+    cdef unsigned int i, j, k
+    cdef unsigned int ndim = x1.shape[1]
+    cdef unsigned int n1 = x1.shape[0]
+    cdef unsigned int n2 = x2.shape[0]
+
+    cdef np.ndarray[DTYPE_t, ndim=2] K = np.empty((n1, n2), dtype=DTYPE)
+
+    for i in range(n1):
+        for j in range(n2):
+            r2 = 0.0
+            for k in range(ndim):
+                d = x1[i, k] - x2[j, k]
+                r2 += d*d
+            K[i, j] = amp * exp(r2 * factor)
+
+    return K

### 2014-08-13 plm/data.py

@@ -1,0 +1,367 @@
+# -*- coding: utf-8 -*-
+
+from __future__ import division, print_function
+
+__all__ = ["find_predictors", "get_matrix"]
+
+import kplr
+import logging
+import numpy as np
+import cPickle as pickle
+from multiprocessing import Pool
+
+import george
+from george import kernels
+
+from ._kernel import build_isotropic_kernel
+
+
+class IsotropicKernel(kernels.Kernel):
+
+    def __init__(self, amp, var, ndim=1):
+        super(IsotropicKernel, self).__init__(amp, var, ndim=ndim)
+
+    def set_pars(self, pars):
+        self._amp = pars[0]
+        self._factor = -0.5 / pars[1] ** 2
+
+    def __call__(self, x1, x2):
+        return build_isotropic_kernel(self._amp, self._factor, x1, x2)
+
+
+def load_data(tpf, is_target=False):
+    columns = ["TIME", "FLUX"]
+    if is_target:
+        columns += ["FLUX_ERR"]
+    data = tpf.read(columns=columns)
+    mask = tpf.read(ext=2)
+    data = map(np.array, (data[k] for k in columns))
+    if is_target:
+        t, f, fe = data
+    else:
+        t, f = data
+
+    # Flatten the pixel images.
+    n = len(t)
+    f = f.reshape((n, -1))
+    mask = mask.flatten()
+    if is_target:
+        fe = fe.reshape((n, -1))
+
+    # Find the missing data.
+    m = np.isfinite(f)
+    tm = np.isfinite(t)
+
+    # Remove missing pixels.
+    pm = np.any(m * tm[:, None], axis=0)
+    m = m[:, pm]
+    mask = mask[pm]
+    f = f[:, pm]
+    assert np.all(mask > 0)
+
+    if is_target:
+        # Throw away any missing epochs.
+        fe = fe[:, pm]
+        tm *= np.any(m, axis=1)
+        return tm, mask, t, f, fe
+
+    # Interpolate the missing data.
+    for i in xrange(m.shape[1]):
+        bad = tm * (~m[:, i])
+        if np.any(bad):
+            good = tm * m[:, i]
+            f[bad, i] = np.interp(t[bad], t[good], f[good, i])
+    return tm, mask, t, f
+
+
+class Dataset(object):
+
+    def __init__(self, kicid, quarter, npred, ccd=True, poly=0):
+        self.kicid = kicid
+        self.quarter = quarter
[…]

### 2014-08-13 plm/solvers.py

@@ -1,0 +1,52 @@
+# -*- coding: utf-8 -*-
+
+from __future__ import division, print_function
+
+__all__ = ["linear_least_squares"]
+
+import numpy as np
+from scipy import linalg
+
+
+def linear_least_squares(A, y, yvar=None, l2=None):
+    """
+    Solve a linear system as fast as possible.
+
+    :param A: ``(ndata, nbasis)``
+        The basis matrix.
+
+    :param y: ``(ndata)``
+        The observations.
+
+    :param yvar:
+        The observational variance of the points ``y``.
+
+    :param l2:
+        The L2 regularization strength. Can be a scalar or a vector (of length
+        ``A.shape[1]``).
+
+    """
+    # Incorporate the observational uncertainties.
+    if yvar is not None:
+        CiA = A / yvar[:, None]
+        if len(y.shape) > 1:
+            Ciy = y / yvar[:, None]
+        else:
+            Ciy = y / yvar
+    else:
+        CiA = A
+        Ciy = y
+
+    # Compute the pre-factor.
+    AT = A.T
+    ATA = np.dot(AT, CiA)
+
+    # Incorporate any L2 regularization.
+    if l2 is not None:
+        if np.isscalar(l2):
+            l2 = l2 + np.zeros(A.shape[1])
+        ATA[np.diag_indices_from(ATA)] += l2
+
+    # Solve the equations overwriting the temporary arrays for speed.
+    factor = linalg.cho_factor(ATA, overwrite_a=True)
+    return linalg.cho_solve(factor, np.dot(AT, Ciy), overwrite_b=True)

### 2014-08-13 run.py

@@ -1,0 +1,59 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+from __future__ import division, print_function
+
+__all__ = []
+
+import george
+import numpy as np
+import matplotlib.pyplot as pl
+from plm.data import Dataset, IsotropicKernel
+from plm.solvers import linear_least_squares
+
+
+if __name__ == "__main__":
+    # kicid = 5088536
+    # quarter = 5
+    # npred = 20
+    # dataset = Dataset(kicid, quarter, npred)
+    # dataset.build_matrix()
+    # dataset.save("dataset.pkl")
+
+    dataset = Dataset.load("dataset.pkl")
+
+    print(dataset.matrix.shape, dataset.targ_flux.shape)
+
+    m = np.ones_like(dataset.time, dtype=bool)
+    m[int(0.4*len(dataset.time)):int(0.6*len(dataset.time))] = False
+    print(m)
+
+    pixel = np.argmax(np.sum(dataset.targ_flux, axis=0))
+
+    w = linear_least_squares(dataset.matrix[m], dataset.targ_flux[m, pixel],
+                             yvar=dataset.targ_flux_err[m, pixel]**2)
+    y = np.dot(dataset.matrix, w)
+
+    # Estimate hyperparameters.
+    i = np.random.randint(len(dataset.time), size=500)
+    j = np.random.randint(len(dataset.time), size=500)
+    r = np.sqrt(np.median(np.sum((dataset.matrix[i] - dataset.matrix[j])**2,
+                                 axis=1)))
+    amp = np.var(dataset.targ_flux[:, pixel])
+
+    kernel = IsotropicKernel(amp, 5 * r, ndim=dataset.matrix.shape[1])
+    gp = george.GP(kernel, mean=np.mean(dataset.targ_flux[:, pixel]))
+    print("Pre-factoring matrix")
+    gp.compute(dataset.matrix[m], dataset.targ_flux_err[m, pixel], sort=False)
+
+    print("Predicting")
+    mu = gp.predict(dataset.targ_flux[m, pixel], dataset.matrix, True)
+    print(mu)
+
+    data = dataset.targ_flux[:, pixel]
+    pl.gca().axvline(min(dataset.time[~m]), color="k", alpha=0.5, lw=3)
+    pl.gca().axvline(max(dataset.time[~m]), color="k", alpha=0.5, lw=3)
[…]

### 2014-08-13 setup.py

@@ -1,0 +1,16 @@
+#!/usr/bin/env python
+# encoding: utf-8
+
+import numpy
+from Cython.Build import cythonize
+from setuptools import setup, Extension
+
+# Set up the extension.
+ext = Extension("plm._kernel", sources=["plm/_kernel.pyx"],
+                include_dirs=[numpy.get_include()])
+
+setup(
+    name="plm",
+    packages=["plm"],
+    ext_modules=cythonize([ext]),
+)

### 2014-08-14 documents/cpm.tex
title, authors, acks

--- 2013-11-15 documents/plm.tex
@@
 % This file is part of the causal-kepler project
-% Copyright 2013 the authors.
+% Copyright 2013, 2014 the authors.
 
@@
 \title{%
+  Self-calibration of time-domain imaging for exoplanet science, informed by causal structure%
+  \\ or \\
   A data-driven, pixel-level model to improve the precision of \Kepler\ photometry%
+  \\ or \\
+  Exploiting causal structure to create a data-driven self-calibration of \Kepler\ imaging%
 }
 \author{%
+  Dun~Wang\altaffilmark{\ref{CCPP}},
   Dan~Foreman-Mackey\altaffilmark{\ref{CCPP}},
-  David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{MPIA},\ref{email}},
-  Tom~Barclay\altaffilmark{\ref{Ames}},
-  Rob~Fergus\altaffilmark{\ref{Courant}},
-  Stefan~Harmeling\altaffilmark{\ref{MPIIS}},
+  David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{CDS},\ref{MPIA},\ref{email}},
   Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}},
@@
 }
-
 \newcounter{address}
@@
   Center for Cosmology and Particle Physics, Department of Physics, New York University}
+\altaffiltext{\theaddress}{\stepcounter{address}\label{CDS}%
+  Center for Data Science, New York University}
 \altaffiltext{\theaddress}{\stepcounter{address}\label{MPIA}%
@@
   To whom correspondence should be addressed; \texttt{<david.hogg@nyu.edu>}.}
-\altaffiltext{\theaddress}{\stepcounter{address}\label{Ames}%
-  NASA Ames Research Center}
-\altaffiltext{\theaddress}{\stepcounter{address}\label{Courant}%
-  Courant Institute of Mathematical Sciences, New York University}
+%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Ames}%
+%%   NASA Ames Research Center}
+%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Courant}%
+%%   Courant Institute of Mathematical Sciences, New York University}
 \altaffiltext{\theaddress}{\stepcounter{address}\label{MPIIS}%
@@
   Ruth~Angus (Oxford),
+  Tom~Barclay (Ames),
   Bekki~Dawson (Berkeley),
+  Rob~Fergus (NYU),
+  Stefan~Harmeling (Dusseldorf),
   Michael~Hirsch (UCL),
@@
 for valuable discussions, input, encouragement, and advice.
-This project was partially supported by NSF grant IIS-1124794 and NASA grant NNX12AI50G.
+This project was partially supported by
+  NSF grant IIS-1124794,
+  NASA grant NNX12AI50G.
+  the Moore Foundation,
+  and
+  the Sloan Foundation.
 This research made use of the NASA Astrophysics Data System.

### 2014-08-14 documents/cpm.tex
switch from PLM to CPM is a single change in the ms

@@
 \newcommand{\Kepler}{\project{Kepler}}
-\newcommand{\name}{PLM}
+\newcommand{\name}{CPM}
 \newcommand{\set}[1]{\mathcal{#1}}
@@
 \begin{abstract}
-The precision of \Kepler\ photometry%
-  ---the most precise photometric measurements of stars ever made---%
-  appears to be limited by unknown or untracked variations
-  in spacecraft pointing, point-spread function, stellar motions and parallaxes, and temperature.
+The precision of \Kepler\ photometry for exoplanet science---the most
+precise photometric measurements of stars ever made---appears to be
+limited by unknown or untracked variations in spacecraft pointing and
+temperature, and unmodeled stellar variability.
 Here we present \name,

### 2014-08-14 plm/gp_lc.py
lc level plm

@@ -1,0 +1,108 @@
+# -*- coding: utf-8 -*-
+
+from __future__ import division, print_function
+
+__all__ = ["load_system", "get_kernel"]
+
+import kplr
+import numpy as np
+from george import kernels
+from multiprocessing import Pool
+from emcee.autocorr import integrated_time
+
+from ._kernel import build_isotropic_kernel
+
+client = kplr.API()
+
+
+class IsotropicKernel(kernels.Kernel):
+
+    def __init__(self, amp, var, ndim=1):
+        super(IsotropicKernel, self).__init__(amp, var, ndim=ndim)
+
+    def set_pars(self, pars):
+        self._amp = pars[0]
+        self._factor = -0.5 / pars[1] ** 2
+
+    def __call__(self, x1, x2):
+        return build_isotropic_kernel(self._amp, self._factor, x1, x2)
+
+
+def load_light_curve(lc):
+    cols = ["TIME", "SAP_FLUX", "SAP_FLUX_ERR"]
+    data = lc.read(columns=cols)
+    return [np.array(data[c], dtype=np.float64) for c in cols]
+
+
+def load_system(kicid, quarter, month, radius=40, N=500, **kwargs):
+    # Load the target light curve.
+    star = client.star(kicid)
+    target_lc = client.light_curves(ktc_kepler_id=kicid,
+                                    sci_data_quarter=quarter,
+                                    ktc_target_type="LC", max_records=1)[0]
+    t, f, fe = load_light_curve(target_lc)
+
+    # Find the n-th month of data.
+    m = np.isfinite(t)
+    month_gaps = np.concatenate([[t[m].min()],
+                                 np.sort(t[m][np.argsort(np.diff(t[m]))[-2:]]),
+                                 [t[m].max()]])
+    tmn, tmx = month_gaps[month], month_gaps[month+1]
+    time_mask = np.isfinite(t)
+    time_mask[m] *= (tmn <= t[m]) * (t[m] <= tmx)
+    t, f, fe = t[time_mask], f[time_mask], fe[time_mask]
+
+    # Interpolate missing data.
+    m = np.isfinite(f)
+    f[~m] = np.interp(t[~m], t[m], f[m])
+    fe[~m] = np.mean(fe[m])
+
+    # Load the predictor light curves.
+    q = dict(
[…]

### 2014-08-14 plm/solvers.py

@@ -5,7 +5,7 @@ from __future__ import division, print_function
 __all__ = ["linear_least_squares"]
 
 import numpy as np
-from scipy import linalg
+from scipy.linalg import cho_factor, cho_solve
 
 
 def linear_least_squares(A, y, yvar=None, l2=None):
@@ -48,5 +48,15 @@ def linear_least_squares(A, y, yvar=None, l2=None):
         ATA[np.diag_indices_from(ATA)] += l2
 
     # Solve the equations overwriting the temporary arrays for speed.
-    factor = linalg.cho_factor(ATA, overwrite_a=True)
-    return linalg.cho_solve(factor, np.dot(AT, Ciy), overwrite_b=True)
+    factor = cho_factor(ATA, overwrite_a=True)
+    return cho_solve(factor, np.dot(AT, Ciy), overwrite_b=True)
+
+
+def compute_kernel_matrix(kernel, x, yerr):
+    K = kernel(x, x)
+    return K
+
+
+def gp_predict(kxx, kxs, y):
+    factor = cho_factor(kxx)
+    return np.dot(kxs, cho_solve(factor, y))

### 2014-08-14 run.py

@@ -5,55 +5,106 @@ from __future__ import division, print_function
 
 __all__ = []
 
-import george
+import time
 import numpy as np
+import cPickle as pickle
 import matplotlib.pyplot as pl
+from itertools import imap, izip
+from IPython.parallel import Client
+
 from plm.data import Dataset, IsotropicKernel
-from plm.solvers import linear_least_squares
+from plm.solvers import compute_kernel_matrix
+
+
+def predict(args):
+    import numpy as np
+    from plm.solvers import linear_least_squares, gp_predict
+
+    t0, pred = args
+    m = np.fabs(t - t0) > window
+    w = linear_least_squares(x[m], y[m], yvar=yerr[m]**2, l2=1e5)
+    mu_lin = np.dot(x[pred], w)
+    mu_gp = gp_predict(Kobs[m][:, m], K[pred][:, m], y[m])
+    return float(mu_lin), float(mu_gp)
 
 
 if __name__ == "__main__":
-    # kicid = 5088536
-    # quarter = 5
-    # npred = 20
-    # dataset = Dataset(kicid, quarter, npred)
-    # dataset.build_matrix()
-    # dataset.save("dataset.pkl")
+    if False:
+        kicid = 5088536
+        quarter = 5
+        npred = 100
+        dataset = Dataset(kicid, quarter, npred, poly=2)
+        dataset.build_matrix()
+        dataset.save("dataset.pkl")
+    else:
+        dataset = Dataset.load("dataset.pkl")
 
-    dataset = Dataset.load("dataset.pkl")
+    # Choose the brightest pixel.
+    pixel = np.argmax(np.median(dataset.targ_flux, axis=0))
+    t = dataset.time
+    x = dataset.matrix
+    y = dataset.targ_flux[:, pixel]
+    yerr = dataset.targ_flux_err[:, pixel]
 
-    print(dataset.matrix.shape, dataset.targ_flux.shape)
+    # Injection.
+    depth = 0.05 ** 2
+    y[np.abs(t - 460) < 0.3] *= 1.0 - depth
 
-    m = np.ones_like(dataset.time, dtype=bool)
-    m[int(0.4*len(dataset.time)):int(0.6*len(dataset.time))] = False
-    print(m)
+    if False:
+        # Estimate hyperparameters and set up the kernel.
+        i = np.random.randint(len(dataset.time), size=500)
[…]

### 2014-08-14 setup.py

@@ -8,9 +8,13 @@ from setuptools import setup, Extension
 # Set up the extension.
 ext = Extension("plm._kernel", sources=["plm/_kernel.pyx"],
                 include_dirs=[numpy.get_include()])
+ext2 = Extension("plm._gp", sources=["plm/_gp.pyx", "plm/gp.cc"],
+                 include_dirs=["gp",
+                               numpy.get_include(),
+                               "/usr/local/include/eigen3"])
 
 setup(
     name="plm",
     packages=["plm"],
-    ext_modules=cythonize([ext]),
+    ext_modules=cythonize([ext, ext2]),
 )

### 2015-02-23 cpm.tex
checked

--- 2014-08-14 documents/cpm.tex
@@
 
+% # to-do
+% - write causal description
+
 \documentclass[12pt, preprint]{aastex}
+
+\usepackage{graphicx}
+\usepackage{caption} 
+\usepackage{subcaption}
+
+\usepackage{hyperref}
+\usepackage{url}
+
+\graphicspath{{figures/}}
 
@@
 
-\title{%
-  Self-calibration of time-domain imaging for exoplanet science, informed by causal structure%
-  \\ or \\
-  A data-driven, pixel-level model to improve the precision of \Kepler\ photometry%
-  \\ or \\
-  Exploiting causal structure to create a data-driven self-calibration of \Kepler\ imaging%
+\title{
+  Calibrating the pixel-level Kepler imaging data with a causal data-driven model
+ \\ 
 }
@@
   To whom correspondence should be addressed; \texttt{<david.hogg@nyu.edu>}.}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Ames}%
-%%   NASA Ames Research Center}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Courant}%
-%%   Courant Institute of Mathematical Sciences, New York University}
 \altaffiltext{\theaddress}{\stepcounter{address}\label{MPIIS}%
   Max-Planck-Institut f\"ur Intelligente Systeme, T\"ubingen}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Oxford}%
-%%   Department of Physics, Oxford University}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{CfA}%
-%%   Harvard--Smithsonian Center for Astrophysics}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{UCL}%
-%%   Department of Physics and Astronomy, University College London}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{CMU}%
-%%   McWilliams Center for Cosmology, Carnegie Mellon University}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Caltech}%
-%%   Department of Astronomy, California Institute of Technology}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Columbia}%
-%%   Department of Astronomy, Columbia University}
 
 \begin{abstract}
-The precision of \Kepler\ photometry for exoplanet science---the most
-precise photometric measurements of stars ever made---appears to be
-limited by unknown or untracked variations in spacecraft pointing and
-temperature, and unmodeled stellar variability.
-Here we present \name,
-  a data-driven model of these variations in \Kepler\ data (or really of their impact on the photometry).
-Importantly (and uniquely),
-  \name\ works at the pixel level (not the photometric measurement level);
-  it can capture more fine-grained information about the variation of the spacecraft
-  (especially regarding pointing and point-spread function)
-  than is available in the pixel-summed photometry.
-\name\ is extreme in that it has enormous flexibility and it only uses data (and meta-data) to predict data:
-\name\ provides a prediction for each readout pixel built from a linear combination of the readouts
-  from very large numbers of nearby pixels (plus some spacecraft information);
-  the choice of nearby pixels is guided by ideas from causal inference.
-\name\ avoids over-fitting by employing a train-and-test formalism
-  designed to ensure that transit-like photometric events and short-timescale stellar variability
-  cannot be captured or distorted by the model;
-  it is designed to remove spacecraft-induced variability but not intrinsic stellar variability.
-We show that \name\ outperforms the \Kepler\ Presearch (\sic) Data Conditioning method on a set of example stars.
-We release open-source code that provides \name\ output for any star in the existing \Kepler\ Archive,
-  and we discuss applications for other missions,
-  including any possible \Kepler\ two-wheel mission.
+In general, astronomical observations are affected by several kinds of noise, each with it's own causal source; there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope.
+In particular, the precision of NASA Kepler photometry for exoplanet science—the most precise photometric measurements of stars ever made—appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, and unmodeled stellar variability.
+Here we present the Causal Pixel Model (CPM) for Kepler data, a data-driven model intended to capture variability but preserve transit signals.
+The CPM works at the pixel level (not the photometric measurement level); it can capture more fine-grained information about the variation of the spacecraft than is available in the pixel-summed aperture photometry.
+The basic idea is that CPM predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities while not containing any information on possible transits at the target star.
+In addition, we use the target star’s future and past (auto-regression).
+By appropriately separating the data into training and test sets, we ensure that information about any transit will be perfectly isolated from the fitting of the model.
+The method has four hyper-parameters (the number of predictor stars, the auto-regressive window size, and two L2-regularization amplitudes for model components), which we set by cross-validation.
+We determine a generic set of hyper-parameters that works well on most of the stars and apply the method to a corresponding set of target stars.
+For these stars, we calculate the Combined Differential Photometric Precision (CDPP), which indicate the noise level of a certain time scale.
+We find that we can consistently outperform (for the purposes of exoplanet detection) the Kepler Pre-search Data Conditioning (PDC) method for exoplanet discovery.
+
 \end{abstract}
@@
   through strong regularization and a train-and-test framework, and
-  (3)~that when \name\ fits a star, there is no possibility of any contribution of the star itself to the fit basis vectors.
+  (3)~that purpose of the \name\ is to search for exoplanets, so in \name, intrinsic stellar
+  variability is also removed as well as the systematics.
 The two methods (\name\ and PDC) are similar however,
@@
 
-\section{Data-driven models}
+\section{Causal data-driven model}
 
@@
   lead to different structures for the data-driven model.
-For example, in the case of \Kepler\ data,
-  if we believe that different stars in the \Kepler\ field vary independently
-  (that is, are not physically synchronized in any way),
-  then the only reason that one star might show variability that is strongly \emph{predictive}
-  (useful for prediction) of another star's variability
+In the case of \Kepler\ data, if we examine two arbitrary stars far away from each other 
+on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light curve time 
+series), we can obviously see that the two stars that are hundreds pixel away from each 
+other do have similar trends. If we believe that different stars in the \Kepler\ field vary 
+independently (that is, are not physically synchronized in any way) because of the 
+distance between them, then the only reason that one star might show variability that is strongly \emph{predictive} (useful for prediction) of another star's variability
   is that both stars are being observed by the same device or spacecraft.
@@
   inasmuch as spacecraft issues imprint on both stars in related ways;
-  they share a common cause.
+  they share a common cause---the systematics.  
 For another example, if we think the spacecraft is being affected by
@@
   (for example, thermal processes),
-  then it would be sensible to model the data at time $t$ using not just simultaneous data,
-  but also data from a range of times around $t$.
+  then it would be sensible to model the data at time $t$ using not just simultaneous data, but also data from a range of times around $t$.
 For another example, if an investigator doesn't care about preserving stellar variability,
@@
   but also intrinsic stellar variability,
-  the predictive model will be permitted to use as input pixels that \emph{do} overlap the target star.
-In what follows, we are only going to use input data that do not overlap that target star pixels.
-These models ought to remove spacecraft variability but not intrinsic stellar variability.
+  the predictive model will be permitted to use as input pixels that \emph{do} overlap the 
+  target star.
+In what follows, we are going to use input data both from pixels of other stars and the  
+target star pixels' past and furture.
+These models ought to remove both spacecraft variability and intrinsic stellar variability, 
+which is optimal for exoplanet transit searching.
+
+\begin{figure}[htb]
+\centering
+\begin{subfigure}[htb]{0.48\columnwidth}
+\includegraphics[width=\columnwidth]{5088536-5}
+\caption{}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.48\columnwidth}
+\includegraphics[width=\columnwidth]{5949551-5}
+\caption{}
+\end{subfigure}
+\caption{\label{ccd} Stars on the same CCD share systematic errors.
+The two panels show pixel fluxes (brightnesses) for two stars: (a) KIC 5088536, (b) KIC 5949551; here, KIC stands for Kepler Input Catalog.
+Both stars lie on the same CCD (see Fig.~\ref{fig1}), but far enough apart such that there is no stray light from one affecting the other.
+Each panel shows the pixels contributing to the respective star.
+Note that there exist similar trends in these two stars, caused by systematic errors.
+%The idea of our approach is to predict each pixel from a set of pixels from other stars in order to remove those systematics.
+}
+\end{figure}
 
@@
 
-In addition, each training data set within which we set the parameters (by optimization) has a finite total time extent $t_{\max}\approx 90$\,d.
+In addition, each training data set within which we set the parameters (by optimization) has a finite total time extent $t_{\max}\approx 30$\,d.
 The train-and-test framework, which includes data out to time $t_{\max}$ but excludes data within $\Delta t$ of the test data,
@@
 
-In the context of this project, the quantities of interest are the light-curves
-  (photometry as a function of time or apparent flux as a function of time)
-  for every star.
-What we get, for every star, from the data-driven model, is a train-and-test prediction
-  for the brightness of every pixel in the patch of the detector relevant to the star,
-  along with the residual, or the difference between the measured read-out pixel value and the prediction (data minus prediction).
-What will be called the ``\name\ photometry'' in what follows is constructed from what will be called the ``\name\ pixels''.
-The \name\ photometry is constructed from the \name\ pixels
-  just as the \Kepler\ official SAP photometry is constructed from the \Kepler\ Target Pixel Files;
-  that is, by summing pre-defined sets of pixels (with unit weights; see above and below for criticism of this).
-The \name\ pixels are constructed from the data-driven model predictions by taking,
-  for each pixel in each contiguous data segment (see below),
-  the \emph{mean} predicted pixel value (mean over time),
-  and adding to it the residuals (data minus prediction) away from the data-driven model prediction.
-These \name\ pixels are ``calibrated'' pixels,
-  in that the data-driven model has been used to fit out all the variability it can,
-  subject to the restrictions imposed by its finite freedom and the train-and-test specification.
-The signal---in which exoplanet transits will be found---is fundamentally the observed residual away from this prediction,
-  but it has to be added back into the mean prediction to have the right ``baseline'' or zero level.
-In short, \name\ will produce prediction pixels, residual pixels, \name\ pixels (mean prediction plus residual),
-  and aperture-based \name\ photometry analogous to the SAP photometry.
-
 Finally, the fifth general idea is that there is no objective \emph{ground truth} against which we can tell
@@
   artificial exoplanet transit signals injected into real \Kepler\ pixel-level data.
-We can also show that it produces stellar light-curves that look sensible for known variable stars.
-We cannot yet show that it is optimal for our long-term goals,
-  nor can we show that it produces pixelss or light-curves that are more accurately calibrated;
-  we will only show promising properties of the \name\ outputs.
+  and promising properties of the \name\ outputs.
 In the end, the value of the \name\ will be demonstrated by the scientific projects it enables.
@@
 \section{\name\ specification and hyper-parameters}
-
-Each individual \Kepler\ target star is, for each quarter (each 90-ish-day period),
+\subsection{\name\ model}
+Each individual \Kepler\ target star is, for each month (here we always use data per month rather than quarter,  
+since there is discontinuity between every 30-ish-day period),
   on a particular CCD on the \Kepler\ focal plane.
@@
 
-Let's consider a particular pixel $m$ in the focal plane in one particular quarter.
-In that quarter, the spacecraft delivers $N\sim 4000$ measurements $I_{mn}$
-  of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the quarter.
+Let's consider a particular pixel $m$ in the focal plane in one particular month.
+In that quarter, the spacecraft delivers $N\sim 1300$ measurements $I_{mn}$
+  of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the month.
 (For intensity measurements $I_{mn}$ here we are using pixels from the Target Pixel Files.)
@@
 Somewhat arbitrarily,
-  we choose all the pixels $m'$ associated with the $Q=5$ stars on the same CCD in the same quarter
+  we choose all the pixels $m'$ associated with the $Q$ stars on the same CCD in the same quarter
   that are closest in magnitude
@@
   is the \emph{pixel set} $\set{M}_m$ associated with pixel $m$.
+   To rule out any direct optical cross-talk by stray
+light, we require that the predictor pixels are from stars
+sufficiently far away from the target star (at least 20 pixels
+distance on the CCD).
 Note that because the set $\set{M}_m$ is of pixels associated with \emph{different} stars
-  than the star associated with pixel $m$,
+  than the star associated with pixel $m$, and are far from it on CCD, 
   the pixel $m$ will not be in the set $\set{M}_m$,
@@
   but we don't even use any times $t$ such that $|t-t_n| < \Delta t$,
-  where $\Delta t\sim 12$\,h.
+  where $\Delta t\sim 10$\,h as shown in Fig.~\ref{train-and-test}.
 That is, we train (optimize fit parameters) using the \emph{time set} $\set{N}_n$ of time
@@
 
-\todo{DFM: Do we want a schematic figure or cartoon which illustrates all of this?}
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\columnwidth]{train_and_test}
+\caption{\label{train-and-test} Train-and-test framework. Data near the target point $t_{n}$ within $\Delta t$ is excluded in the training set}
+\end{figure}
 
-In addition to the other data (from pixels $m'\in\set{M}_m$ and taken at time points $n'\in\set{N}_n$)
-  used to make each prediction, we will use also some \emph{meta-data};
-  these include the time itself $t_n$,
-  the sine and cosine of the parallactic angle $\theta(t_n)$,
-  and the dot product $\hat{n}\cdot v(t_n)$ of the spacecraft velocity $v(t_n)$
-  with the direction $\hat{n}$ towards the \Kepler\ field center.
-These additional meta-data variables permit the data-driven model
-  to capture easily variations induced in the data
-  by proper motions, parallaxes, and stellar aberration.
-Symbolically, we will denote these $K=4$ pieces of meta-data $d_{kn}$.
+In addition to pixel set $m'\in\set{M}_m$ from other stars,  we also include
+past and future of the target star --- autoregressive (AR) component as input to remove 
+more of the stellar variability and thus increase the sensitivity for transits. To do this, 
+we select an exclusion window of half-width $\Delta t$ including R data points, 
+where $\Delta t\sim 10$ (as big 
+as the window in train-and-test framework) around the point of time $t_{n}$ being 
+corrected, to ensure that we do not remove the transit itself and then use S closest 
+future and past time points. That is, for every pixel m in the target star , we construct S virtual time series, in which every component v is defined to be     
+\begin{eqnarray}
+I_{vn} = I_{mn-R-k}\ or\ I_{vn} = I_{mn+R+k},
+\quad,
+\end{eqnarray}
+where k = 0, 1, ..., S, so if there are totally M pixels in the target stars, we will finally add 
+$2\cdot M\cdot S$ autoregressive components into the predictors,  which construct the autoregressive set $\set{V}_m$
 
@@
 \\
-I^{\ast}_{mn}  &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m'n} + \sum_{k=1}^{K} b_{mnk}\,d_{kn}
+I^{\ast}_{mn}  &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m'n} + \sum_{v\in\set{V}_m} b_{mnv}\,I_{vn}
 \quad,
@@
 \chi^2_{mn}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{mn'} - I^{\ast}_{mnn'}]^2}{\sigma^2_{mn'}}
-                 + \sum_{m'\in\set{M}_m} \frac{a_{mnm'}^2}{\Sigma^2}
+                 + \lambda_{a}\sum_{m'\in\set{M}_m}a_{mnm'}^2 + \lambda_{b}\sum_{v\in\set{V}_m}b_{mnv}^2
 \\
-I^{\ast}_{mnn'} &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m'n'} + \sum_{k=1}^{K} b_{mnk}\,d_{kn'}
+I^{\ast}_{mnn'} &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m'n'} + \sum_{v\in\set{V}_m} b_{mnv}\,I_{vn'}
 \quad,
@@
 where the $\sigma^2_{mn'}$ are the (presumed known) individual-pixel noise variances,
-  and $\Sigma^2$ sets the strength of the regularization (or width of the prior pdf).
-Although the variances $\sigma^2_{mn'}$ are in principle different for every time step $n'$,
-  for nearly-constant stars in good data, there is not much variation;
-  in what follows, we treat these uncertainties as fixed at
-  \todo{DFM: some mean value (we can't ignore this,
-   because it ``plays off against'' the regularization)}
-The regularization variance $\Sigma^2$ we set to 0.3 (\todo{DFM TAKE NOTE; that's about 10 for the parameter you usually use.})
-  because we expect almost all the coefficients $a_{mnm'}$ to be less than unity in magnitude.
-We do not regularize the meta-data coefficients $b_{mnk}$,
-  because we want the model to make use of the (easily interpretable) meta-data coefficients as much as possible.
+  and $\lambda_{a}$, $\lambda_{b}$ set the strength of the regularization (or width of the prior pdf) for parameters $a_{mnm'}, b_{mnv}$.
 
@@
   we are using only time points $n'\in\set{N}_n$ that don't overlap the target (or test) time point $n$.
-We train the model---that is, set the parameters $a_{mnm'}$ and $b_{mnk}$---%
+We train the model---that is, set the parameters $a_{mnm'}$ and $b_{mnv}$---%
   by choosing the full set of parameters that jointly minimize the objective function $\chi^2_{mn}$.
@@
 
-For this reason---\emph{so many solves}---%
-  we do \todo{some crazy clever stuff} to make this work fast;
-  \todo{DFM implementation notes here}.
-
-Once we have obtained the parameters $a_{mnm'}$ corresponding to a particular data point $I_{mn}$,
-  we can make a \emph{prediction} $I^{\ast}_{mnn}$ for the intensity at that pixel.
+Once we have obtained the parameters $a_{mnm'}$ and $b_{mnv}$ corresponding to a particular data point $I_{mn}$,
+  we can make a \emph{prediction} $I^{\ast}_{mn}$ for the intensity at that pixel.
 By construction of our objective function, this is truly a prediction,
@@
   (as described above).
-In addition to the predicted pixel value $I^{\ast}_{mnn}$,
-  we can also construct a \emph{residual} $\delta_{mn}$ (data minus prediction),
-  defined by
-\begin{eqnarray}
-\delta_{mn} &\equiv& I_{mn} - I^{\ast}_{mnn}
-\quad .
-\end{eqnarray}
-
-In some sense, it is this residual that contains the exoplanet transit signals we seek.
-That is, a transit creates a negative residual away from the prediction.
-So far, however, the model is a model of \emph{pixels},
-  and we need to obtain from this model \emph{photometric measurements} of stars.
-In order to construct stellar photometry measurements out of the residual pixels $\delta_{mn}$,
-  we add into each pixel residual $\delta_{mn}$ the \emph{mean predicted intensity} $\bar{I}^{\ast}_m$
-\begin{eqnarray}
-\bar{I}^{\ast}_m &=& \frac{1}{N_m}\,\sum_n I^{\ast}_{mnn}
-\quad ,
-\end{eqnarray}
-where $N_m$ is the number of time steps in the quarter,
-  and the sum is over those time steps.
-\todo{DFM: Should we use mean or median here?}
-We construct what we will call ``the \name\ pixels'' $J_{mn}$,
-  which are the residuals plus the mean, or
-\begin{eqnarray}
-J_{mn} &=& \delta_{mn} + \bar{I}^{\ast}_m
-\quad .
-\end{eqnarray}
-That is, we treat each pixel as differing from constant intensity
-  only inasmuch as it has residuals away from the model prediction.
-
-Our new stellar flux estimates,
-  what we will call the ``\name\ photometry'',
+  With all the predicted pixel values $I^{\ast}_{mn}$ of the target star,  
+  our new stellar flux estimates,
+  what we will call the ``\name\ prediction'',
   is constructed from the \name\ pixels
@@
   is constructed from the Target Pixel Files.
-That is, we perform a weighted sum of \name\ pixels $J_{mn}$ with weights $w_m$,
+That is, we perform a weighted sum of \name\ predicted pixels $I^{\ast}_{mn}$ with weights $w_m$,
   all of which are either zero or unity,
@@
 \begin{eqnarray}
-S_n = \frac{1}{M}\,\sum_m w_m\,J_{mn}
+S_n = \sum_m w_m\,I^{\ast}_{mn}
 \quad ,
@@
 
-Some---or probably most---of the variations of the pixel intensities
-  are being caused by small changes to stellar positions relative to the detector,
-  in turn caused by pointing drifts, parallaxes, proper motions, aberration, and temperature changes.
-The \name\ pixels, being constructed from a mean prediction plus residuals,
-  represent some kind of mean image, averaged over these positional changes.
-  that is, the image constructed from the \name\ pixels would have a broader
-  point-spread function than any individual time-step,
-  and does not necessarily represent any true astronomical scene.
-This is another consequence of the point, discussed above,
-  that data-driven models do not in general provide interpretable results.
-This uninterpretability creates a small problem,
-  which is that the optimization by which the \Kepler\ team chose the pixel weights $w_m$
-  cannot be precisely appropriate for the \name\ pixels,
-  even if it \emph{is} appropriate for the \Kepler\ Target Pixel Files.
-That is, there could be a small sacrifice at this step in photometric estimator quality.
-This motivates future work on photometric estimation.
-That said, we don't expect this effect to be large,
-  because the positional drifts involved are orders of magnitude smaller than a pixel.
+It is worth to mention that the \name\ prediction $S_{n}$ is constructed from pixels without any transit information. Therefore, it can be regarded as a light curve without
+signal. Based on this idea, we can construct the ``\name\ flux'' to be the relative residual
+between \name\ prediction and SAP Flux $F_{n}$
+\begin{eqnarray}
+\delta_{n}&\equiv&\frac{F_{n} - S_{n}}{S_{n}}
+\quad .
+\end{eqnarray}
+The \name\ flux is 
+In some sense, it is this relative residual that contains the exoplanet transit signals we 
+seek. That is, a transit creates a negative residual away from the prediction.
 
-\todo{DFM: What does the interface look like?  What are the run times and so on?}
+\subsection{Hyper-parameters}
+In the description of \name, we introduce 4 hyper-parameters---number of predictor 
+stars Q (or number of predictor pixels P), number of autoregressive components S, and 
+the two regularization strength
+$\lambda_{a}$ and $\lambda_{b}$. To set these 4 hyper-parameters, in principle we 
+need to run cross-validation on every single stars to optimize the performance of \name.
+But optimizing in this 4-dimensional space is expensive, especially in \name\ we need 
+to solve thousands of linear system with thousands of parameters. Therefore, in this 
+paper we just set a general set of hyper-parameters ($P=4000$, $Q=3$, $
+\lambda_a=1e5$, $\lambda_a=1e5$) which works well in most of the stars without
+highly variability. To show how this general set of hyper-parameters performs, here we 
+present a typical comparison between optimized and default hyper-parameters in 
+Fig~\ref{hyperparameter}. We can see that, in Fig~\ref{hyperparameter}, there is less variation in the \name\ flux from optimized hyper-parameters 
+(green points in second panel) than from the default one 
+(red points in the bottom panel). In addition, the optimized flux has higher signal to 
+noise ratio of the known transit than the default. 
+However, the performance of default hyper-parameters is acceptable and we will use  
+this set of hyper-parameters throughout rest of the paper to show the general 
+performance of \name.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=\columnwidth]{compare_10187017}
+\caption{\label{hyperparameter} Comparsion between default and optimized hyper-parameters.
+The three panels plot show the results from default, In the top panel, SAP flux is plotted in black, CPM prediction of default hyper parameters is in red line, \name prediction of optimized hyper-parameters is in green line.
+The middle panel shows the CPM flux of the optimized hyper-parameters, while the bottom is the CPM flux of the default hyper-parameters, the two vertical blue lines indicate the location of the transit signal,  and signal to noise ratio is calculated in both situation.
+The optimized hyper-parameter performs better than the Default one, but the results from both situation are close.
+}
+\end{figure}
+
+\clearpage
+
+\subsection{Transit signal in \name}
+One important feature of \name\ is that we use the train-and-test framework to preserve 
+the transit signal. To show how well train-and-test framework performs, we make the
+following experiments on \Kepler\ data as shown in Fig~\ref{distortion}
+In the light curve of single pixel (1, 2) of KIC 9822284, a 10-hrs fake signal 
+with amplitude 1.0005 is inserted. To insert the signal, we simply multiply the light curve 
+by the factor of 1.0005, which makes the little bump in the middle of the SAP light curve 
+(black points in the first panel). With the distorted light curve, we both applied the 
+\name\ and ordinary fitting to the data. In the result, we can see that both \name and 
+ordinary fit the light curve quite well outside the range of inserted signal. However, 
+when examine how these two models preserve the signal that we care, the ordinary
+fitting fit out about 30 percent of the signal, while \name\ almost preserve the whole 
+original amplitude. Therefore,  by this simple experiment, we are able to show that 
+the train-and-test framework used here is capable to keep the transit signal with 
+a particular time scale. And we want to emphasise that it is crucial for searching for
+exoplanets, especially the small ones such as earth-like planets, which only have  
+about tens of parts per million signal in the light curve.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=\columnwidth]{distortion_9822284_normal}
+\caption{\label{distortion} CPM preserves transit signals.
+Fake signal with amplitude 1.0005 is inserted into the single pixel (1, 2) of star KIC 9822284.
+In the top panel, the black points shows the SAP flux of the pixel with the injected signal, the green line is the fitting of the SAP flux, and the red line is the CPM prediction.
+In the bottom panel, red and green points represent the CPM flux and fit flux, while the signal value is indicated by the horizontal line.
+CPM largely preserves the signal while the fitting flux overfit the signal.}
+\end{figure}
+
+\clearpage
 
@@
 
-For each example, give the code and show the output and provide some discussion.
+To give a view on how our method performs, \name\ is applied on several stars with 
+known transit signals with different variability and magnitudes 
+as shown in Fig.~\ref{fluxes}. From the plots, we can see that \name\ works quite well
+on these stars,  producing the \name\ fluxes with low variation and preserving the transit
+signals.
+In addition, we compare 6 quiet stars (non-variable stars) with the 
+PDC method The results illustrate that for these quiet stars our approach removes 
+a major part of the variability present in the PDC light curves, while preserving the transit signals. 
+To provide a quantitative comparison, we ran CPM on 1000 stars from the whole Kepler input catalog (500 chosen randomly from the whole list, and 500 random G-type sun-like stars), and estimate the Combined Differential Photometric Precision (CDPP) for CPM and PDC (before CDPP is estimated, the 100 most variable stars in the list are
+removed, since PDC is not designed to remove stellar variability).
+CDPP is an estimate of the relative precision in a time window, indicating the noise level seen by a transit signal with a given duration.
+The duration is typically chosen to be 3, 6, or 12 hours.
+We use the 12-hours CDPP metric, since the transit duration of an earth-like planet is roughly 10 hours.
+Fig.~\ref{cdpp} presents our CDPP comparison of CPM and PDC, showing that our method (CPM) outperforms PDC.
 
-We need a metric for comparing outputs.
-For now lets try plotting the power spectrum of the SAP, PDC, and \name\ photometry for each star.
+\begin{figure}[htb]
+\centering
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_11295426_pdc}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_11401755_pdc}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_5966154_pdc}
+\end{subfigure}
 
-So DWH is imagining multi-panel plots: SAP, PDC, and \name\ vs time,
-  plus a power-spectrum plot vs frequency.
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_3544595_pdc}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_4914423_pdc}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_9892816_pdc}
+\end{subfigure}
 
-Cases ought to include
-\begin{itemize}
-\item a bright, non-variable G star with an Earth injection,
-\item a significant variable like that shown in the white paper, and
-\item a star with a bad quarter or where \Kepler\ sucked it.
-\end{itemize}
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_8866102}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_5695396}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_9950612}
+\end{subfigure}
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_8292840}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_9451706}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_6677841}
+\end{subfigure}
 
-Then we want to show some kind of scatter plot, which is some variance estimate from us,
-  vs the same estimate from the PDC,
-  to show that we always or usually win.
-This variance estimate should be something like the power in the residuals at frequencies
-  corresponding to 30-hour periods or maybe 50-hour periods or something like that.
+\caption{\label{fluxes} Corrected fluxes using \name, for 12 example stars, spanning the main magnitude (brightness) range encountered.
+In first column plots,   we consider bright stars with magnitude from 9 to 10.5, second cloumn are stars with magnitude from 11 to 12.5,  and the third column are faint stars with magnitude above 13.
+In the first two rows, we present some quiet stars.
+In all three panels, the top panel shows the SAP flux (black) and the CPM regression (red), i.e., our prediction of the star from other stars.
+The middle panel shows the CPM flux corrected using the regression, and the bottom shows the PDC flux.
+One can see that the CPM flux curve preserves the exoplanet transits (little downward spikes), while removing a substantial part of the variability present in the PDC flux.
+Both the bottom two rows present some variable stars with slow and fast variability.
+For the variable stars, we did not present the PDC
+comparison, since the PDC flux try to preserve intrinsic steller variability.}
+\end{figure}
+
+\begin{figure*}[htb]
+\centering
+\begin{subfigure}[htb]{0.33\columnwidth}
+\includegraphics[width=\columnwidth]{pdc_cdpp12_r}
+\caption{}
+\end{subfigure}%
+%\hfill
+\begin{subfigure}[htb]{0.33\columnwidth}
+\includegraphics[width=\columnwidth]{boxplot_r}
+\caption{}
+\end{subfigure}%
+%\hfill
+\begin{subfigure}[htb]{0.33\columnwidth}
+\includegraphics[width=\columnwidth]{pdc_cdpp12_hist_r100}
+\caption{}
+\end{subfigure}
+\caption{\label{cdpp} Comparison of the proposed method (CPM) to the Kepler Pre-search Data Conditioning (PDC) method in terms of Combined Differential Photometric Precision (CDPP) (see text).
+Plot (a) shows our performance (red) vs.\ the PDC performance in a scatter plot, as a function of star magnitude (note that larger magnitude means fainter stars, and smaller values of CDPP indicate a higher quality as measured by CDPP.
+Plot (b) bins the same dataset and shows box plots within each bin, indicating median, top quartile and bottom quartile.
+The red box corresponds to CPM, while the black box refers to PDC.
+Plot (c), finally, shows a histogram of CDPP values.
+Note that the red histogram has more mass towards the left, i.e., smaller values of CDPP, indicating that our method overall outperforms PDC, the Kepler ``gold standard.''
+}
+\end{figure*}
+
+\clearpage
 
 \section{Discussion}
+We have presented a a simple yet highly effective method that works in pixel-level based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ light curves, which is intended to search
+exoplanets. However, based on our assumption of the causal structure of the \Kepler 
+data, if we turn off the auto-regressive components and keep the predictors from other
+stars working  in the \name, we should be able to still remove the systematics while
+preserve the intrinsic stellar  variability, since there is no reason that these independent
+stars can be used to predict the stellar variability of the target star. However, in fact, we
+can not preserve the stellar variability just by turning off the auto-regressive 
+components. One possible reason can be that, since our model is so flexible 
+(thousands of parameters), in principle it can fit any functions. In this sense, we should 
+run cross-validation with the auto-regressive components turned off and to find out how
+many pixels from other stars we need to just remove systematics while preserve stellar
+variability, but in fact we do not have a good criterion to check how well we preserve
+stellar variability in cross-validation because we do not have enough knowledge of the 
+true stellar variability. Thus for the time being, we just focus on producing well-
+calibrated light curves for searching exoplanets, but in long term, we are looking
+forward to find a method to preserve the stellar variability.
 
-Return to the SAP photometry ``unweighted sum'' issue here.
-
-Didn't do anything about short-cadence data; suck it up.
-
-Lots of quantitative and qualitative choices that ought to be explored.
-These include what and what and what and what?
-How \emph{ought we} make all these choices?
-
-Not the least of these is linearity; deep learning and so on.
-
-The potential for autoregressive models.  Cite the white paper.
-
-The weakest point is construction of photometry from the model plus residuals;
-  interesting whether the output of the model can be interrogated
-  to provide value for those building physical models.
+However, forget all the unsolved problems, we expect that our method will enable
+astronomical discoveries at higher sensitivity on the existing \Kepler data as well as on
+future missions.  As we know, \Kepler K2 data are suffering from the broken-down of
+reaction wheels, which makes the satellite hard to control and introduce significant
+systematics. Moreover, in 2017, NASA is planning the launch of another space 
+telescope---TESS (Transiting Exoplanet Survey Satellite), which will perform an all-sky 
+survey for small (earth-like) planets of nearby M stars. We think our method can be simply
+extended for these project to help achieving higher precession and more scientific results.
 
@@
 
-\todo{White-paper Authors:  Feel free to contribute to this paper and move from the ack list to the author list.}
-
 \clearpage
-\begin{figure}
-~ % DFM: replace this ~ with a figure
-\caption{A patch of \Kepler\ pixels from the Target Pixel Files
-  from \todo{XXX quarter}, centered on \todo{YYY target}.
-  In the top panel, each box represents a pixel.
-  Within each box is shown the light-curve of that pixel over the quarter.
-  In the bottom panel, the SAP photometry for this target is shown;
-  the SAP photometry is based on a straight sum of the pixels marked with darker borders.
-  Note that every pixel varies substantially but the total SAP photometry is better than any individual pixel.
-  Note also that the pixel variations are strongly inter-related.\label{fig:pixelpatch}}
-\end{figure}
-
-\clearpage
-\begin{figure}
-~ % DFM: replace this ~ with a figure
-\caption{One quarter of photometric data for star \todo{KIC XXX}.
-  The top panel shows the \Kepler\ SAP photometry;
-    the vertical axis is \todo{something like median-divided brightness}
-    and the horizontal axis is \todo{something like KBJD}.
-  The next panel shows the \Kepler\ PDC photometry.
-  The next shows the \name\ photometry.
-  The bottom panel shows the power spectra of the three lightcurves.\label{fig:example1}}
-\end{figure}
 

### 2015-02-24 cpm.tex
test commit, only correcting a typo

@@
 \begin{abstract}
-In general, astronomical observations are affected by several kinds of noise, each with it's own causal source; there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope.
+In general, astronomical observations are affected by several kinds of noise, each with its own causal source; there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope.
 In particular, the precision of NASA Kepler photometry for exoplanet science—the most precise photometric measurements of stars ever made—appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, and unmodeled stellar variability.

### 2015-02-24 cpm.tex
typo
typos

@@
 \usepackage{url}
+
+\usepackage{natbib}
 
@@
 \begin{abstract}
-In general, astronomical observations are affected by several kinds of noise, each with its own causal source; there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope.
-In particular, the precision of NASA Kepler photometry for exoplanet science—the most precise photometric measurements of stars ever made—appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, and unmodeled stellar variability.
-Here we present the Causal Pixel Model (CPM) for Kepler data, a data-driven model intended to capture variability but preserve transit signals.
-The CPM works at the pixel level (not the photometric measurement level); it can capture more fine-grained information about the variation of the spacecraft than is available in the pixel-summed aperture photometry.
-The basic idea is that CPM predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities while not containing any information on possible transits at the target star.
-In addition, we use the target star’s future and past (auto-regression).
+In general, astronomical observations are affected by several kinds of noise, each with its own causal source; 
+there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
+In particular, the precision of NASA Kepler photometry for exoplanet science—
+the most precise photometric measurements of stars ever made—
+appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
+and unmodeled stellar variability. Here we present the Causal Pixel Model (CPM) for Kepler data, 
+a data-driven model intended to capture variability but preserve transit signals. 
+The CPM works at the pixel level (not the photometric measurement level); 
+it can capture more fine-grained information about the variation of the spacecraft than is available in the pixel-summed aperture photometry. 
+The basic idea is that CPM predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
+while not containing any information on possible transits at the target star. In addition, we use the target star’s future and past (auto-regression). 
 By appropriately separating the data into training and test sets, we ensure that information about any transit will be perfectly isolated from the fitting of the model. 
-The method has four hyper-parameters (the number of predictor stars, the auto-regressive window size, and two L2-regularization amplitudes for model components), which we set by cross-validation.
+The method has four hyper-parameters (the number of predictor stars, the auto-regressive window size, 
+and two L2-regularization amplitudes for model components), which we set by cross-validation. 
 We determine a generic set of hyper-parameters that works well on most of the stars and apply the method to a corresponding set of target stars. 
-For these stars, we calculate the Combined Differential Photometric Precision (CDPP), which indicate the noise level of a certain time scale.
+For these stars, we calculate the Combined Differential Photometric Precision (CDPP), which indicates the noise level of a certain time scale. 
 We find that we can consistently outperform (for the purposes of exoplanet detection) the Kepler Pre-search Data Conditioning (PDC) method for exoplanet discovery.
@@
 \caption{\label{ccd} Stars on the same CCD share systematic errors. 
-The two panels show pixel fluxes (brightnesses) for two stars: (a) KIC 5088536, (b) KIC 5949551; here, KIC stands for Kepler Input Catalog.
-Both stars lie on the same CCD (see Fig.~\ref{fig1}), but far enough apart such that there is no stray light from one affecting the other.
+The two panels show pixel fluxes (brightnesses) for two stars: (a) KIC 5088536, (b) KIC 5949551; 
+here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD (see Fig.~\ref{fig1}), 
+but far enough apart such that there is no stray light from one affecting the other. 
 Each panel shows the pixels contributing to the respective star. 
@@
 \caption{\label{hyperparameter} Comparsion between default and optimized hyper-parameters. 
-The three panels plot show the results from default, In the top panel, SAP flux is plotted in black, CPM prediction of default hyper parameters is in red line, \name prediction of optimized hyper-parameters is in green line.
-The middle panel shows the CPM flux of the optimized hyper-parameters, while the bottom is the CPM flux of the default hyper-parameters, the two vertical blue lines indicate the location of the transit signal,  and signal to noise ratio is calculated in both situation.
-The optimized hyper-parameter performs better than the Default one, but the results from both situation are close.
-}
+In the top panel, SAP flux is plotted in black, \name\ prediction of default hyper parameters is in red line, 
+\name\ prediction of optimized hyper-parameters is in green line. 
+The middle panel shows the CPM flux of the optimized hyper-parameters, 
+while CPM flux of the default hyper-parameters is in the bottom panel, 
+the two vertical blue lines indicate the location of the transit signal, and signal to noise ratio is calculated in both situation. 
+The optimized hyper-parameter performs better than the default one, but the results from both situation are close. }
 \end{figure}
@@
 \includegraphics[width=\columnwidth]{distortion_9822284_normal}
-\caption{\label{distortion} CPM preserves transit signals.
+\caption{\label{distortion} \name\ preserves transit signals. 
 Fake signal with amplitude 1.0005 is inserted into the single pixel (1, 2) of star KIC 9822284. 
-In the top panel, the black points shows the SAP flux of the pixel with the injected signal, the green line is the fitting of the SAP flux, and the red line is the CPM prediction.
-In the bottom panel, red and green points represent the CPM flux and fit flux, while the signal value is indicated by the horizontal line.
+In the top panel, the black points shows the SAP flux of the pixel with the injected signal, 
+the green line is the fitting of the SAP flux, and the red line is the \name\ prediction. 
+In the bottom panel, red and green points represent the \name\ flux and fit flux, 
+while the signal value is indicated by the horizontal line. 
 CPM largely preserves the signal while the fitting flux overfit the signal.}
@@
 To give a view on how our method performs, \name\ is applied on several stars with 
-known transit signals with different variability and magnitudes 
-as shown in Fig.~\ref{fluxes}. From the plots, we can see that \name\ works quite well
-on these stars,  producing the \name\ fluxes with low variation and preserving the transit
-signals.
-In addition, we compare 6 quiet stars (non-variable stars) with the 
-PDC method The results illustrate that for these quiet stars our approach removes 
+known transit signals but different variability and magnitudes as shown in Fig.~\ref{fluxes}. 
+From the plots, we can see that \name\ works quite well on these stars, producing the \name\ fluxes 
+with low variation and preserving the transit signals.
+In addition, \name\ and PDC are compared based on 6 quiet stars 
+(non-variable stars, first two rows of Fig.~\ref{fluxes}). 
+The results illustrate that for these quiet stars our approach removes 
 a major part of the variability present in the PDC light curves, while preserving the transit signals. 
-To provide a quantitative comparison, we ran CPM on 1000 stars from the whole Kepler input catalog (500 chosen randomly from the whole list, and 500 random G-type sun-like stars), and estimate the Combined Differential Photometric Precision (CDPP) for CPM and PDC (before CDPP is estimated, the 100 most variable stars in the list are
-removed, since PDC is not designed to remove stellar variability).
-CDPP is an estimate of the relative precision in a time window, indicating the noise level seen by a transit signal with a given duration.
+To provide a quantitative comparison, we ran \name\ on 1000 stars from the whole Kepler input catalog 
+(500 chosen randomly from the whole list, and 500 random G-type sun-like stars), 
+and estimate the Combined Differential Photometric Precision (CDPP) for \name\ and PDC. 
+CDPP is an estimate of the relative precision in a time window, 
+indicating the noise level seen by a transit signal with a given duration. 
 The duration is typically chosen to be 3, 6, or 12 hours. 
 We use the 12-hours CDPP metric, since the transit duration of an earth-like planet is roughly 10 hours. 
-Fig.~\ref{cdpp} presents our CDPP comparison of CPM and PDC, showing that our method (CPM) outperforms PDC.
+Before CDPP is estimated, the 100 most variable stars in the list are removed, 
+since PDC is not designed to remove stellar variability, and we want to compare \name\ and PDC on the same footing.
+Fig.~\ref{cdpp} presents our CDPP comparison of \name\ and PDC, showing that our method (\name) outperforms PDC.
 
@@
 \caption{\label{fluxes} Corrected fluxes using \name, for 12 example stars, spanning the main magnitude (brightness) range encountered. 
-In first column plots,   we consider bright stars with magnitude from 9 to 10.5, second cloumn are stars with magnitude from 11 to 12.5,  and the third column are faint stars with magnitude above 13.
-In the first two rows, we present some quiet stars.
+In first column plots,   we consider bright stars with magnitude from 9 to 10.5, second cloumn are stars with magnitude from 11 to 12.5,  
+and the third column are faint stars with magnitude above 13. In the first two rows, we present some quiet stars. 
 In all three panels, the top panel shows the SAP flux (black) and the CPM regression (red), i.e., our prediction of the star from other stars. 
 The middle panel shows the CPM flux corrected using the regression, and the bottom shows the PDC flux. 
-One can see that the CPM flux curve preserves the exoplanet transits (little downward spikes), while removing a substantial part of the variability present in the PDC flux.
+One can see that the CPM flux curve preserves the exoplanet transits (little downward spikes), 
+while removing a substantial part of the variability present in the PDC flux. 
 Both the bottom two rows present some variable stars with slow and fast variability. 
-For the variable stars, we did not present the PDC
-comparison, since the PDC flux try to preserve intrinsic steller variability.}
+For the variable stars, we did not present the PDC comparison, since the PDC flux try to preserve intrinsic steller variability.}
 \end{figure}
@@
 \end{subfigure}
-\caption{\label{cdpp} Comparison of the proposed method (CPM) to the Kepler Pre-search Data Conditioning (PDC) method in terms of Combined Differential Photometric Precision (CDPP) (see text).
-Plot (a) shows our performance (red) vs.\ the PDC performance in a scatter plot, as a function of star magnitude (note that larger magnitude means fainter stars, and smaller values of CDPP indicate a higher quality as measured by CDPP.
+\caption{\label{cdpp} Comparison of the proposed method (CPM) to the \Kepler\ Pre-search Data Conditioning (PDC) method 
+in terms of Combined Differential Photometric Precision (CDPP) (see text). 
+Plot (a) shows our performance (red) vs.\ the PDC performance in a scatter plot, as a function of star magnitude 
+(note that larger magnitude means fainter stars, and smaller values of CDPP indicate a higher quality as measured by CDPP.  
 Plot (b) bins the same dataset and shows box plots within each bin, indicating median, top quartile and bottom quartile. 
-The red box corresponds to CPM, while the black box refers to PDC.
-Plot (c), finally, shows a histogram of CDPP values.
+The red box corresponds to CPM, while the black box refers to PDC. Plot (c), finally, shows a histogram of CDPP values. 
 Note that the red histogram has more mass towards the left, i.e., smaller values of CDPP, indicating that our method overall outperforms PDC, the Kepler ``gold standard.'' 
@@
 \section{Discussion}
-We have presented a a simple yet highly effective method that works in pixel-level based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ light curves, which is intended to search
-exoplanets. However, based on our assumption of the causal structure of the \Kepler 
+We have presented a simple yet highly effective method that works in pixel-level 
+based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ light curves, 
+which is intended to search exoplanets. 
+However, based on our assumption of the causal structure of the \Kepler\ 
 data, if we turn off the auto-regressive components and keep the predictors from other
@@
 However, forget all the unsolved problems, we expect that our method will enable
-astronomical discoveries at higher sensitivity on the existing \Kepler data as well as on
-future missions.  As we know, \Kepler K2 data are suffering from the broken-down of
+astronomical discoveries at higher sensitivity on the existing \Kepler\ data as well as on
+future missions.  As we know, \Kepler\ K2 data are suffering from the broken-down of
 reaction wheels, which makes the satellite hard to control and introduce significant

### 2015-02-25 cpm.tex
typos

@@
 \subsection{\name\ model}
-Each individual \Kepler\ target star is, for each month (here we always use data per month rather than quarter,  
-since there is discontinuity between every 30-ish-day period),
+Each individual \Kepler\ target star is, for each quarter (each 90-ish-day period)
   on a particular CCD on the \Kepler\ focal plane.
@@
 
-Let's consider a particular pixel $m$ in the focal plane in one particular month.
-In that quarter, the spacecraft delivers $N\sim 1300$ measurements $I_{mn}$
+Let's consider a particular pixel $m$ in the focal plane in one particular month
+(here we always use data per month rather than quarter,  
+since there is discontinuity between every 30-ish-day period).
+In that month, the spacecraft delivers $N\sim 1300$ measurements $I_{mn}$
   of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the month.
@@
   is the \emph{pixel set} $\set{M}_m$ associated with pixel $m$.
-   To rule out any direct optical cross-talk by stray
+   To rule out any direct optical cross-talk by starry 
 light, we require that the predictor pixels are from stars
-sufficiently far away from the target star (at least 20 pixels
-distance on the CCD).
+sufficiently far away from the target star (at least 20 pixels distance on the CCD).
 Note that because the set $\set{M}_m$ is of pixels associated with \emph{different} stars
@@
 
-In addition to pixel set $m'\in\set{M}_m$ from other stars,  we also include
-past and future of the target star --- autoregressive (AR) component as input to remove 
-more of the stellar variability and thus increase the sensitivity for transits. To do this, 
-we select an exclusion window of half-width $\Delta t$ including R data points, 
-where $\Delta t\sim 10$ (as big 
-as the window in train-and-test framework) around the point of time $t_{n}$ being 
-corrected, to ensure that we do not remove the transit itself and then use S closest 
-future and past time points. That is, for every pixel m in the target star , we construct S virtual time series, in which every component v is defined to be     
+In addition to pixel set $m'\in\set{M}_m$ from other stars,  
+  we also include past and future of the target star --- autoregressive (AR) component as input 
+  to remove more of the stellar variability and thus increase the sensitivity for transits. 
+To do this, we select an exclusion window of half-width $\Delta t$ including R data points, 
+  where $\Delta t\sim 10$ (as big as the window in train-and-test framework) 
+  around the point of time $t_{n}$ being corrected, 
+  to ensure that we do not remove the transit itself and then use S closest future and past time points. 
+That is, for every pixel m in the target star , we construct S virtual time series, 
+  in which every component v is defined to be     
 \begin{eqnarray}
@@
 \end{eqnarray}
-where k = 0, 1, ..., S, so if there are totally M pixels in the target stars, we will finally add 
-$2\cdot M\cdot S$ autoregressive components into the predictors,  which construct the autoregressive set $\set{V}_m$
+where k = 0, 1, ..., S, so if there are totally M pixels in the target stars, 
+  we will finally add $2\cdot M\cdot S$ autoregressive components into the predictors, 
+  which constructs the autoregressive set $\set{V}_m$
 
@@
 
-It is worth to mention that the \name\ prediction $S_{n}$ is constructed from pixels without any transit information. Therefore, it can be regarded as a light curve without
-signal. Based on this idea, we can construct the ``\name\ flux'' to be the relative residual
-between \name\ prediction and SAP Flux $F_{n}$
+It is worth to mention that the \name\ prediction $S_{n}$ is constructed from pixels without any transit information. Therefore, it can be regarded as a light curve without transit signal. 
+Based on this idea, 
+  we can construct the ``\name\ flux'' to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
 \begin{eqnarray}
@@
 The \name\ flux is 
-In some sense, it is this relative residual that contains the exoplanet transit signals we 
-seek. That is, a transit creates a negative residual away from the prediction.
+In some sense, it is this relative residual that contains the exoplanet transit signals we seek. 
+That is, a transit creates a negative residual away from the prediction, 
+  and the amount of relative residual is just the fraction of the light eclipsed by the planet (the transit depth).
 
 \subsection{Hyper-parameters}
-In the description of \name, we introduce 4 hyper-parameters---number of predictor 
-stars Q (or number of predictor pixels P), number of autoregressive components S, and 
-the two regularization strength
-$\lambda_{a}$ and $\lambda_{b}$. To set these 4 hyper-parameters, in principle we 
-need to run cross-validation on every single stars to optimize the performance of \name.
-But optimizing in this 4-dimensional space is expensive, especially in \name\ we need 
-to solve thousands of linear system with thousands of parameters. Therefore, in this 
-paper we just set a general set of hyper-parameters ($P=4000$, $Q=3$, $
-\lambda_a=1e5$, $\lambda_a=1e5$) which works well in most of the stars without
-highly variability. To show how this general set of hyper-parameters performs, here we 
-present a typical comparison between optimized and default hyper-parameters in 
-Fig~\ref{hyperparameter}. We can see that, in Fig~\ref{hyperparameter}, there is less variation in the \name\ flux from optimized hyper-parameters 
-(green points in second panel) than from the default one 
-(red points in the bottom panel). In addition, the optimized flux has higher signal to 
-noise ratio of the known transit than the default. 
-However, the performance of default hyper-parameters is acceptable and we will use  
-this set of hyper-parameters throughout rest of the paper to show the general 
-performance of \name.
+In the description of \name, 
+  we introduce 4 hyper-parameters---number of predictor stars Q (or number of predictor pixels P), 
+  number of autoregressive components S, and the two regularization strength $\lambda_{a}$ and $\lambda_{b}$.
+To set these 4 hyper-parameters, 
+  in principle we need to run cross-validation on every single stars to optimize the performance of \name.
+But optimizing in this 4-dimensional space is expensive, 
+  especially in \name\ we need to solve thousands of linear system with thousands of parameters. 
+Therefore, in this paper, 
+  we just set a general set of hyper-parameters ($P=4000$, $Q=3$, $\lambda_a=1e5$, $\lambda_a=1e5$), 
+  which works well in most of the stars without highly variability. 
+To show how this general set of hyper-parameters performs, 
+  here we present a typical comparison between optimized and default hyper-parameters 
+  in Fig~\ref{hyperparameter}. 
+We can see that, in Fig~\ref{hyperparameter}, 
+  there is less variation in the \name\ flux from optimized hyper-parameters (green points in second panel) 
+  than from the default one (red points in the bottom panel). 
+In addition, the optimized flux has higher signal to noise ratio of the known transit than the default. 
+However, the performance of default hyper-parameters is acceptable 
+  and we will use this set of hyper-parameters throughout rest of the paper 
+  to show the general performance of \name.
 
@@
 (500 chosen randomly from the whole list, and 500 random G-type sun-like stars), 
-and estimate the Combined Differential Photometric Precision (CDPP) for \name\ and PDC. 
+and estimate the Combined Differential Photometric Precision (CDPP) (\todo{citation}) for \name\ and PDC. 
 CDPP is an estimate of the relative precision in a time window, 

### 2015-02-25 cpm.tex
page 1 -3

@@
 \newcommand{\todo}[1]{\textbf{#1}}
+
+\newcommand{\Bernhard}[1]{$\bullet$\footnote{{\bf Bernhard:} #1}}
 
@@
   which leads to slightly different illumination of the focal-plane pixels,
-  and thus different sensitivity to errors (problems) in the device flat-field or sensitivity map.
+  and thus different sensitivity to errors (problems) in the device flat-field \Bernhard{I recall Dan saying that they don't do flat-fielding at Kepler?} or sensitivity map.
 There are also \emph{intra-pixel} sensitivity variations that can contribute (\todo{cite white paper; Spitzer results}).
@@
 In this context, a model is (at least) a parameterized function that can predict data, given parameter settings,
-  and an objective function that can be optimized or sampled to choose or set those parameters.
-Ideally the objective function is probabilistic, or has a probabilistic justification,
-  as with a likelihood or a posterior pdf.
+  and an objective function that can be used to set or sample those parameters.
+In some cases, the objective function can be given a probabilistic justification or interpretation, e.g., if it is constructed using a likelihood and a prior pdf.
 The model can be a physical model (of the spacecraft PSF, pointing, temperature, and so on)
   or it can be a flexible, effective model that has no direct interpretation in terms of physical spacecraft parameters.
-In principle a physical model will do a better job,
-  because it necessarily embodies more prior information,
-  but it requires research and intuition about dominant effects,
-  and this research and intuition is often wrong or incomplete.
+If done well, we would expect a physical model to do a better job,
+  because it embodies more prior information,
+  but it requires research and intuition about dominant effects. 
+If this research and intuition is wrong or incomplete, a physical model may actually perform worse.
 The model we propose here is in the non-physical, effective category.

### 2015-02-25 cpm.tex
up to page 4

@@
   is the \Kepler\ Presearch (\sic) Data Conditioning (PDC) method (\todo{citation}).
-The PDC ``de-trends'' the \Kepler\ lightcurves by fitting them with a small set of basis lightcurves
+The PDC builds on the idea that systematic errors have a temporal structure that can be extracted from ancillary quantities. 
+%This seems the original paper on PDC:
+%[PDC1] https://kepler.nasa.gov/science/ForScientists/papersAndDocumentation/SOCpapers/7740-67-pdc-jtwicken-copyright.pdf
+%
+%This describes the later version of PDC:
+%[PDC2] http://arxiv.org/pdf/1203.1382v1.pdf
+%[PDC3] http://arxiv.org/pdf/1203.1383v1.pdf
+
+In the first PDC \cite{PDC1}, removal of systematic errors was performed based on correlations with a set of ancillary engineering data.
+These data include the temperatures at the local detector electronics below the CCD array, and polynomials describing the centroid motion of the targets from PA.
+
+In \cite{PDC2,PDC3}, filtered light curves of other stars are used instead.
+The light curve of a target star is projected on the leading eight principal components of these light curves.
+This projection is then removed from the star's light curve.
+The principal components are computed from a set of relatively quiet stars close in position and magnitude.
+This was done since it was observed that otherwise, too much of the stellar variability was being removed.
+
+From the point of view of the present paper, one can only guarantee that {\em no} stellar variability is removed if the stars do not depend on time at all.
+If both the target star signal as well as some of the other stars do depend on time, then time acts as a confounder influencing both, and thus the true signals are not statistically independent, and thus the target signal may be compromised.
+We suspect that this effect is limited in \cite{PDC2,PDC3} since only eight principal components are used, which limits the capacity of the model.
+
+PDC ``de-trends'' the \Kepler\ lightcurves by removing those parts that are explained by the basis lightcurves
   generated from a principal components analysis (PCA) of filtered lightcurves.
-That is, it uses data to predict data,
-  regularizing the fit (and avoiding over-fitting) by filtering and restricting the dimensionality (through PCA).
-The method proposed here, \name, is very similar in spirit to the PDC.
-The main differences are
-  (1)~that \name\ works in the pixel domain, not the lightcurve domain, so it has access to more fine-grained information,
-  (2)~that \name\ has far more freedom (far more parameters) than the PDC
+That is, it exploits statistical dependences between different time series, regularizing the fit (and avoiding over-fitting) by filtering and restricting the dimensionality (through PCA).
+
+The method proposed here, \name, shares the motivation of PDC.
+The main differences are that
+\begin{enumerate}
+\item
+\name\ works in the pixel domain, not the lightcurve domain, so it has access to more fine-grained information,
+\item
+\name has far more freedom (far more parameters) than the PDC
   but it strictly avoids over-fitting the lightcurves on exoplanet-transit time-scales
-  through strong regularization and a train-and-test framework, and
-  (3)~that purpose of the \name\ is to search for exoplanets, so in \name, intrinsic stellar
+  through strong regularization and a train-and-test framework,
+\item \name directly optimizes for prediction accuracy, while PDC uses PCA projections
+\item
+the purpose of \name\ is to search for exoplanets, so in \name, intrinsic stellar
   variability is also removed as well as the systematics.
+\item \name uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion.
+PDC works with time series (lightcurves) of the other stars
+\end{enumerate}
+
 The two methods (\name\ and PDC) are similar however,
-  in that they both make the assumption that whatever spacecraft effects are imprinting variability on a stellar lightcurve
+  in that they both make the (implicit or explicit) assumption that whatever spacecraft effects are imprinting variability on a stellar lightcurve
   must also be imprinting similar or related variability on other lightcurves.
-They also assume that the relationships can be captured with linear models.
+In their current versions, they also assume that the relationships can be captured with linear models (although we have also used nonlinear predictions methods for \name, which would be harder to do in PDC).
 By going to the pixel level (unlike the PDC, which works at the photometry level),
@@
 
-The scope of this project is an intervention---\name---that makes the \Kepler\ photometry more precise.
+The scope of this project is an intervention---\name---that makes the \Kepler\ photometry more precise.\Bernhard{doesn't this contradict our statement that we only care about transits and we remove the lightcurve variability?
+Suggestion: The scope of this project is an intervention---\name---that makes the \Kepler\ transit photometry more precise.}
 We describe the method and deliver all the relevant code in a public, open-source repository.
@@
   or along directions in parameter space in which the data are not constraining.
-General regularizations or priors will break the convexity of linear models;
+General regularizations or priors will break the convexity of linear model fitting;
   if convexity is to be maintained, these regularizations also have to be quadratic,
-  or else one of a small number of other known forms (one of which is L1-regularization).
+  or else one of a class of other known forms (one of which is L1-regularization).\Bernhard{deleted ``small number'' -- I think it is convex for Lp with $p\ge1$.}
 Given these considerations, it makes sense to try to build our pixel-level model

### 2015-02-25 cpm.tex
up to page 10

@@
   pixels from the target star can be used to predict pixels from the target star,
-  provided they are at large-enough time lags that they don't overlap (in time)
-  the signals of interest.
+  provided they are at large-enough time lags that they don't contain information about
+  the signals of interest (i.e., the transits).
 That is, if the model is designed to fit not just spacecraft variability
@@
 
-The fourth general idea involved in this kind of data-driven modeling is that the models aren't \emph{interpretable}.
+The fourth general idea involved in this kind of data-driven modeling is that the models often aren't \emph{interpretable}, or at least hard to interpret.
 This means, in particular, that although the model might do a good job of \emph{predicting} the target pixels,
@@
 
+\Bernhard{Hogg: maybe you want to add sth about the device being 'self-calibratable'?}
+
 \section{\name\ specification and hyper-parameters}
@@
 (here we always use data per month rather than quarter,  
-since there is discontinuity between every 30-ish-day period).
+since there is discontinuity between every 30-ish-day period).\Bernhard{as an aside: I wonder whether \name reduces these discontinuities at all? (if we were to apply it across the discontinuities)}
 In that month, the spacecraft delivers $N\sim 1300$ measurements $I_{mn}$
   of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the month.
-(For intensity measurements $I_{mn}$ here we are using pixels from the Target Pixel Files.)
+(For intensity measurements $I_{mn}$ here we are using pixels from the Target Pixel Files.\Bernhard{include reference})
 We want to build a prediction for the intensity $I_{mn}$ in pixel $m$ at each time $t_n$
@@
 There are many possible qualitatively and quantitatively different choices here.
-Somewhat arbitrarily,
-  we choose all the pixels $m'$ associated with the $Q$ stars on the same CCD in the same quarter
+Assuming that they are affected by similar systematic errors as the target star pixels, we choose all the pixels $m'$ associated with the $Q$ stars on the same CCD in the same quarter
   that are closest in magnitude
@@
 To do this, we select an exclusion window of half-width $\Delta t$ including R data points, 
-  where $\Delta t\sim 10$ (as big as the window in train-and-test framework) 
+  where $\Delta t\sim 10$\, h (as big as the window in the train-and-test framework) 
   around the point of time $t_{n}$ being corrected, 
-  to ensure that we do not remove the transit itself and then use S closest future and past time points. 
-That is, for every pixel m in the target star , we construct S virtual time series, 
-  in which every component v is defined to be     
+  to ensure that we do not remove the transit itself and then use $S$ closest future and past time points. 
+That is, for every pixel $m$ in the target star , we construct $S$ virtual time series, 
+  in which every component $v$ is defined to be     
 \begin{eqnarray}
@@
 \end{eqnarray}
-where k = 0, 1, ..., S, so if there are totally M pixels in the target stars, 
-  we will finally add $2\cdot M\cdot S$ autoregressive components into the predictors, 
+\Bernhard{I find the notation $I_{mn-R-k}$ confusing --- better write $I_{m,n-R-k}$, and then for consistency also $I_{v,n}$ etc.}
+where $k = 0, 1,\dots, S,$ so if there are totally $M$ pixels in the target stars, 
+  we will finally add $2\cdot M\cdot S$\Bernhard{not quite: if I am right, then there are overall $(2R-1)$ in the exclusion zone, and $2S+2$ are used, for each pixel} autoregressive components into the predictors,
   which constructs the autoregressive set $\set{V}_m$
@@
   and an objective function that can be used to find best values for those parameters.
-We prefer to work in a probabilistic mode in which the objective function can be justified
+It is often preferable to work in a probabilistic mode in which the objective function can be justified
   in terms of a likelihood (probability for the data given the model)
@@
   and known variance,
-  likelihood optimization reduces to chi-squared minimization.
+  likelihood optimization reduces to chi-squared \Bernhard{maybe better $\chi^2$?} minimization.
 We add to the standard chi-squared definition a regularization term
@@
 \end{eqnarray}
-where the $\sigma^2_{mn'}$ are the (presumed known) individual-pixel noise variances,
+\Bernhard{(1) why does $I$ have three indices now, and what does that mean? In Eq. (3) there are only two indices. (2) do we need the sigmas at all, or could we absord this into the lambdas?}
+where the $\sigma^2_{mn'}$ are the (presumed known)\Bernhard{known, or estimated from data? If not estimated, how do we know them?} individual-pixel noise variances,
   and $\lambda_{a}$, $\lambda_{b}$ set the strength of the regularization (or width of the prior pdf) for parameters $a_{mnm'}, b_{mnv}$.
+In general, $\lambda_a$ and $\lambda_b$ could depend on $m,n$, however, we do not make use of this freedom.
 

### 2015-02-25 cpm.tex
up to page 12 - that's how far I have read it in detail.

@@
 \end{eqnarray}
-where the sum is over the $M$ pixels that are associated with the target star.
+where the sum is over the $M$ pixels that are associated with the target star \Bernhard{if the sum is only over the pixels of the target star, then all $w_m$ are equal to 1 and they can be dropped}.
 As we have noted above and below, these photometric estimators are not optimal for any purpose,
@@
 
-It is worth to mention that the \name\ prediction $S_{n}$ is constructed from pixels without any transit information. Therefore, it can be regarded as a light curve without transit signal. 
+It is worth to mention that the \name\ prediction $S_{n}$ is constructed from pixels without any information about transits in the target star.\Bernhard{changed this --- I didn't understand it} Therefore, it can be regarded as a light curve without transit signal.
 Based on this idea, 
-  we can construct the ``\name\ flux'' to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
+  we can construct the ``\name\ flux'' (where the inverted commas indicate that it is not a flux in the sense that stellar variability is not preserved) to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
 \begin{eqnarray}
@@
 To set these 4 hyper-parameters, 
-  in principle we need to run cross-validation on every single stars to optimize the performance of \name.
+  in principle we need to run cross-validation on every single star to optimize the performance of \name.
 But optimizing in this 4-dimensional space is expensive, 
-  especially in \name\ we need to solve thousands of linear system with thousands of parameters. 
+  especially in \name\ we need to solve thousands of linear systems with thousands of parameters. 
 Therefore, in this paper, 
-  we just set a general set of hyper-parameters ($P=4000$, $Q=3$, $\lambda_a=1e5$, $\lambda_a=1e5$), 
+  we just set a general set of ``default'' hyper-parameters ($P=4000$, $Q=3$, $\lambda_a=1e5$, $\lambda_a=1e5$), 
   which works well in most of the stars without highly variability. 
@@
   here we present a typical comparison between optimized and default hyper-parameters 
-  in Fig~\ref{hyperparameter}. 
+  in Fig~\ref{hyperparameter}.\Bernhard{maybe explain somewhere how SNR is calculated}  
 We can see that, in Fig~\ref{hyperparameter}, 
@@
 \includegraphics[width=\columnwidth]{compare_10187017}
-\caption{\label{hyperparameter} Comparsion between default and optimized hyper-parameters. 
+\caption{\label{hyperparameter} Comparison between default and optimized hyper-parameters. 
 In the top panel, SAP flux is plotted in black, \name\ prediction of default hyper parameters is in red line, 
@@
 the two vertical blue lines indicate the location of the transit signal, and signal to noise ratio is calculated in both situation. 
-The optimized hyper-parameter performs better than the default one, but the results from both situation are close. }
+The optimized hyper-parameter performs better than the default one, but the results from both situation are close.}
 \end{figure}

### 2015-02-26 documents/cpm.tex
just testing
start to-do list

@@
 
+% # to-do
+% - write causal description
+
 \documentclass[12pt, preprint]{aastex}
+
+\usepackage{graphicx}
+\usepackage{caption} 
+\usepackage{subcaption}
+
+\usepackage{hyperref}
+\usepackage{url}
+
+\usepackage{natbib}
+
+\graphicspath{{figures/}}
 
@@
 
+\newcommand{\Bernhard}[1]{$\bullet$\footnote{{\bf Bernhard:} #1}}
+
 \begin{document}
 
-\title{%
-  Self-calibration of time-domain imaging for exoplanet science, informed by causal structure%
-  \\ or \\
-  A data-driven, pixel-level model to improve the precision of \Kepler\ photometry%
-  \\ or \\
-  Exploiting causal structure to create a data-driven self-calibration of \Kepler\ imaging%
+\title{
+  Calibrating the pixel-level Kepler imaging data with a causal data-driven model
+ \\ 
 }
@@
 \begin{abstract}
-The precision of \Kepler\ photometry for exoplanet science---the most
-precise photometric measurements of stars ever made---appears to be
-limited by unknown or untracked variations in spacecraft pointing and
-temperature, and unmodeled stellar variability.
-Here we present \name,
-  a data-driven model of these variations in \Kepler\ data (or really of their impact on the photometry).
-Importantly (and uniquely),
-  \name\ works at the pixel level (not the photometric measurement level);
-  it can capture more fine-grained information about the variation of the spacecraft
-  (especially regarding pointing and point-spread function)
-  than is available in the pixel-summed photometry.
-\name\ is extreme in that it has enormous flexibility and it only uses data (and meta-data) to predict data:
-\name\ provides a prediction for each readout pixel built from a linear combination of the readouts
-  from very large numbers of nearby pixels (plus some spacecraft information);
-  the choice of nearby pixels is guided by ideas from causal inference.
-\name\ avoids over-fitting by employing a train-and-test formalism
-  designed to ensure that transit-like photometric events and short-timescale stellar variability
-  cannot be captured or distorted by the model;
-  it is designed to remove spacecraft-induced variability but not intrinsic stellar variability.
-We show that \name\ outperforms the \Kepler\ Presearch (\sic) Data Conditioning method on a set of example stars.
-We release open-source code that provides \name\ output for any star in the existing \Kepler\ Archive,
-  and we discuss applications for other missions,
-  including any possible \Kepler\ two-wheel mission.
+In general, astronomical observations are affected by several kinds of noise, each with its own causal source; 
+there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
+In particular, the precision of NASA Kepler photometry for exoplanet science—
+the most precise photometric measurements of stars ever made—
+appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
+and unmodeled stellar variability. Here we present the Causal Pixel Model (CPM) for Kepler data, 
+a data-driven model intended to capture variability but preserve transit signals. 
+The CPM works at the pixel level (not the photometric measurement level); 
+it can capture more fine-grained information about the variation of the spacecraft than is available in the pixel-summed aperture photometry. 
+The basic idea is that CPM predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
+while not containing any information on possible transits at the target star. In addition, we use the target star’s future and past (auto-regression). 
+By appropriately separating the data into training and test sets, we ensure that information about any transit will be perfectly isolated from the fitting of the model. 
+The method has four hyper-parameters (the number of predictor stars, the auto-regressive window size, 
+and two L2-regularization amplitudes for model components), which we set by cross-validation. 
+We determine a generic set of hyper-parameters that works well on most of the stars and apply the method to a corresponding set of target stars. 
+For these stars, we calculate the Combined Differential Photometric Precision (CDPP), which indicates the noise level of a certain time scale. 
+We find that we can consistently outperform (for the purposes of exoplanet detection) the Kepler Pre-search Data Conditioning (PDC) method for exoplanet discovery.
+
 \end{abstract}
@@
   is the \Kepler\ Presearch (\sic) Data Conditioning (PDC) method (\todo{citation}).
-The PDC ``de-trends'' the \Kepler\ lightcurves by fitting them with a small set of basis lightcurves
+The PDC builds on the idea that systematic errors have a temporal structure that can be extracted from ancillary quantities. 
+%This seems the original paper on PDC:
+%[PDC1] https://kepler.nasa.gov/science/ForScientists/papersAndDocumentation/SOCpapers/7740-67-pdc-jtwicken-copyright.pdf
+%
+%This describes the later version of PDC:
+%[PDC2] http://arxiv.org/pdf/1203.1382v1.pdf
+%[PDC3] http://arxiv.org/pdf/1203.1383v1.pdf
+
+In the first PDC \cite{PDC1}, removal of systematic errors was performed based on correlations with a set of ancillary engineering data.
+These data include the temperatures at the local detector electronics below the CCD array, and polynomials describing the centroid motion of the targets from PA.
+
+In \cite{PDC2,PDC3}, filtered light curves of other stars are used instead.
+The light curve of a target star is projected on the leading eight principal components of these light curves.
+This projection is then removed from the star's light curve.
+The principal components are computed from a set of relatively quiet stars close in position and magnitude.
+This was done since it was observed that otherwise, too much of the stellar variability was being removed.
+
+From the point of view of the present paper, one can only guarantee that {\em no} stellar variability is removed if the stars do not depend on time at all.
+If both the target star signal as well as some of the other stars do depend on time, then time acts as a confounder influencing both, and thus the true signals are not statistically independent, and thus the target signal may be compromised.
+We suspect that this effect is limited in \cite{PDC2,PDC3} since only eight principal components are used, which limits the capacity of the model.
+
+PDC ``de-trends'' the \Kepler\ lightcurves by removing those parts that are explained by the basis lightcurves
   generated from a principal components analysis (PCA) of filtered lightcurves.
-That is, it uses data to predict data,
-  regularizing the fit (and avoiding over-fitting) by filtering and restricting the dimensionality (through PCA).
-The method proposed here, \name, is very similar in spirit to the PDC.
-The main differences are
-  (1)~that \name\ works in the pixel domain, not the lightcurve domain, so it has access to more fine-grained information,
-  (2)~that \name\ has far more freedom (far more parameters) than the PDC
+That is, it exploits statistical dependences between different time series, regularizing the fit (and avoiding over-fitting) by filtering and restricting the dimensionality (through PCA).
+
+The method proposed here, \name, shares the motivation of PDC.
+The main differences are that
+\begin{enumerate}
+\item
+\name\ works in the pixel domain, not the lightcurve domain, so it has access to more fine-grained information,
+\item
+\name has far more freedom (far more parameters) than the PDC
   but it strictly avoids over-fitting the lightcurves on exoplanet-transit time-scales
-  through strong regularization and a train-and-test framework, and
-  (3)~that when \name\ fits a star, there is no possibility of any contribution of the star itself to the fit basis vectors.
+  through strong regularization and a train-and-test framework,
+\item \name directly optimizes for prediction accuracy, while PDC uses PCA projections
+\item
+the purpose of \name\ is to search for exoplanets, so in \name, intrinsic stellar
+  variability is also removed as well as the systematics.
+\item \name uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion.
+PDC works with time series (lightcurves) of the other stars
+\end{enumerate}
+
 The two methods (\name\ and PDC) are similar however,
-  in that they both make the assumption that whatever spacecraft effects are imprinting variability on a stellar lightcurve
+  in that they both make the (implicit or explicit) assumption that whatever spacecraft effects are imprinting variability on a stellar lightcurve
   must also be imprinting similar or related variability on other lightcurves.
-They also assume that the relationships can be captured with linear models.
+In their current versions, they also assume that the relationships can be captured with linear models (although we have also used nonlinear predictions methods for \name, which would be harder to do in PDC).
 By going to the pixel level (unlike the PDC, which works at the photometry level),
@@
   pixels from the target star can be used to predict pixels from the target star,
-  provided they are at large-enough time lags that they don't overlap (in time)
-  the signals of interest.
+  provided they are at large-enough time lags that they don't contain information about
+  the signals of interest (i.e., the transits).
 That is, if the model is designed to fit not just spacecraft variability
   but also intrinsic stellar variability,
-  the predictive model will be permitted to use as input pixels that \emph{do} overlap the target star.
-In what follows, we are only going to use input data that do not overlap that target star pixels.
-These models ought to remove spacecraft variability but not intrinsic stellar variability.
+  the predictive model will be permitted to use as input pixels that \emph{do} overlap the 
+  target star.
+In what follows, we are going to use input data both from pixels of other stars and the  
+target star pixels' past and furture.
+These models ought to remove both spacecraft variability and intrinsic stellar variability, 
+which is optimal for exoplanet transit searching.
+
+\begin{figure}[htb]
+\centering
+\begin{subfigure}[htb]{0.48\columnwidth}
+\includegraphics[width=\columnwidth]{5088536-5}
+\caption{}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.48\columnwidth}
+\includegraphics[width=\columnwidth]{5949551-5}
+\caption{}
+\end{subfigure}
+\caption{\label{ccd} Stars on the same CCD share systematic errors. 
+The two panels show pixel fluxes (brightnesses) for two stars: (a) KIC 5088536, (b) KIC 5949551; 
+here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD (see Fig.~\ref{fig1}), 
+but far enough apart such that there is no stray light from one affecting the other. 
+Each panel shows the pixels contributing to the respective star. 
+Note that there exist similar trends in these two stars, caused by systematic errors. 
+%The idea of our approach is to predict each pixel from a set of pixels from other stars in order to remove those systematics.
+}
+\end{figure}
 
@@
 We have to make some kind of heuristic or interpretive move to extract from the data-driven model the quanitites of interest.
-
-In the context of this project, the quantities of interest are the light-curves
-  (photometry as a function of time or apparent flux as a function of time)
-  for every star.
-What we get, for every star, from the data-driven model, is a train-and-test prediction
-  for the brightness of every pixel in the patch of the detector relevant to the star,
-  along with the residual, or the difference between the measured read-out pixel value and the prediction (data minus prediction).
-What will be called the ``\name\ photometry'' in what follows is constructed from what will be called the ``\name\ pixels''.
-The \name\ photometry is constructed from the \name\ pixels
-  just as the \Kepler\ official SAP photometry is constructed from the \Kepler\ Target Pixel Files;
-  that is, by summing pre-defined sets of pixels (with unit weights; see above and below for criticism of this).
-The \name\ pixels are constructed from the data-driven model predictions by taking,
-  for each pixel in each contiguous data segment (see below),
-  the \emph{mean} predicted pixel value (mean over time),
-  and adding to it the residuals (data minus prediction) away from the data-driven model prediction.
-These \name\ pixels are ``calibrated'' pixels,
-  in that the data-driven model has been used to fit out all the variability it can,
-  subject to the restrictions imposed by its finite freedom and the train-and-test specification.
-The signal---in which exoplanet transits will be found---is fundamentally the observed residual away from this prediction,
-  but it has to be added back into the mean prediction to have the right ``baseline'' or zero level.
-In short, \name\ will produce prediction pixels, residual pixels, \name\ pixels (mean prediction plus residual),
-  and aperture-based \name\ photometry analogous to the SAP photometry.
 
@@
   artificial exoplanet transit signals injected into real \Kepler\ pixel-level data.
-We can also show that it produces stellar light-curves that look sensible for known variable stars.
-We cannot yet show that it is optimal for our long-term goals,
-  nor can we show that it produces pixelss or light-curves that are more accurately calibrated;
-  we will only show promising properties of the \name\ outputs.
+  and promising properties of the \name\ outputs.
 In the end, the value of the \name\ will be demonstrated by the scientific projects it enables.
 
+\Bernhard{Hogg: maybe you want to add sth about the device being 'self-calibratable'?}
+
 \section{\name\ specification and hyper-parameters}
-
-Each individual \Kepler\ target star is, for each quarter (each 90-ish-day period),
+\subsection{\name\ model}
+Each individual \Kepler\ target star is, for each quarter (each 90-ish-day period)
   on a particular CCD on the \Kepler\ focal plane.
@@
 
-Let's consider a particular pixel $m$ in the focal plane in one particular quarter.
-In that quarter, the spacecraft delivers $N\sim 4000$ measurements $I_{mn}$
-  of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the quarter.
-(For intensity measurements $I_{mn}$ here we are using pixels from the Target Pixel Files.)
+Let's consider a particular pixel $m$ in the focal plane in one particular month
+(here we always use data per month rather than quarter,  
+since there is discontinuity between every 30-ish-day period).\Bernhard{as an aside: I wonder whether \name reduces these discontinuities at all? (if we were to apply it across the discontinuities)}
+In that month, the spacecraft delivers $N\sim 1300$ measurements $I_{mn}$
+  of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the month.
+(For intensity measurements $I_{mn}$ here we are using pixels from the Target Pixel Files.\Bernhard{include reference})
 We want to build a prediction for the intensity $I_{mn}$ in pixel $m$ at each time $t_n$
@@
 There are many possible qualitatively and quantitatively different choices here.
-Somewhat arbitrarily,
-  we choose all the pixels $m'$ associated with the $Q=5$ stars on the same CCD in the same quarter
+Assuming that they are affected by similar systematic errors as the target star pixels, we choose all the pixels $m'$ associated with the $Q$ stars on the same CCD in the same quarter
   that are closest in magnitude
@@
   is the \emph{pixel set} $\set{M}_m$ associated with pixel $m$.
+   To rule out any direct optical cross-talk by starry 
+light, we require that the predictor pixels are from stars
+sufficiently far away from the target star (at least 20 pixels distance on the CCD).
 Note that because the set $\set{M}_m$ is of pixels associated with \emph{different} stars
-  than the star associated with pixel $m$,
+  than the star associated with pixel $m$, and are far from it on CCD, 
   the pixel $m$ will not be in the set $\set{M}_m$,
@@
 
-\todo{DFM: Do we want a schematic figure or cartoon which illustrates all of this?}
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.8\columnwidth]{train_and_test}
+\caption{\label{train-and-test} Train-and-test framework. Data near the target point $t_{n}$ within $\Delta t$ is excluded in the training set}
+\end{figure}
 
-In addition to the other data (from pixels $m'\in\set{M}_m$ and taken at time points $n'\in\set{N}_n$)
-  used to make each prediction, we will use also some \emph{meta-data};
-  these include the time itself $t_n$,
-  the sine and cosine of the parallactic angle $\theta(t_n)$,
-  and the dot product $\hat{n}\cdot v(t_n)$ of the spacecraft velocity $v(t_n)$
-  with the direction $\hat{n}$ towards the \Kepler\ field center.
-These additional meta-data variables permit the data-driven model
-  to capture easily variations induced in the data
-  by proper motions, parallaxes, and stellar aberration.
-Symbolically, we will denote these $K=4$ pieces of meta-data $d_{kn}$.
+In addition to pixel set $m'\in\set{M}_m$ from other stars,  
+  we also include past and future of the target star --- autoregressive (AR) component as input 
+  to remove more of the stellar variability and thus increase the sensitivity for transits. 
+To do this, we select an exclusion window of half-width $\Delta t$ including R data points, 
+  where $\Delta t\sim 10$\, h (as big as the window in the train-and-test framework) 
+  around the point of time $t_{n}$ being corrected, 
+  to ensure that we do not remove the transit itself and then use $S$ closest future and past time points. 
+That is, for every pixel $m$ in the target star , we construct $S$ virtual time series, 
+  in which every component $v$ is defined to be     
+\begin{eqnarray}
+I_{vn} = I_{mn-R-k}\ or\ I_{vn} = I_{mn+R+k},
+\quad,
+\end{eqnarray}
+\Bernhard{I find the notation $I_{mn-R-k}$ confusing --- better write $I_{m,n-R-k}$, and then for consistency also $I_{v,n}$ etc.}
+where $k = 0, 1,\dots, S,$ so if there are totally $M$ pixels in the target stars, 
+  we will finally add $2\cdot M\cdot S$\Bernhard{not quite: if I am right, then there are overall $(2R-1)$ in the exclusion zone, and $2S+2$ are used, for each pixel} autoregressive components into the predictors,
+  which constructs the autoregressive set $\set{V}_m$
 
@@
 \chi^2_{mn}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{mn'} - I^{\ast}_{mnn'}]^2}{\sigma^2_{mn'}}
-                 + \sum_{m'\in\set{M}_m} \frac{a_{mnm'}^2}{\Sigma^2}
+                 + \lambda_{a}\sum_{m'\in\set{M}_m}a_{mnm'}^2 + \lambda_{b}\sum_{v\in\set{V}_m}b_{mnv}^2
 \\
-I^{\ast}_{mnn'} &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m'n'} + \sum_{k=1}^{K} b_{mnk}\,d_{kn'}
+I^{\ast}_{mnn'} &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m'n'} + \sum_{v\in\set{V}_m} b_{mnv}\,I_{vn'}
 \quad,
 \end{eqnarray}
-where the $\sigma^2_{mn'}$ are the (presumed known) individual-pixel noise variances,
-  and $\Sigma^2$ sets the strength of the regularization (or width of the prior pdf).
-Although the variances $\sigma^2_{mn'}$ are in principle different for every time step $n'$,
-  for nearly-constant stars in good data, there is not much variation;
-  in what follows, we treat these uncertainties as fixed at
-  \todo{DFM: some mean value (we can't ignore this,
-   because it ``plays off against'' the regularization)}
-The regularization variance $\Sigma^2$ we set to 0.3 (\todo{DFM TAKE NOTE; that's about 10 for the parameter you usually use.})
-  because we expect almost all the coefficients $a_{mnm'}$ to be less than unity in magnitude.
-We do not regularize the meta-data coefficients $b_{mnk}$,
-  because we want the model to make use of the (easily interpretable) meta-data coefficients as much as possible.
+\Bernhard{(1) why does $I$ have three indices now, and what does that mean? In Eq. (3) there are only two indices. (2) do we need the sigmas at all, or could we absord this into the lambdas?}
+where the $\sigma^2_{mn'}$ are the (presumed known)\Bernhard{known, or estimated from data? If not estimated, how do we know them?} individual-pixel noise variances,
+  and $\lambda_{a}$, $\lambda_{b}$ set the strength of the regularization (or width of the prior pdf) for parameters $a_{mnm'}, b_{mnv}$.
+In general, $\lambda_a$ and $\lambda_b$ could depend on $m,n$, however, we do not make use of this freedom.
 
@@
 \begin{eqnarray}
-S_n = \frac{1}{M}\,\sum_m w_m\,J_{mn}
+S_n = \sum_m w_m\,I^{\ast}_{mn}
 \quad ,
 \end{eqnarray}
-where the sum is over the $M$ pixels that are associated with the target star.
+where the sum is over the $M$ pixels that are associated with the target star \Bernhard{if the sum is only over the pixels of the target star, then all $w_m$ are equal to 1 and they can be dropped}.
 As we have noted above and below, these photometric estimators are not optimal for any purpose,
@@
 
-Some---or probably most---of the variations of the pixel intensities
-  are being caused by small changes to stellar positions relative to the detector,
-  in turn caused by pointing drifts, parallaxes, proper motions, aberration, and temperature changes.
-The \name\ pixels, being constructed from a mean prediction plus residuals,
-  represent some kind of mean image, averaged over these positional changes.
-  that is, the image constructed from the \name\ pixels would have a broader
-  point-spread function than any individual time-step,
-  and does not necessarily represent any true astronomical scene.
-This is another consequence of the point, discussed above,
-  that data-driven models do not in general provide interpretable results.
-This uninterpretability creates a small problem,
-  which is that the optimization by which the \Kepler\ team chose the pixel weights $w_m$
-  cannot be precisely appropriate for the \name\ pixels,
-  even if it \emph{is} appropriate for the \Kepler\ Target Pixel Files.
-That is, there could be a small sacrifice at this step in photometric estimator quality.
-This motivates future work on photometric estimation.
-That said, we don't expect this effect to be large,
-  because the positional drifts involved are orders of magnitude smaller than a pixel.
+It is worth to mention that the \name\ prediction $S_{n}$ is constructed from pixels without any information about transits in the target star.\Bernhard{changed this --- I didn't understand it} Therefore, it can be regarded as a light curve without transit signal.
+Based on this idea, 
+  we can construct the ``\name\ flux'' (where the inverted commas indicate that it is not a flux in the sense that stellar variability is not preserved) to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
+\begin{eqnarray}
+\delta_{n}&\equiv&\frac{F_{n} - S_{n}}{S_{n}}
+\quad .
+\end{eqnarray}
+The \name\ flux is 
+In some sense, it is this relative residual that contains the exoplanet transit signals we seek. 
+That is, a transit creates a negative residual away from the prediction, 
+  and the amount of relative residual is just the fraction of the light eclipsed by the planet (the transit depth).
 
-\todo{DFM: What does the interface look like?  What are the run times and so on?}
+\subsection{Hyper-parameters}
+In the description of \name, 
+  we introduce 4 hyper-parameters---number of predictor stars Q (or number of predictor pixels P), 
+  number of autoregressive components S, and the two regularization strength $\lambda_{a}$ and $\lambda_{b}$.
+To set these 4 hyper-parameters, 
+  in principle we need to run cross-validation on every single star to optimize the performance of \name.
+But optimizing in this 4-dimensional space is expensive, 
+  especially in \name\ we need to solve thousands of linear systems with thousands of parameters. 
+Therefore, in this paper, 
+  we just set a general set of ``default'' hyper-parameters ($P=4000$, $Q=3$, $\lambda_a=1e5$, $\lambda_a=1e5$), 
+  which works well in most of the stars without highly variability. 
+To show how this general set of hyper-parameters performs, 
+  here we present a typical comparison between optimized and default hyper-parameters 
+  in Fig~\ref{hyperparameter}.\Bernhard{maybe explain somewhere how SNR is calculated}  
+We can see that, in Fig~\ref{hyperparameter}, 
+  there is less variation in the \name\ flux from optimized hyper-parameters (green points in second panel) 
+  than from the default one (red points in the bottom panel). 
+In addition, the optimized flux has higher signal to noise ratio of the known transit than the default. 
+However, the performance of default hyper-parameters is acceptable 
+  and we will use this set of hyper-parameters throughout rest of the paper 
+  to show the general performance of \name.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=\columnwidth]{compare_10187017}
+\caption{\label{hyperparameter} Comparison between default and optimized hyper-parameters. 
+In the top panel, SAP flux is plotted in black, \name\ prediction of default hyper parameters is in red line, 
+\name\ prediction of optimized hyper-parameters is in green line. 
+The middle panel shows the CPM flux of the optimized hyper-parameters, 
+while CPM flux of the default hyper-parameters is in the bottom panel, 
+the two vertical blue lines indicate the location of the transit signal, and signal to noise ratio is calculated in both situation. 
+The optimized hyper-parameter performs better than the default one, but the results from both situation are close.}
+\end{figure}
+
+\clearpage
+
+\subsection{Transit signal in \name}
+One important feature of \name\ is that we use the train-and-test framework to preserve 
+the transit signal. To show how well train-and-test framework performs, we make the
+following experiments on \Kepler\ data as shown in Fig~\ref{distortion}
+In the light curve of single pixel (1, 2) of KIC 9822284, a 10-hrs fake signal 
+with amplitude 1.0005 is inserted. To insert the signal, we simply multiply the light curve 
+by the factor of 1.0005, which makes the little bump in the middle of the SAP light curve 
+(black points in the first panel). With the distorted light curve, we both applied the 
+\name\ and ordinary fitting to the data. In the result, we can see that both \name and 
+ordinary fit the light curve quite well outside the range of inserted signal. However, 
+when examine how these two models preserve the signal that we care, the ordinary
+fitting fit out about 30 percent of the signal, while \name\ almost preserve the whole 
+original amplitude. Therefore,  by this simple experiment, we are able to show that 
+the train-and-test framework used here is capable to keep the transit signal with 
+a particular time scale. And we want to emphasise that it is crucial for searching for
+exoplanets, especially the small ones such as earth-like planets, which only have  
+about tens of parts per million signal in the light curve.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=\columnwidth]{distortion_9822284_normal}
+\caption{\label{distortion} \name\ preserves transit signals. 
+Fake signal with amplitude 1.0005 is inserted into the single pixel (1, 2) of star KIC 9822284. 
+In the top panel, the black points shows the SAP flux of the pixel with the injected signal, 
+the green line is the fitting of the SAP flux, and the red line is the \name\ prediction. 
+In the bottom panel, red and green points represent the \name\ flux and fit flux, 
+while the signal value is indicated by the horizontal line. 
+CPM largely preserves the signal while the fitting flux overfit the signal.}
+\end{figure}
+
+\clearpage
 
@@
 
-For each example, give the code and show the output and provide some discussion.
+To give a view on how our method performs, \name\ is applied on several stars with 
+known transit signals but different variability and magnitudes as shown in Fig.~\ref{fluxes}. 
+From the plots, we can see that \name\ works quite well on these stars, producing the \name\ fluxes 
+with low variation and preserving the transit signals.
+In addition, \name\ and PDC are compared based on 6 quiet stars 
+(non-variable stars, first two rows of Fig.~\ref{fluxes}). 
+The results illustrate that for these quiet stars our approach removes 
+a major part of the variability present in the PDC light curves, while preserving the transit signals. 
+To provide a quantitative comparison, we ran \name\ on 1000 stars from the whole Kepler input catalog 
+(500 chosen randomly from the whole list, and 500 random G-type sun-like stars), 
+and estimate the Combined Differential Photometric Precision (CDPP) (\todo{citation}) for \name\ and PDC. 
+CDPP is an estimate of the relative precision in a time window, 
+indicating the noise level seen by a transit signal with a given duration. 
+The duration is typically chosen to be 3, 6, or 12 hours. 
+We use the 12-hours CDPP metric, since the transit duration of an earth-like planet is roughly 10 hours. 
+Before CDPP is estimated, the 100 most variable stars in the list are removed, 
+since PDC is not designed to remove stellar variability, and we want to compare \name\ and PDC on the same footing.
+Fig.~\ref{cdpp} presents our CDPP comparison of \name\ and PDC, showing that our method (\name) outperforms PDC.
 
-We need a metric for comparing outputs.
-For now lets try plotting the power spectrum of the SAP, PDC, and \name\ photometry for each star.
+\begin{figure}[htb]
+\centering
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_11295426_pdc}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_11401755_pdc}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_5966154_pdc}
+\end{subfigure}
 
-So DWH is imagining multi-panel plots: SAP, PDC, and \name\ vs time,
-  plus a power-spectrum plot vs frequency.
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_3544595_pdc}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_4914423_pdc}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_9892816_pdc}
+\end{subfigure}
 
-Cases ought to include
-\begin{itemize}
-\item a bright, non-variable G star with an Earth injection,
-\item a significant variable like that shown in the white paper, and
-\item a star with a bad quarter or where \Kepler\ sucked it.
-\end{itemize}
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_8866102}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_5695396}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_9950612}
+\end{subfigure}
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_8292840}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_9451706}
+\end{subfigure}%
+\hfill
+\begin{subfigure}[htb]{0.33\textwidth}
+\includegraphics[width=\textwidth]{kic_6677841}
+\end{subfigure}
 
-Then we want to show some kind of scatter plot, which is some variance estimate from us,
-  vs the same estimate from the PDC,
-  to show that we always or usually win.
-This variance estimate should be something like the power in the residuals at frequencies
-  corresponding to 30-hour periods or maybe 50-hour periods or something like that.
+\caption{\label{fluxes} Corrected fluxes using \name, for 12 example stars, spanning the main magnitude (brightness) range encountered. 
+In first column plots,   we consider bright stars with magnitude from 9 to 10.5, second cloumn are stars with magnitude from 11 to 12.5,  
+and the third column are faint stars with magnitude above 13. In the first two rows, we present some quiet stars. 
+In all three panels, the top panel shows the SAP flux (black) and the CPM regression (red), i.e., our prediction of the star from other stars. 
+The middle panel shows the CPM flux corrected using the regression, and the bottom shows the PDC flux. 
+One can see that the CPM flux curve preserves the exoplanet transits (little downward spikes), 
+while removing a substantial part of the variability present in the PDC flux. 
+Both the bottom two rows present some variable stars with slow and fast variability. 
+For the variable stars, we did not present the PDC comparison, since the PDC flux try to preserve intrinsic steller variability.}
+\end{figure}
+
+\begin{figure*}[htb]
+\centering
+\begin{subfigure}[htb]{0.33\columnwidth}
+\includegraphics[width=\columnwidth]{pdc_cdpp12_r}
+\caption{}
+\end{subfigure}%
+%\hfill
+\begin{subfigure}[htb]{0.33\columnwidth}
+\includegraphics[width=\columnwidth]{boxplot_r}
+\caption{}
+\end{subfigure}%
+%\hfill
+\begin{subfigure}[htb]{0.33\columnwidth}
+\includegraphics[width=\columnwidth]{pdc_cdpp12_hist_r100}
+\caption{}
+\end{subfigure}
+\caption{\label{cdpp} Comparison of the proposed method (CPM) to the \Kepler\ Pre-search Data Conditioning (PDC) method 
+in terms of Combined Differential Photometric Precision (CDPP) (see text). 
+Plot (a) shows our performance (red) vs.\ the PDC performance in a scatter plot, as a function of star magnitude 
+(note that larger magnitude means fainter stars, and smaller values of CDPP indicate a higher quality as measured by CDPP.  
+Plot (b) bins the same dataset and shows box plots within each bin, indicating median, top quartile and bottom quartile. 
+The red box corresponds to CPM, while the black box refers to PDC. Plot (c), finally, shows a histogram of CDPP values. 
+Note that the red histogram has more mass towards the left, i.e., smaller values of CDPP, indicating that our method overall outperforms PDC, the Kepler ``gold standard.'' 
+}
+\end{figure*}
+
+\clearpage
 
 \section{Discussion}
+We have presented a simple yet highly effective method that works in pixel-level 
+based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ light curves, 
+which is intended to search exoplanets. 
+However, based on our assumption of the causal structure of the \Kepler\ 
+data, if we turn off the auto-regressive components and keep the predictors from other
+stars working  in the \name, we should be able to still remove the systematics while
+preserve the intrinsic stellar  variability, since there is no reason that these independent
+stars can be used to predict the stellar variability of the target star. However, in fact, we
+can not preserve the stellar variability just by turning off the auto-regressive 
+components. One possible reason can be that, since our model is so flexible 
+(thousands of parameters), in principle it can fit any functions. In this sense, we should 
+run cross-validation with the auto-regressive components turned off and to find out how
+many pixels from other stars we need to just remove systematics while preserve stellar
+variability, but in fact we do not have a good criterion to check how well we preserve
+stellar variability in cross-validation because we do not have enough knowledge of the 
+true stellar variability. Thus for the time being, we just focus on producing well-
+calibrated light curves for searching exoplanets, but in long term, we are looking
+forward to find a method to preserve the stellar variability.
 
-Return to the SAP photometry ``unweighted sum'' issue here.
-
-Didn't do anything about short-cadence data; suck it up.
-
-Lots of quantitative and qualitative choices that ought to be explored.
-These include what and what and what and what?
-How \emph{ought we} make all these choices?
-
-Not the least of these is linearity; deep learning and so on.
-
-The potential for autoregressive models.  Cite the white paper.
-
-The weakest point is construction of photometry from the model plus residuals;
-  interesting whether the output of the model can be interrogated
-  to provide value for those building physical models.
+However, forget all the unsolved problems, we expect that our method will enable
+astronomical discoveries at higher sensitivity on the existing \Kepler\ data as well as on
+future missions.  As we know, \Kepler\ K2 data are suffering from the broken-down of
+reaction wheels, which makes the satellite hard to control and introduce significant
+systematics. Moreover, in 2017, NASA is planning the launch of another space 
+telescope---TESS (Transiting Exoplanet Survey Satellite), which will perform an all-sky 
+survey for small (earth-like) planets of nearby M stars. We think our method can be simply
+extended for these project to help achieving higher precession and more scientific results.
 

### 2015-03-06 documents/cpm.tex
notation

@@
 \newcommand{\Bernhard}[1]{$\bullet$\footnote{{\bf Bernhard:} #1}}
+\newcommand{\Dun}[1]{$\bullet$\footnote{{\bf Dun:} #1}}
 
@@
 since there is discontinuity between every 30-ish-day period).\Bernhard{as an aside: I wonder whether \name reduces these discontinuities at all? (if we were to apply it across the discontinuities)}
-In that month, the spacecraft delivers $N\sim 1300$ measurements $I_{mn}$
+In that month, the spacecraft delivers $N\sim 1300$ measurements $I_{m,n}$
   of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the month.
-(For intensity measurements $I_{mn}$ here we are using pixels from the Target Pixel Files.\Bernhard{include reference})
-We want to build a prediction for the intensity $I_{mn}$ in pixel $m$ at each time $t_n$
-  using the intensities $I_{m'n}$ of other pixels $m'$.
+(For intensity measurements $I_{m,n}$ here we are using pixels from the Target Pixel Files.\Bernhard{include reference})
+We want to build a prediction for the intensity $I_{m,n}$ in pixel $m$ at each time $t_n$
+  using the intensities $I_{m',n}$ of other pixels $m'$.
 The question is:  What other pixels to choose?
@@
 
-When we are predicting the measurement $I_{mn}$ from pixel $m$ at a particular time $t_n$,
+When we are predicting the measurement $I_{m,n}$ from pixel $m$ at a particular time $t_n$,
   we are going to use a train-and-test framework in which not only do we not use
@@
 \begin{eqnarray}
-I_{vn} = I_{mn-R-k}\ or\ I_{vn} = I_{mn+R+k},
+I_{v,n} = I_{m,n-R-k}\ or\ I_{v,n} = I_{m,n+R+k},
 \quad,
@@
   or a posterior probability density function (likelihood times a prior pdf).
-The \name\ treats each \Kepler\ data point $I_{mn}$ as being
-  predictable from a linear combination of data points $I_{m'n}$,
+The \name\ treats each \Kepler\ data point $I_{m,n}$ as being
+  predictable from a linear combination of data points $I_{m',n}$,
   where $m'$ is from the set of non-overlapping pixels $m'\in\set{M}_m$.
 \begin{eqnarray}
-I_{mn}         &=& I^{\ast}_{mn} + e_{mn}
+I_{m,n}         &=& I^{\ast}_{m,n} + e_{m,n}
 \\
-I^{\ast}_{mn}  &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m'n} + \sum_{v\in\set{V}_m} b_{mnv}\,I_{vn}
+I^{\ast}_{m,n}  &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m',n} + \sum_{v\in\set{V}_m} b_{mnv}\,I_{v,n}
 \quad,
 \end{eqnarray}
-where $I^{\ast}_{mn}$ is the prediction (by the model) for data point $I_{mn}$,
-  $e_{mn}$ is a noise contribution or residual away from the prediction,
+where $I^{\ast}_{m,n}$ is the prediction (by the model) for data point $I_{m,n}$,
+  $e_{m,n}$ is a noise contribution or residual away from the prediction,
   and the $a_{mnm'}$ and $b_{mnk}$ are the parameters (linear coefficients of the prediction).
@@
   and they will even be different for every time step $n$;
-  that is, there will be a separate best-fit value for the parameters for every $I_{mn}$.
+  that is, there will be a separate best-fit value for the parameters for every $I_{m,n}$.
 If we presume that the residuals away from the prediction are normally distributed with zero mean
   and known variance,
-  likelihood optimization reduces to chi-squared \Bernhard{maybe better $\chi^2$?} minimization.
+  likelihood optimization reduces to $\chi^2$ \Bernhard{maybe better $\chi^2$?} minimization.
 We add to the standard chi-squared definition a regularization term
@@
 \begin{eqnarray}
-\chi^2_{mn}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{mn'} - I^{\ast}_{mnn'}]^2}{\sigma^2_{mn'}}
+\chi^2_{m,n}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{m,n'} - I^{\ast}_{m,n',n}]^2}{\sigma^2_{m,n'}}
                  + \lambda_{a}\sum_{m'\in\set{M}_m}a_{mnm'}^2 + \lambda_{b}\sum_{v\in\set{V}_m}b_{mnv}^2
 \\
-I^{\ast}_{mnn'} &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m'n'} + \sum_{v\in\set{V}_m} b_{mnv}\,I_{vn'}
+I^{\ast}_{m,n',n} &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m',n'} + \sum_{v\in\set{V}_m} b_{mnv}\,I_{v,n'}
 \quad,
@@
 \Bernhard{(1) why does $I$ have three indices now, and what does that mean? In Eq. (3) there are only two indices. (2) do we need the sigmas at all, or could we absord this into the lambdas?}
-where the $\sigma^2_{mn'}$ are the (presumed known)\Bernhard{known, or estimated from data? If not estimated, how do we know them?} individual-pixel noise variances,
+\Dun{In CPM,  for every time points,  the $\chi^2$ minimization is independent, the third index of $I^{\ast}$ indicates which time point is being 
+optimized,  maybe I can find a better notation}
+where the $\sigma^2_{m,n'}$ are the (presumed known)\Bernhard{known, or estimated from data? If not estimated, how do we know them?} individual-pixel noise variances,
   and $\lambda_{a}$, $\lambda_{b}$ set the strength of the regularization (or width of the prior pdf) for parameters $a_{mnm'}, b_{mnv}$.
@@
 
-The train-and-test idea comes into the objective function $\chi^2_{mn}$:
-When we are computing the objective function $\chi^2_{mn}$,
+The train-and-test idea comes into the objective function $\chi^2_{m,n}$:
+When we are computing the objective function $\chi^2_{m,n}$,
   we are using only time points $n'\in\set{N}_n$ that don't overlap the target (or test) time point $n$.
 We train the model---that is, set the parameters $a_{mnm'}$ and $b_{mnv}$---%
-  by choosing the full set of parameters that jointly minimize the objective function $\chi^2_{mn}$.
+  by choosing the full set of parameters that jointly minimize the objective function $\chi^2_{m,n}$.
 Fortunately, given the form of the model,
   this minimization is just a linear solve (linear operation on the data).
-Importantly however, and perhaps surprisingly, the objective function $\chi^2_{mn}$ is \emph{different}
-  for every target data point (pixel value to be predicted) $I_{mn}$;
+Importantly however, and perhaps surprisingly, the objective function $\chi^2_{m,n}$ is \emph{different}
+  for every target data point (pixel value to be predicted) $I_{m,n}$;
   we have to do an \emph{independent optimization} (or really linear solve)
   of the parameters for every pixel value we want to predict.
-That is, every pixel datum $I_{mn}$ we predict will have
+That is, every pixel datum $I_{m,n}$ we predict will have
   \emph{different} settings of the parameters $a_{mnm'}$ and $b_{mnk}$.
@@
 
-Once we have obtained the parameters $a_{mnm'}$ and $b_{mnv}$ corresponding to a particular data point $I_{mn}$,
-  we can make a \emph{prediction} $I^{\ast}_{mn}$ for the intensity at that pixel.
+Once we have obtained the parameters $a_{mnm'}$ and $b_{mnv}$ corresponding to a particular data point $I_{m,n}$,
+  we can make a \emph{prediction} $I^{\ast}_{m,n}$ for the intensity at that pixel.
 By construction of our objective function, this is truly a prediction,
@@
   (and thus the prediction)
-  did not make use of $I_{mn}$ itself,
+  did not make use of $I_{m,n}$ itself,
   or even any of the pixel values that are nearby in angle or time
   (as described above).
-  With all the predicted pixel values $I^{\ast}_{mn}$ of the target star,  
+  With all the predicted pixel values $I^{\ast}_{m,n}$ of the target star,  
   our new stellar flux estimates,
@@
   is constructed from the Target Pixel Files.
-That is, we perform a weighted sum of \name\ predicted pixels $I^{\ast}_{mn}$ with weights $w_m$,
+That is, we perform a weighted sum of \name\ predicted pixels $I^{\ast}_{m,n}$ with weights $w_m$,
   all of which are either zero or unity,
@@
 \begin{eqnarray}
-S_n = \sum_m w_m\,I^{\ast}_{mn}
+S_n = \sum_m w_m\,I^{\ast}_{m,n}
 \quad ,
 \end{eqnarray}
-where the sum is over the $M$ pixels that are associated with the target star \Bernhard{if the sum is only over the pixels of the target star, then all $w_m$ are equal to 1 and they can be dropped}.
+where the sum is over the $M$ pixels that are associated with the target star and the weight $w_m$ is unity for pixels in the optimal
+aperture while zero outside the optimal aperture.
+ \Bernhard{if the sum is only over the pixels of the target star, then all $w_m$ are equal to 1 and they can be dropped}.
 As we have noted above and below, these photometric estimators are not optimal for any purpose,

### 2015-03-06 documents/cpm.tex
response to bernhard's comments

@@
 
-The scope of this project is an intervention---\name---that makes the \Kepler\ photometry more precise.\Bernhard{doesn't this contradict our statement that we only care about transits and we remove the lightcurve variability?
+The scope of this project is an intervention---\name---that makes the \Kepler\ transit photometry more precise.\Bernhard{doesn't this contradict our statement that we only care about transits and we remove the lightcurve variability?
 Suggestion: The scope of this project is an intervention---\name---that makes the \Kepler\ transit photometry more precise.}
+\Dun{Yes, I think so and made this change.}
 We describe the method and deliver all the relevant code in a public, open-source repository.
@@
 since there is discontinuity between every 30-ish-day period).\Bernhard{as an aside: I wonder whether \name reduces these discontinuities at all? (if we were to apply it across the discontinuities)}
+\Dun{I don't think \name\ will be applied across the discontinuities, especially when auto-regression are applied,  but in the end,  the \name somehow reduces the discontinuities, since it put light curve of every month into the same base line.}
+
 In that month, the spacecraft delivers $N\sim 1300$ measurements $I_{m,n}$
@@
 \Bernhard{I find the notation $I_{mn-R-k}$ confusing --- better write $I_{m,n-R-k}$, and then for consistency also $I_{v,n}$ etc.}
-where $k = 0, 1,\dots, S,$ so if there are totally $M$ pixels in the target stars, 
-  we will finally add $2\cdot M\cdot S$\Bernhard{not quite: if I am right, then there are overall $(2R-1)$ in the exclusion zone, and $2S+2$ are used, for each pixel} autoregressive components into the predictors,
-  which constructs the autoregressive set $\set{V}_m$
+where $k = 1, 2\dots, S,$ so if there are totally $M$ pixels in the target stars, 
+  we will finally add $2\cdot M\cdot S$\Bernhard{not quite: if I am right, then there are overall $(2R-1)$ in the exclusion zone, and $2S+2$ are used, for each pixel} \Dun{I changed k to be $1,2\dots, S$ so, so for every pixel, $2S$ are used}
+  autoregressive components into the predictors, which constructs the autoregressive set $\set{V}_m$
 
@@
 \\
-I^{\ast}_{m,n}  &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m',n} + \sum_{v\in\set{V}_m} b_{mnv}\,I_{v,n}
+I^{\ast}_{m,n}  &=& \sum_{m'\in\set{M}_m} a_{m,n,m'}\,I_{m',n} + \sum_{v\in\set{V}_m} b_{m,n,v}\,I_{v,n}
 \quad,
@@
   $e_{m,n}$ is a noise contribution or residual away from the prediction,
-  and the $a_{mnm'}$ and $b_{mnk}$ are the parameters (linear coefficients of the prediction).
-The parameters $a_{mnm'}$ and $b_{mnk}$ have indices $m$ because
+  and the $a_{m,n,m'}$ and $b_{m,n,k}$ are the parameters (linear coefficients of the prediction).
+The parameters $a_{m,n,m'}$ and $b_{m,n,k}$ have indices $m$ because
   they are different for every pixel $m$,
@@
   (equivalent to multiplying the likelihood by a Gaussian prior pdf)
-  that penalizes large absolute values for the the coefficients $a_{mnm'}$:
+  that penalizes large absolute values for the the coefficients $a_{m,n,m'}$:
 \begin{eqnarray}
 \chi^2_{m,n}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{m,n'} - I^{\ast}_{m,n',n}]^2}{\sigma^2_{m,n'}}
-                 + \lambda_{a}\sum_{m'\in\set{M}_m}a_{mnm'}^2 + \lambda_{b}\sum_{v\in\set{V}_m}b_{mnv}^2
+                 + \lambda_{a}\sum_{m'\in\set{M}_m}a_{m,n,m'}^2 + \lambda_{b}\sum_{v\in\set{V}_m}b_{m,n,v}^2
 \\
-I^{\ast}_{m,n',n} &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m',n'} + \sum_{v\in\set{V}_m} b_{mnv}\,I_{v,n'}
+I^{\ast}_{m,n',n} &=& \sum_{m'\in\set{M}_m} a_{m,n,m'}\,I_{m',n'} + \sum_{v\in\set{V}_m} b_{m,n,v}\,I_{v,n'}
 \quad,
@@
 \Bernhard{(1) why does $I$ have three indices now, and what does that mean? In Eq. (3) there are only two indices. (2) do we need the sigmas at all, or could we absord this into the lambdas?}
-\Dun{In CPM,  for every time points,  the $\chi^2$ minimization is independent, the third index of $I^{\ast}$ indicates which time point is being 
-optimized,  maybe I can find a better notation}
-where the $\sigma^2_{m,n'}$ are the (presumed known)\Bernhard{known, or estimated from data? If not estimated, how do we know them?} individual-pixel noise variances,
-  and $\lambda_{a}$, $\lambda_{b}$ set the strength of the regularization (or width of the prior pdf) for parameters $a_{mnm'}, b_{mnv}$.
+\Dun{In CPM,  for every time points,  the $\chi^2$ minimization is independent, the third indice of $I^{\ast}$ indicates which time point is being optimized, I've added some words to explain it,  maybe we can find a better notation?}
+where the $\sigma^2_{m,n'}$ are the (presumed known)\Bernhard{known, or estimated from data? 
+  If not estimated, how do we know them?} individual-pixel noise variances, and $\lambda_{a}$, 
+  $\lambda_{b}$ set the strength of the regularization (or width of the prior pdf) for parameters $a_{m,n,m'}, b_{m,n,v}$. 
   In general, $\lambda_a$ and $\lambda_b$ could depend on $m,n$, however, we do not make use of this freedom. 
+  Here the prediction $I^{\ast}_{m,n',n}$ has three indices, because in \name\ the $\chi^2$ minimization for every time
+  point is independent and the third indice--n indicates which time point the prediction $I^{\ast}_{m,n',n}$ is used for, 
+  the detail of the independent $\chi^2$ minimization will be discussed as follows.
 
@@
   we are using only time points $n'\in\set{N}_n$ that don't overlap the target (or test) time point $n$.
-We train the model---that is, set the parameters $a_{mnm'}$ and $b_{mnv}$---%
+We train the model---that is, set the parameters $a_{m,n,m'}$ and $b_{m,n,v}$---%
   by choosing the full set of parameters that jointly minimize the objective function $\chi^2_{m,n}$.
@@
 That is, every pixel datum $I_{m,n}$ we predict will have
-  \emph{different} settings of the parameters $a_{mnm'}$ and $b_{mnk}$.
+  \emph{different} settings of the parameters $a_{m,n,m'}$ and $b_{m,n,v}$.
 Since there are of order $10^{6}$ total pixel values in the \Kepler\ Target Pixel Files for \emph{each \Kepler\ target},
@@
 
-Once we have obtained the parameters $a_{mnm'}$ and $b_{mnv}$ corresponding to a particular data point $I_{m,n}$,
+Once we have obtained the parameters $a_{m,n,m'}$ and $b_{m,n,v}$ corresponding to a particular data point $I_{m,n}$,
   we can make a \emph{prediction} $I^{\ast}_{m,n}$ for the intensity at that pixel.
@@
  \Bernhard{if the sum is only over the pixels of the target star, then all $w_m$ are equal to 1 and they can be dropped}.
+ \Dun{$w_m$ is 0 out of the optimal aperture,  we've added some words to explain it.}
 As we have noted above and below, these photometric estimators are not optimal for any purpose,
@@
 
-It is worth to mention that the \name\ prediction $S_{n}$ is constructed from pixels without any information about transits in the target star.\Bernhard{changed this --- I didn't understand it} Therefore, it can be regarded as a light curve without transit signal.
+It is worth to mention that the \name\ prediction $S_{n}$ is constructed from predicted pixel value without any information about transits in the target star due to the train-and-test framework.\Bernhard{changed this --- I didn't understand it} \Dun{Does it look better now?} Therefore, it can be regarded as a light curve without transit signal.
 Based on this idea, 

### 2015-03-08 documents/cpm.tex
changes according to Hogg's comments(page1-5)

@@
   David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{CDS},\ref{MPIA},\ref{email}},
-  Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}},
-  others%
+  Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}}
   }
@@
 \begin{abstract}
-In general, astronomical observations are affected by several kinds of noise, each with its own causal source; 
+Astronomical observations are affected by several kinds of noise, each with its own causal source; 
 there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
-In particular, the precision of NASA Kepler photometry for exoplanet science—
-the most precise photometric measurements of stars ever made—
+The precision of NASA \Kepler\ photometry for exoplanet science ---
+the most precise photometric measurements of stars ever made ---
 appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
-and unmodeled stellar variability. Here we present the Causal Pixel Model (CPM) for Kepler data, 
+and unmodeled stellar variability. Here we present the Causal Pixel Model (\name) for \Kepler\ data, 
 a data-driven model intended to capture variability but preserve transit signals. 
-The CPM works at the pixel level (not the photometric measurement level); 
-it can capture more fine-grained information about the variation of the spacecraft than is available in the pixel-summed aperture photometry. 
-The basic idea is that CPM predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
-while not containing any information on possible transits at the target star. In addition, we use the target star’s future and past (auto-regression). 
-By appropriately separating the data into training and test sets, we ensure that information about any transit will be perfectly isolated from the fitting of the model. 
+The \name\ works at the pixel level; So that
+it can capture more fine-grained information about the variation of the spacecraft.
+The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
+while not containing any information on possible transits in the target star. In addition, we use the target star’s future and past (auto-regression). 
+By appropriately separating, for each data point, the data into training and test sets, we ensure that information about any transit will be perfectly isolated from the model. 
 The method has four hyper-parameters (the number of predictor stars, the auto-regressive window size, 
 and two L2-regularization amplitudes for model components), which we set by cross-validation. 
-We determine a generic set of hyper-parameters that works well on most of the stars and apply the method to a corresponding set of target stars. 
-For these stars, we calculate the Combined Differential Photometric Precision (CDPP), which indicates the noise level of a certain time scale. 
-We find that we can consistently outperform (for the purposes of exoplanet detection) the Kepler Pre-search Data Conditioning (PDC) method for exoplanet discovery.
+We determine a generic set of hyper-parameters that works well for most of the stars and apply the method to a corresponding set of target stars. 
+We find that we can consistently outperform (for the purposes of exoplanet detection) the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.
 
@@
   which leads to slightly different illumination of the focal-plane pixels,
-  and thus different sensitivity to errors (problems) in the device flat-field \Bernhard{I recall Dan saying that they don't do flat-fielding at Kepler?} or sensitivity map.
+  and thus different sensitivity to variations in the device
 There are also \emph{intra-pixel} sensitivity variations that can contribute (\todo{cite white paper; Spitzer results}).
@@
 \item
-\name\ works in the pixel domain, not the lightcurve domain, so it has access to more fine-grained information,
+\name\ works in the pixel domain, not the lightcurve domain, so it has access to more fine-grained information
 \item
-\name has far more freedom (far more parameters) than the PDC
+\name\ has far more freedom (far more parameters) than the PDC
   but it strictly avoids over-fitting the lightcurves on exoplanet-transit time-scales
-  through strong regularization and a train-and-test framework,
-\item \name directly optimizes for prediction accuracy, while PDC uses PCA projections
+  through strong regularization and a train-and-test framework.
+\item 
+\name\ directly optimizes for prediction accuracy, while PDC uses PCA projections.
 \item
@@
   variability is also removed as well as the systematics.
-\item \name uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion.
-PDC works with time series (lightcurves) of the other stars
+\item 
+\name\ uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion, while PDC works with time series (lightcurves) of the other stars.
 \end{enumerate}
@@
 
-The scope of this project is an intervention---\name---that makes the \Kepler\ transit photometry more precise.\Bernhard{doesn't this contradict our statement that we only care about transits and we remove the lightcurve variability?
-Suggestion: The scope of this project is an intervention---\name---that makes the \Kepler\ transit photometry more precise.}
-\Dun{Yes, I think so and made this change.}
+The scope of this project is an intervention---\name---that makes the \Kepler\ transit photometry more precise.
+
 We describe the method and deliver all the relevant code in a public, open-source repository.
@@
   if convexity is to be maintained, these regularizations also have to be quadratic,
-  or else one of a class of other known forms (one of which is L1-regularization).\Bernhard{deleted ``small number'' -- I think it is convex for Lp with $p\ge1$.}
+  or else one of a class of other known forms (one of which is L1-regularization).
 Given these considerations, it makes sense to try to build our pixel-level model
@@
 \name\ prediction of optimized hyper-parameters is in green line. 
-The middle panel shows the CPM flux of the optimized hyper-parameters, 
-while CPM flux of the default hyper-parameters is in the bottom panel, 
+The middle panel shows the \name\ flux of the optimized hyper-parameters, 
+while \name\ flux of the default hyper-parameters is in the bottom panel, 
 the two vertical blue lines indicate the location of the transit signal, and signal to noise ratio is calculated in both situation. 
@@
 while the signal value is indicated by the horizontal line. 
-CPM largely preserves the signal while the fitting flux overfit the signal.}
+\name\ largely preserves the signal while the fitting flux overfit the signal.}
 \end{figure}
@@
 and the third column are faint stars with magnitude above 13. In the first two rows, we present some quiet stars. 
-In all three panels, the top panel shows the SAP flux (black) and the CPM regression (red), i.e., our prediction of the star from other stars. 
-The middle panel shows the CPM flux corrected using the regression, and the bottom shows the PDC flux. 
-One can see that the CPM flux curve preserves the exoplanet transits (little downward spikes), 
+In all three panels, the top panel shows the SAP flux (black) and the \name\ regression (red), i.e., our prediction of the star from other stars. 
+The middle panel shows the \name\ flux corrected using the regression, and the bottom shows the PDC flux. 
+One can see that the \name\ flux curve preserves the exoplanet transits (little downward spikes), 
 while removing a substantial part of the variability present in the PDC flux. 
@@
 \end{subfigure}
-\caption{\label{cdpp} Comparison of the proposed method (CPM) to the \Kepler\ Pre-search Data Conditioning (PDC) method 
+\caption{\label{cdpp} Comparison of the proposed method (\name) to the \Kepler\ Pre-search Data Conditioning (PDC) method 
 in terms of Combined Differential Photometric Precision (CDPP) (see text). 
@@
 Plot (b) bins the same dataset and shows box plots within each bin, indicating median, top quartile and bottom quartile. 
-The red box corresponds to CPM, while the black box refers to PDC. Plot (c), finally, shows a histogram of CDPP values. 
+The red box corresponds to \name, while the black box refers to PDC. Plot (c), finally, shows a histogram of CDPP values. 
 Note that the red histogram has more mass towards the left, i.e., smaller values of CDPP, indicating that our method overall outperforms PDC, the Kepler ``gold standard.'' 

### 2015-03-09 documents/cpm.tex
reference and bibtex

@@
 \newcommand{\Dun}[1]{$\bullet$\footnote{{\bf Dun:} #1}}
+
+\bibliographystyle{apj}
 
@@
   and thus different sensitivity to variations in the device
-There are also \emph{intra-pixel} sensitivity variations that can contribute (\todo{cite white paper; Spitzer results}).
+There are also \emph{intra-pixel} sensitivity variations that can contribute \citep{whitepaper} (\todo{cite white paper; Spitzer results}).
 There are small changes in spacecraft temperature,
@@
   new effects really \emph{must} appear at some point.
-In \figurename~\ref{fig:pixelpatch}, we show the pixel-level variability in the \Kepler\ data
+In \figurename~\ref{ccd}, we show the pixel-level variability in the \Kepler\ data
   near one bright star that shows minimal intrinsic variability;
@@
   but \emph{not} interfere with measurements of stellar variability---%
-  is the \Kepler\ Presearch (\sic) Data Conditioning (PDC) method (\todo{citation}).
+  is the \Kepler\ Presearch (\sic) Data Conditioning (PDC) method \citep{pdc1}, (\todo{citation}).
 The PDC builds on the idea that systematic errors have a temporal structure that can be extracted from ancillary quantities. 
@@
 
-In the first PDC \cite{PDC1}, removal of systematic errors was performed based on correlations with a set of ancillary engineering data.
+In the first PDC \cite{pdc1}, removal of systematic errors was performed based on correlations with a set of ancillary engineering data.
 These data include the temperatures at the local detector electronics below the CCD array, and polynomials describing the centroid motion of the targets from PA.
 
-In \cite{PDC2,PDC3}, filtered light curves of other stars are used instead.
+In \cite{pdc2,pdc3}, filtered light curves of other stars are used instead.
 The light curve of a target star is projected on the leading eight principal components of these light curves.
@@
 If both the target star signal as well as some of the other stars do depend on time, then time acts as a confounder influencing both, and thus the true signals are not statistically independent, and thus the target signal may be compromised.
-We suspect that this effect is limited in \cite{PDC2,PDC3} since only eight principal components are used, which limits the capacity of the model.
+We suspect that this effect is limited in \cite{pdc2,pdc3} since only eight principal components are used, which limits the capacity of the model.
 
@@
 The two panels show pixel fluxes (brightnesses) for two stars: (a) KIC 5088536, (b) KIC 5949551; 
-here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD (see Fig.~\ref{fig1}), 
+here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD, 
 but far enough apart such that there is no stray light from one affecting the other. 
@@
 
+\bibliography{cpm}
+
 \end{document}

### 2015-03-10 documents/cpm.tex
add reference

@@
 \usepackage{subcaption} 
-
+\usepackage{color}
 \usepackage{hyperref}
@@
 \bibliographystyle{apj}
+\definecolor{linkcolor}{rgb}{0,0,0.5}
+\hypersetup{colorlinks=true,linkcolor=linkcolor,citecolor=linkcolor,
+            filecolor=linkcolor,urlcolor=linkcolor}
 
@@
   supplemented by various methods for removing small residual spacecraft-induced and stellar-variability trends in the brightnesses,
-  either filtering the data (with things like median filters; \todo{citations})
-  or fitting the data with flexible models (like polynomials or splines or Gaussian Processes; \todo{citations}).
+  either filtering the data (with things like median filters; \cite{trendfilter})
+  or fitting the data with flexible models (like polynomials or splines or Gaussian Processes; 
+  \cite{gaussian}).
 When employed in the service of exoplanet search and characterization,
@@
   which leads to slightly different illumination of the focal-plane pixels,
-  and thus different sensitivity to variations in the device
-There are also \emph{intra-pixel} sensitivity variations that can contribute \citep{whitepaper} (\todo{cite white paper; Spitzer results}).
+  and thus different sensitivity to variations in the device.
+There are also \emph{intra-pixel} sensitivity variations that can contribute \citep{whitepaper}.
 There are small changes in spacecraft temperature,
@@
   but \emph{not} interfere with measurements of stellar variability---%
-  is the \Kepler\ Presearch (\sic) Data Conditioning (PDC) method \citep{pdc1}, (\todo{citation}).
+  is the \Kepler\ Presearch (\sic) Data Conditioning (PDC, \cite{pdc1}).
 The PDC builds on the idea that systematic errors have a temporal structure that can be extracted from ancillary quantities. 
@@
 
-In the first PDC \cite{pdc1}, removal of systematic errors was performed based on correlations with a set of ancillary engineering data.
+In the first PDC \citep{pdc1}, removal of systematic errors was performed based on correlations with a set of ancillary engineering data.
 These data include the temperatures at the local detector electronics below the CCD array, and polynomials describing the centroid motion of the targets from PA.
@@
   of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the month.
-(For intensity measurements $I_{m,n}$ here we are using pixels from the Target Pixel Files.\Bernhard{include reference})
+(For intensity measurements $I_{m,n}$ here we are using pixels from the Target Pixel Files on MAST
+  \footnote{\url{http://archive.stsci.edu/kepler/}}, for details of the TPF, 
+  see the \project{Kepler Archive Manual} 
+  \footnote{\url{http://archive.stsci.edu/kepler/manuals/archive_manual.pdf}}).
 We want to build a prediction for the intensity $I_{m,n}$ in pixel $m$ at each time $t_n$
@@
 (500 chosen randomly from the whole list, and 500 random G-type sun-like stars), 
-and estimate the Combined Differential Photometric Precision (CDPP) (\todo{citation}) for \name\ and PDC. 
+and estimate the Combined Differential Photometric Precision (CDPP,  \cite{cdpp1} )for \name\ and PDC. 
 CDPP is an estimate of the relative precision in a time window, 
@@
 We use the 12-hours CDPP metric, since the transit duration of an earth-like planet is roughly 10 hours. 
-Before CDPP is estimated, the 100 most variable stars in the list are removed, 
-since PDC is not designed to remove stellar variability, and we want to compare \name\ and PDC on the same footing.
+Before CDPP is estimated, the variability of the stars are evaluated by median differential variability 
+  (MDV, see \cite{basri2013} for details). 
+Based on the variability, the 100 most variable stars in the list are removed, 
+  since PDC is not designed to remove stellar variability, 
+  and we want to compare \name\ and PDC on the same footing.
 Fig.~\ref{cdpp} presents our CDPP comparison of \name\ and PDC, showing that our method (\name) outperforms PDC.
@@
 
-However, forget all the unsolved problems, we expect that our method will enable
-astronomical discoveries at higher sensitivity on the existing \Kepler\ data as well as on
-future missions.  As we know, \Kepler\ K2 data are suffering from the broken-down of
-reaction wheels, which makes the satellite hard to control and introduce significant
-systematics. Moreover, in 2017, NASA is planning the launch of another space 
-telescope---TESS (Transiting Exoplanet Survey Satellite), which will perform an all-sky 
-survey for small (earth-like) planets of nearby M stars. We think our method can be simply
-extended for these project to help achieving higher precession and more scientific results.
+However, forget all the unsolved problems, 
+  we expect that data-driven model like our method will enable astronomical discoveries 
+  at higher sensitivity on the existing \Kepler\ data as well as on future missions.  
+As we know, \Kepler\ \project{K2} \citep{k2} data are suffering from the broken-down of reaction wheels, 
+  which makes the satellite hard to control and introduce significant systematics. 
+Flexible data-driven model \citep{dfm} has already shown the power on the \project{K2} data 
+  and find new planets.
+Moreover, in 2017, NASA is planning the launch of another space telescope---
+  \project{TESS} (Transiting Exoplanet Survey Satellite, \cite{tess}), 
+  which will perform an all-sky survey for small (earth-like) planets of nearby M stars. 
+  We think our method can be simply extended for these project to help achieving higher precession and more scientific results.
 

### 2015-03-17 documents/cpm.tex
changes to Hogg's comments

@@
 In what follows, we are going to use input data both from pixels of other stars and the  
-target star pixels' past and furture.
+target star pixels' past and future.
 These models ought to remove both spacecraft variability and intrinsic stellar variability, 
@@
   or by applying strong priors
-  (as with smoothness priors, that effectively reduce freedom without explicitly reducing the number of parameters).
+  (as with smoothness priors or regularization, that effectively reduce freedom without explicitly reducing the number of parameters).
 In each case, the restriction on model freedom is controlled by some \emph{hyper-parameter}
@@
   ---meaning the data that are being predicted (the target data).
-Because we are extremely concerned with detecting Earth-analog exoplanet transits,
-  which take about ten hours,
+Because we are concerned with detecting exoplanet transits,
+  which take few hours,
   we adopt an extreme version of the train-and-test framework,
-  in which the training data are always separated from the test data by at least ten hours.
+  in which the training data are always separated from the test data by couple of hours.
 That is, when we are using the model to predict a particular pixel in the target data taken at time $t$,
@@
   that comes either at times prior to $t-\Delta t$ or after $t+\Delta t$,
-  where $\Delta t$ is a tunable parameter but which we will set to roughly $12$~h.
+  where $\Delta t$ is a tunable parameter but which we will set to $9$~h.
 This ensures that no information about any exoplanet transit itself
@@
 
-The fourth general idea involved in this kind of data-driven modeling is that the models often aren't \emph{interpretable}, or at least hard to interpret.
+The fourth general idea involved in this kind of data-driven modelling is that the models often aren't \emph{interpretable}, or at least are hard to interpret.
 This means, in particular, that although the model might do a good job of \emph{predicting} the target pixels,
@@
   will effectively over-fit and distort the most important information in the light-curves.
-That is, what is considered best for modeling the data depends on the objectives of the user.
+That is, what is considered best for modelling the data depends on the objectives of the user.
 For us, who are interested (in the long term) in finding and characterizing Earth analogs,

### 2015-03-20 documents/cpm.tex
Changes to Hogg's comments

@@
   To whom correspondence should be addressed; \texttt{<david.hogg@nyu.edu>}.}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Ames}%
-%%   NASA Ames Research Center}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Courant}%
-%%   Courant Institute of Mathematical Sciences, New York University}
 \altaffiltext{\theaddress}{\stepcounter{address}\label{MPIIS}%
   Max-Planck-Institut f\"ur Intelligente Systeme, T\"ubingen}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Oxford}%
-%%   Department of Physics, Oxford University}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{CfA}%
-%%   Harvard--Smithsonian Center for Astrophysics}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{UCL}%
-%%   Department of Physics and Astronomy, University College London}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{CMU}%
-%%   McWilliams Center for Cosmology, Carnegie Mellon University}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Caltech}%
-%%   Department of Astronomy, California Institute of Technology}
-%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Columbia}%
-%%   Department of Astronomy, Columbia University}
 
@@
 Let's consider a particular pixel $m$ in the focal plane in one particular month
-(here we always use data per month rather than quarter,  
-since there is discontinuity between every 30-ish-day period).\Bernhard{as an aside: I wonder whether \name reduces these discontinuities at all? (if we were to apply it across the discontinuities)}
-\Dun{I don't think \name\ will be applied across the discontinuities, especially when auto-regression are applied,  but in the end,  the \name somehow reduces the discontinuities, since it put light curve of every month into the same base line.}
-
+  (here we always use data per month rather than quarter,  since there are discontinuities between every 30-ish-day period).
 In that month, the spacecraft delivers $N\sim 1300$ measurements $I_{m,n}$
-  of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the month.
+  of the intensity falling in pixel $m$ at the $N$ times $t_n$ at which exposures were taken during the month.
 (For intensity measurements $I_{m,n}$ here we are using pixels from the Target Pixel Files on MAST
@@
 
-When we are predicting the measurement $I_{m,n}$ from pixel $m$ at a particular time $t_n$,
-  we are going to use a train-and-test framework in which not only do we not use
-  data at time $t_n$ in optimizing the parameters of the regression or fit,
+When the measurement $I_{m,n}$ is being predicted from pixel $m$ at a particular time $t_n$,
+  train-and-test framework is used, in which not only
+  data at time $t_n$ are not used in optimizing the parameters of the regression or fit,
   but we don't even use any times $t$ such that $|t-t_n| < \Delta t$,
   where $\Delta t\sim 10$\,h as shown in Fig.~\ref{train-and-test}.
-That is, we train (optimize fit parameters) using the \emph{time set} $\set{N}_n$ of time
+That is, the model is trained (optimize fit parameters) by using the \emph{time set} $\set{N}_n$ of time
   indices $n'$ such that for all $n'\in\set{N}_n$,
-  $t_{n'}$ is in the same quarter as $t_n$,
+  $t_{n'}$ is in the same month as $t_n$,
   and $|t_{n'} - t_n|>\Delta t$.
@@
 
-In addition to pixel set $m'\in\set{M}_m$ from other stars,  
-  we also include past and future of the target star --- autoregressive (AR) component as input 
+In addition to the pixel set $m'\in\set{M}_m$ from other stars,  
+  we also include the past and future of the target star --- autoregressive (AR) component as input 
   to remove more of the stellar variability and thus increase the sensitivity for transits. 
@@
   around the point of time $t_{n}$ being corrected, 
-  to ensure that we do not remove the transit itself and then use $S$ closest future and past time points. 
+  to ensure that we do not remove the transit itself 
+  and then use $S$ closest future and past time points subject to that exclusion. 
 That is, for every pixel $m$ in the target star , we construct $S$ virtual time series, 
@@
 \end{eqnarray}
-\Bernhard{I find the notation $I_{mn-R-k}$ confusing --- better write $I_{m,n-R-k}$, and then for consistency also $I_{v,n}$ etc.}
 where $k = 1, 2\dots, S,$ so if there are totally $M$ pixels in the target stars, 

### 2015-03-23 documents/cpm.tex
changes to Hogg's comments

@@
 while not containing any information on possible transits in the target star. In addition, we use the target star’s future and past (auto-regression). 
-By appropriately separating, for each data point, the data into training and test sets, we ensure that information about any transit will be perfectly isolated from the model. 
+By appropriately separating, for each data point, the data into training and test sets, 
+  we ensure that information about any transit will be perfectly isolated from the model. 
 The method has four hyper-parameters (the number of predictor stars, the auto-regressive window size, 
@@
 We determine a generic set of hyper-parameters that works well for most of the stars and apply the method to a corresponding set of target stars. 
-We find that we can consistently outperform (for the purposes of exoplanet detection) the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.
+We find that we can consistently outperform (for the purposes of exoplanet detection)% 
+  the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.
 
@@
 
-In the first PDC \citep{pdc1}, removal of systematic errors was performed based on correlations with a set of ancillary engineering data.
-These data include the temperatures at the local detector electronics below the CCD array, and polynomials describing the centroid motion of the targets from PA.
+In the first PDC \citep{pdc1}, 
+  removal of systematic errors was performed based on correlations with a set of ancillary engineering data. 
+These data include the temperatures at the local detector electronics below the CCD array, 
+  and polynomials describing the centroid motion of the targets from PA.
 
@@
 
-From the point of view of the present paper, one can only guarantee that {\em no} stellar variability is removed if the stars do not depend on time at all.
-If both the target star signal as well as some of the other stars do depend on time, then time acts as a confounder influencing both, and thus the true signals are not statistically independent, and thus the target signal may be compromised.
-We suspect that this effect is limited in \cite{pdc2,pdc3} since only eight principal components are used, which limits the capacity of the model.
+From the point of view of the present paper, 
+one can only guarantee that {\em no} stellar variability is removed if the stars do not depend on time at all. 
+If both the target star signal as well as some of the other stars do depend on time, 
+  then time acts as a confounder influencing both, and thus the true signals are not statistically independent, 
+  and thus the target signal may be compromised. 
+We suspect that this effect is limited in \cite{pdc2,pdc3}, 
+  since only eight principal components are used, which limits the capacity of the model.
 
@@
   generated from a principal components analysis (PCA) of filtered lightcurves.
-That is, it exploits statistical dependences between different time series, regularizing the fit (and avoiding over-fitting) by filtering and restricting the dimensionality (through PCA).
+That is, it exploits statistical dependences between different time series, regularizing the fit (and avoiding over-fitting) 
+  by filtering and restricting the dimensionality (through PCA).
 
@@
 
-The first general idea about data-driven modeling of the kind used here
+The first general idea about data-driven modelling of the kind used here
   is that each data point or data source is going to be 
@@
   lead to different structures for the data-driven model.
-In the case of \Kepler\ data, if we examine two arbitrary stars far away from each other 
-on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light curve time 
-series), we can obviously see that the two stars that are hundreds pixel away from each 
-other do have similar trends. If we believe that different stars in the \Kepler\ field vary 
-independently (that is, are not physically synchronized in any way) because of the 
-distance between them, then the only reason that one star might show variability that is strongly \emph{predictive} (useful for prediction) of another star's variability
+In the case of \Kepler\ data, 
+  if we examine two arbitrary stars far away from each other 
+  on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light curve time series), 
+  we can obviously see that the two stars that are hundreds pixel away from each other do have similar trends. 
+  If we believe that different stars in the \Kepler\ field vary independently 
+  (that is, are not physically synchronized in any way) because of the distance between them, 
+  then the only reason that one star might show variability that is strongly \emph{predictive} (useful for prediction) of another star's variability
   is that both stars are being observed by the same device or spacecraft.
@@
 \end{subfigure}
-\caption{\label{ccd} Stars on the same CCD share systematic errors. 
+\caption{
+  \label{ccd} 
+  Stars on the same CCD share systematic errors. 
   The two panels show pixel fluxes (brightnesses) for two stars: (a) KIC 5088536, (b) KIC 5949551; 
@@
   or by applying strong priors
-  (as with smoothness priors or regularization, that effectively reduce freedom without explicitly reducing the number of parameters).
+  (as with smoothness priors or regularization, 
+  that effectively reduce freedom without explicitly reducing the number of parameters).
 In each case, the restriction on model freedom is controlled by some \emph{hyper-parameter}
@@
 
-In addition, each training data set within which we set the parameters (by optimization) has a finite total time extent $t_{\max}\approx 30$\,d.
+In addition, 
+  each training data set within which we set the parameters (by optimization) has a finite total time extent $t_{\max}\approx 30$\,d.
 The train-and-test framework, which includes data out to time $t_{\max}$ but excludes data within $\Delta t$ of the test data,
-  effectively assumes that the signals worth preserving have time-scales less than $\Delta t$ but don't recur on time-scales
-  shorter than $t_{\max}$.
+  effectively assumes that the signals worth preserving have time-scales less than $\Delta t$ 
+  but don't recur on time-scales shorter than $t_{\max}$.
 Those assumptions are good for our purposes but not necessarily ideal for all users:
@@
 
-The fourth general idea involved in this kind of data-driven modelling is that the models often aren't \emph{interpretable}, or at least are hard to interpret.
+The fourth general idea involved in this kind of data-driven modelling is that the models often aren't \emph{interpretable}, 
+  or at least are hard to interpret.
 This means, in particular, that although the model might do a good job of \emph{predicting} the target pixels,
@@
 There are many possible qualitatively and quantitatively different choices here.
-Assuming that they are affected by similar systematic errors as the target star pixels, we choose all the pixels $m'$ associated with the $Q$ stars on the same CCD in the same quarter
-  that are closest in magnitude
+Assuming that they are affected by similar systematic errors as the target star pixels, 
+  we choose all the pixels $m'$ associated with the $Q$ stars on the same CCD in the same quarter that are closest in magnitude
   (\Kepler\ magnitude as reported in the \Kepler\ Input Catalog)
@@
 \includegraphics[width=0.8\columnwidth]{train_and_test}
-\caption{\label{train-and-test} Train-and-test framework. Data near the target point $t_{n}$ within $\Delta t$ is excluded in the training set}
+\caption{
+  \label{train-and-test} 
+  Train-and-test framework. 
+  Data near the target point $t_{n}$ within $\Delta t$ is excluded in the training set}
 \end{figure}
@@
 where $k = 1, 2\dots, S,$ so if there are totally $M$ pixels in the target stars, 
-  we will finally add $2\cdot M\cdot S$\Bernhard{not quite: if I am right, then there are overall $(2R-1)$ in the exclusion zone, and $2S+2$ are used, for each pixel} \Dun{I changed k to be $1,2\dots, S$ so, so for every pixel, $2S$ are used}
+  we will finally add $2\cdot M\cdot S$
   autoregressive components into the predictors, which constructs the autoregressive set $\set{V}_m$
@@
   and known variance,
-  likelihood optimization reduces to $\chi^2$ \Bernhard{maybe better $\chi^2$?} minimization.
+  likelihood optimization reduces to $\chi^2$ minimization.
 We add to the standard chi-squared definition a regularization term
@@
 \end{eqnarray}
-\Bernhard{(1) why does $I$ have three indices now, and what does that mean? In Eq. (3) there are only two indices. (2) do we need the sigmas at all, or could we absord this into the lambdas?}
-\Dun{In CPM,  for every time points,  the $\chi^2$ minimization is independent, the third indice of $I^{\ast}$ indicates which time point is being optimized, I've added some words to explain it,  maybe we can find a better notation?}
+
 where the $\sigma^2_{m,n'}$ are the (presumed known)\Bernhard{known, or estimated from data? 
@@
   In general, $\lambda_a$ and $\lambda_b$ could depend on $m,n$, however, we do not make use of this freedom. 
-  Here the prediction $I^{\ast}_{m,n',n}$ has three indices, because in \name\ the $\chi^2$ minimization for every time
-  point is independent and the third indice--n indicates which time point the prediction $I^{\ast}_{m,n',n}$ is used for, 
-  the detail of the independent $\chi^2$ minimization will be discussed as follows.
+  Here the prediction $I^{\ast}_{m,n',n}$ has three indices, 
+  because in \name\ the $\chi^2$ minimization for every time
+  point is independent and the third index--$n$ indicates 
+  which time point the prediction $I^{\ast}_{m,n',n}$ is being trained for, 
+  the detail of the independent $\chi^2$ minimization will be discussed below.
 
@@
 We train the model---that is, set the parameters $a_{m,n,m'}$ and $b_{m,n,v}$---%
-  by choosing the full set of parameters that jointly minimize the objective function $\chi^2_{m,n}$.
+  by choosing the full set of parameters $a_{m,n,m'}$ and $b_{m,n,v}$% 
+  that jointly minimize the objective function $\chi^2_{m,n}$.
 Fortunately, given the form of the model,
@@
   we have to do an \emph{independent optimization} (or really linear solve)
-  of the parameters for every pixel value we want to predict.
+  of the parameters for every pixel value we want to predict at every time.
 That is, every pixel datum $I_{m,n}$ we predict will have
@@
 Since there are of order $10^{6}$ total pixel values in the \Kepler\ Target Pixel Files for \emph{each \Kepler\ target},
-  and of order $10^7$ data sources used as basis functions in the linear fitting,
-  this represents one fuck of a lot of linear solves,
-  and a lot of parameters to obtain and record.
+  and of order $10^{3}$ data sources used as basis functions in the linear fitting,
+  this represents a lot of linear solves, and of order $10^{9}$ parameters to obtain and record.
 
@@
   did not make use of $I_{m,n}$ itself,
-  or even any of the pixel values that are nearby in angle or time
+  nor even any of the pixel values that are nearby in angle or time
   (as described above).
@@
 
-It is worth to mention that the \name\ prediction $S_{n}$ is constructed from predicted pixel value without any information about transits in the target star due to the train-and-test framework.\Bernhard{changed this --- I didn't understand it} \Dun{Does it look better now?} Therefore, it can be regarded as a light curve without transit signal.
+It is worth to mention that the \name\ prediction $S_{n}$ is constructed from predicted pixel value 
+  without any information about transits in the target star due to the train-and-test framework.
+  \Bernhard{changed this --- I didn't understand it} \Dun{Does it look better now?} 
+Therefore, it can be regarded as a light curve without transit signal. 
 Based on this idea, 
-  we can construct the ``\name\ flux'' (where the inverted commas indicate that it is not a flux in the sense that stellar variability is not preserved) to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
+  we can construct the ``\name\ flux''% 
+  (where the inverted commas indicate that it is not a flux in the sense that stellar variability is not preserved)% 
+  to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
 \begin{eqnarray}
@@
 \includegraphics[width=\columnwidth]{compare_10187017}
-\caption{\label{hyperparameter} Comparison between default and optimized hyper-parameters. 
+\caption{
+  \label{hyperparameter} 
+  Comparison between default and optimized hyper-parameters. 
   In the top panel, SAP flux is plotted in black, \name\ prediction of default hyper parameters is in red line, 
@@
     while \name\ flux of the default hyper-parameters is in the bottom panel, 
-the two vertical blue lines indicate the location of the transit signal, and signal to noise ratio is calculated in both situation. 
-The optimized hyper-parameter performs better than the default one, but the results from both situation are close.}
+    the two vertical blue lines indicate the location of the transit signal, 
+    and signal to noise ratio is calculated in both situation. 
+  The optimized hyper-parameter performs better than the default one, 
+    but the results from both situation are close.}
 \end{figure}
@@
 \includegraphics[width=\columnwidth]{distortion_9822284_normal}
-\caption{\label{distortion} \name\ preserves transit signals. 
+\caption{
+  \label{distortion} 
+  \name\ preserves transit signals. 
   Fake signal with amplitude 1.0005 is inserted into the single pixel (1, 2) of star KIC 9822284. 
@@
   and we want to compare \name\ and PDC on the same footing.
-Fig.~\ref{cdpp} presents our CDPP comparison of \name\ and PDC, showing that our method (\name) outperforms PDC.
+Fig.~\ref{cdpp} presents our CDPP comparison of \name\ and PDC, 
+  showing that our method (\name) outperforms PDC.
 
@@
 
-\caption{\label{fluxes} Corrected fluxes using \name, for 12 example stars, spanning the main magnitude (brightness) range encountered. 
-In first column plots,   we consider bright stars with magnitude from 9 to 10.5, second cloumn are stars with magnitude from 11 to 12.5,  
-and the third column are faint stars with magnitude above 13. In the first two rows, we present some quiet stars. 
-In all three panels, the top panel shows the SAP flux (black) and the \name\ regression (red), i.e., our prediction of the star from other stars. 
+\caption{
+  \label{fluxes} 
+  Corrected fluxes using \name, for 12 example stars, 
+    spanning the main magnitude (brightness) range encountered. 
+  In first column plots, we consider bright stars with magnitude from 9 to 10.5, 
+    second cloumn are stars with magnitude from 11 to 12.5,  
+    and the third column are faint stars with magnitude above 13. 
+  In the first two rows, we present some quiet stars. 
+  In all three panels, the top panel shows the SAP flux (black) and the \name\ regression (red), 
+    i.e., our prediction of the star from other stars. 
   The middle panel shows the \name\ flux corrected using the regression, and the bottom shows the PDC flux. 
@@
   Both the bottom two rows present some variable stars with slow and fast variability. 
-For the variable stars, we did not present the PDC comparison, since the PDC flux try to preserve intrinsic steller variability.}
+  For the variable stars, we did not present the PDC comparison, 
+    since the PDC flux try to preserve intrinsic steller variability.}
 \end{figure}
@@
 \end{subfigure}
-\caption{\label{cdpp} Comparison of the proposed method (\name) to the \Kepler\ Pre-search Data Conditioning (PDC) method 
+\caption{
+  \label{cdpp} 
+  Comparison of the proposed method (\name) to the \Kepler\ Pre-search Data Conditioning (PDC) method 
     in terms of Combined Differential Photometric Precision (CDPP) (see text). 
   Plot (a) shows our performance (red) vs.\ the PDC performance in a scatter plot, as a function of star magnitude 
-(note that larger magnitude means fainter stars, and smaller values of CDPP indicate a higher quality as measured by CDPP.  
-Plot (b) bins the same dataset and shows box plots within each bin, indicating median, top quartile and bottom quartile. 
-The red box corresponds to \name, while the black box refers to PDC. Plot (c), finally, shows a histogram of CDPP values. 
-Note that the red histogram has more mass towards the left, i.e., smaller values of CDPP, indicating that our method overall outperforms PDC, the Kepler ``gold standard.'' 
+    (note that larger magnitude means fainter stars, 
+    and smaller values of CDPP indicate a higher quality as measured by CDPP.  
+  Plot (b) bins the same dataset and shows box plots within each bin, 
+    indicating median, top quartile and bottom quartile. 
+  The red box corresponds to \name, while the black box refers to PDC. 
+  Plot (c), finally, shows a histogram of CDPP values. 
+  Note that the red histogram has more mass towards the left, i.e., smaller values of CDPP, 
+    indicating that our method overall outperforms PDC, the Kepler ``gold standard.'' 
 }

### 2015-03-28 documents/cpm.tex
changes to Hogg's comments

@@
 aperture while zero outside the optimal aperture.
- \Bernhard{if the sum is only over the pixels of the target star, then all $w_m$ are equal to 1 and they can be dropped}.
- \Dun{$w_m$ is 0 out of the optimal aperture,  we've added some words to explain it.}
 As we have noted above and below, these photometric estimators are not optimal for any purpose,
@@
 
-It is worth to mention that the \name\ prediction $S_{n}$ is constructed from predicted pixel value 
-  without any information about transits in the target star due to the train-and-test framework.
-  \Bernhard{changed this --- I didn't understand it} \Dun{Does it look better now?} 
-Therefore, it can be regarded as a light curve without transit signal. 
+Because of the train-and-test framework,  
+  we expect the \name\ prediction $S_{n}$ to be a prediction of%
+  what the star lightcurve would have under the influence of the spacecraft but with no exoplanet signal 
 Based on this idea, 
@@
 \end{eqnarray} 
-The \name\ flux is 
-In some sense, it is this relative residual that contains the exoplanet transit signals we seek. 
+In some sense, it is this relative residual--- the \name\ flux that contains the exoplanet transit signals we seek. 
 That is, a transit creates a negative residual away from the prediction, 
@@
 \subsection{Hyper-parameters}
-In the description of \name, 
-  we introduce 4 hyper-parameters---number of predictor stars Q (or number of predictor pixels P), 
-  number of autoregressive components S, and the two regularization strength $\lambda_{a}$ and $\lambda_{b}$.
+The \name\ has 4 hyper-parameters--- 
+  the number of predictor stars Q (or number of predictor pixels P), 
+  the number of autoregressive components S, 
+  and the two regularization strength $\lambda_{a}$ and $\lambda_{b}$.
 To set these 4 hyper-parameters, 
-  in principle we need to run cross-validation on every single star to optimize the performance of \name.
+  in principle we need to run something like a cross-validation on every single star to optimize performance.
 But optimizing in this 4-dimensional space is expensive, 
-  especially in \name\ we need to solve thousands of linear systems with thousands of parameters. 
+  especially since in the \name\ we need to solve thousands of linear systems, 
+  each of which has thousands of free parameters. 
 Therefore, in this paper, 
   we just set a general set of ``default'' hyper-parameters ($P=4000$, $Q=3$, $\lambda_a=1e5$, $\lambda_a=1e5$), 
-  which works well in most of the stars without highly variability. 
+  which works well in most of the stars without high variability. 
 To show how this general set of hyper-parameters performs, 
-  here we present a typical comparison between optimized and default hyper-parameters 
+  we present a few comparison between optimized and default hyper-parameters 
   in Fig~\ref{hyperparameter}.\Bernhard{maybe explain somewhere how SNR is calculated}  
 We can see that, in Fig~\ref{hyperparameter}, 
-  there is less variation in the \name\ flux from optimized hyper-parameters (green points in second panel) 
-  than from the default one (red points in the bottom panel). 
+  there is less variation in the \name\ flux% 
+  when we use optimized hyper-parameters (green points in second panel)% 
+  than when we use the default one (red points in the bottom panel). 
 In addition, the optimized flux has higher signal to noise ratio of the known transit than the default. 
 However, the performance of default hyper-parameters is acceptable 
-  and we will use this set of hyper-parameters throughout rest of the paper 
+  and we will use this set of hyper-parameters throughout the rest of the paper 
   to show the general performance of \name.
@@
   For the variable stars, we did not present the PDC comparison, 
-    since the PDC flux try to preserve intrinsic steller variability.}
+    since the PDC flux try to preserve intrinsic stellar variability.}
 \end{figure}
@@
 We have presented a simple yet highly effective method that works in pixel-level 
-based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ light curves, 
+based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ lightcurves, 
 which is intended to search exoplanets. 

### 2015-03-29 documents/cpm.tex
discussion

@@
 \section{Discussion}
-We have presented a simple yet highly effective method that works in pixel-level 
+We have presented a simple yet highly effective method---the \name\ that works in pixel-level 
   based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ lightcurves, 
   which is intended to search exoplanets.
-However, based on our assumption of the causal structure of the \Kepler\ 
-data, if we turn off the auto-regressive components and keep the predictors from other
-stars working  in the \name, we should be able to still remove the systematics while
-preserve the intrinsic stellar  variability, since there is no reason that these independent
-stars can be used to predict the stellar variability of the target star. However, in fact, we
-can not preserve the stellar variability just by turning off the auto-regressive 
-components. One possible reason can be that, since our model is so flexible 
-(thousands of parameters), in principle it can fit any functions. In this sense, we should 
-run cross-validation with the auto-regressive components turned off and to find out how
-many pixels from other stars we need to just remove systematics while preserve stellar
-variability, but in fact we do not have a good criterion to check how well we preserve
-stellar variability in cross-validation because we do not have enough knowledge of the 
-true stellar variability. Thus for the time being, we just focus on producing well-
-calibrated light curves for searching exoplanets, but in long term, we are looking
-forward to find a method to preserve the stellar variability.
+In \name, systematics and stellar variabilities are removed by% 
+  either fitting with other stars' lightcures or auto-regressive components,
+  while transit signals can still be perfectly preserved by train-and-test framework.
+Low variable clean lightcurves can be produced by \name\,  which is ideal for transit planet searching. 
+The CDPP noise level estimation is also presented in the paper to show the performance of \name.
+
+\todo{Compare with PDC, median filter, pre-whitening}
+
+However, based on our assumption of the causal structure of the \Kepler\ data, 
+  if we turn off the auto-regressive components and keep the predictors from other stars working in the \name, 
+  we should be able to still remove the systematics while preserve the intrinsic stellar variability, 
+  since there is no reason that these independent stars can be used to predict the stellar variability of the target star.
+However, in fact, we can not preserve the stellar variability just by turning off the auto-regressive components. 
+One possible reason can be that, since our model is so flexible (thousands of parameters), 
+  in principle it can fit any functions. 
+In this sense, 
+  we should run cross-validation with the auto-regressive components turned off 
+  and to find out how many pixels from other stars we need to just remove systematics 
+  while preserve stellar variability, 
+  but in fact we do not have a good criterion to check how well we preserve stellar variability in cross-validation 
+  because we do not have enough knowledge of the true stellar variability. 
+Thus for the time being, we just focus on producing well-calibrated light curves for searching exoplanets, 
+  but in long term, we are looking forward to find a method to preserve the stellar variability.
+
+Another issue of the \name\ is that when there are strong transit signals in the lightcurve,  
+  one can find distortion around the these signals.
+We think this problem is caused by the train-and-test framework.
+Train-and-test framework is applied in the \name\ to preserve the transit signals, 
+  in which data points in a certain excluded window are separated from the model.
+However, for data points half-window size away from the transit signals, 
+  the prediction of these points in \name\ is largely influenced by the strong transit signal.
+That is,  these points are predicted to be a little bit smaller than they should be, 
+  since transit signal (negative points away from the continuum) makes the model think
+  there is a decreasing trend in this region.
+This window edge effect is a trade-off of the train-and-test framework that is crucial for \name,
+ and can not be solved in the scope of \name.
 

### 2015-04-01 documents/cpm.tex
commit discussion

@@
 
-The second general idea about data-driven modeling is the investigator's beliefs
+The second general idea about data-driven modelling is the investigator's beliefs
   about the causal processes that generate the data
@@
 
-\Bernhard{Hogg: maybe you want to add sth about the device being 'self-calibratable'?}
+We also want to emphasis that all the calibration in this paper for \Kepler is 
+  based on the assumption that the device is 'self-calibratable', 
+  which means all the information we need to calibrate the device are contained in the device itself 
+  (either in science data or engineering data) and no external information, 
+  for example, measurements from other device, are needed
 
@@
 
-where the $\sigma^2_{m,n'}$ are the (presumed known)\Bernhard{known, or estimated from data? 
-  If not estimated, how do we know them?} individual-pixel noise variances, and $\lambda_{a}$, 
+where the $\sigma^2_{m,n'}$ are the (the column FLUX\_ERR in TPF is used, which is a image of 1-sigma error provided by the Kepler team) individual-pixel noise variances, and $\lambda_{a}$, 
   $\lambda_{b}$ set the strength of the regularization (or width of the prior pdf) for parameters $a_{m,n,m'}, b_{m,n,v}$. 
@@
 
-However, forget all the unsolved problems, 
+One possible way to solve this kind of edge effect 
+  but still preserve the transit signals to do the simultaneous fitting 
+  for both systematics and transit signal together, 
+  like what have been done in \cite{dfm}. 
+That is,  
+  instead of only modelling the systematics% 
+  and then subtracting it from the raw data to produce some de-trended lightcurves,
+  a comprehensive model for both all components in the data (systematics, stellar variabilities and transits)  can be made. In this kind of model, there is no need for train-and-test framework,
+  since all transit signals have already been modelled 
+  and no de-trended lightcurve will be produced. Planets will be found directly in the model itself.
+
+However, despite all the problems mentioned in the \name,
   we expect that data-driven model like our method will enable astronomical discoveries 

### 2015-04-02 documents/cpm.tex
typos

@@
 We determine a generic set of hyper-parameters that works well for most of the stars and apply the method to a corresponding set of target stars. 
-We find that we can consistently outperform (for the purposes of exoplanet detection)% 
+We find that we can consistently outperform (for the purposes of exoplanet detection) 
   the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.
@@
 We train the model---that is, set the parameters $a_{m,n,m'}$ and $b_{m,n,v}$---%
-  by choosing the full set of parameters $a_{m,n,m'}$ and $b_{m,n,v}$% 
+  by choosing the full set of parameters $a_{m,n,m'}$ and $b_{m,n,v}$ 
   that jointly minimize the objective function $\chi^2_{m,n}$.
@@
 Because of the train-and-test framework,  
-  we expect the \name\ prediction $S_{n}$ to be a prediction of%
+  we expect the \name\ prediction $S_{n}$ to be a prediction of
   what the star lightcurve would have under the influence of the spacecraft but with no exoplanet signal 
 Based on this idea, 
-  we can construct the ``\name\ flux''% 
-  (where the inverted commas indicate that it is not a flux in the sense that stellar variability is not preserved)% 
+  we can construct the ``\name\ flux'' 
+  (where the inverted commas indicate that it is not a flux in the sense that stellar variability is not preserved) 
   to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
@@
 We can see that, in Fig~\ref{hyperparameter}, 
-  there is less variation in the \name\ flux% 
-  when we use optimized hyper-parameters (green points in second panel)% 
+  there is less variation in the \name\ flux 
+  when we use optimized hyper-parameters (green points in second panel) 
   than when we use the default one (red points in the bottom panel). 
@@
   which is intended to search exoplanets.
-In \name, systematics and stellar variabilities are removed by% 
+In \name, systematics and stellar variabilities are removed by
   either fitting with other stars' lightcures or auto-regressive components,
@@
 One possible way to solve this kind of edge effect 
-  but still preserve the transit signals to do the simultaneous fitting 
+  but still preserve the transit signals is to do the simultaneous fitting 
   for both systematics and transit signal together, 
@@
 That is,  
-  instead of only modelling the systematics% 
+  instead of only modelling the systematics 
   and then subtracting it from the raw data to produce some de-trended lightcurves,
-  a comprehensive model for both all components in the data (systematics, stellar variabilities and transits)  can be made. In this kind of model, there is no need for train-and-test framework,
+  a comprehensive model for all components in the data (systematics, stellar variabilities and transits)  can be made. In this kind of model, there is no need for train-and-test framework,
   since all transit signals have already been modelled 

### 2015-04-03 documents/cpm.tex
discussion about cpm and other methods

@@
   these can effectively transfer variability from one source to another.
-There are additional electronics effects like ``rolling bands'' that put additional features into lightcurves.
+There are additional electronics effects like ``rolling bands'' that put additional features into light-curves.
 There are also probably changes to the detector sensitivity with temperature and time,
@@
 
-In \cite{pdc2,pdc3}, filtered light curves of other stars are used instead. 
-The light curve of a target star is projected on the leading eight principal components of these light curves. 
-This projection is then removed from the star's light curve. 
+In \cite{pdc2,pdc3}, filtered light-curves of other stars are used instead. 
+The light-curve of a target star is projected on the leading eight principal components of these light-curves. 
+This projection is then removed from the star's light-curve. 
 The principal components are computed from a set of relatively quiet stars close in position and magnitude. 
@@
 
-PDC ``de-trends'' the \Kepler\ lightcurves by removing those parts that are explained by the basis lightcurves
-  generated from a principal components analysis (PCA) of filtered lightcurves.
+PDC ``de-trends'' the \Kepler\ light-curves by removing those parts that are explained by the basis light-curves
+  generated from a principal components analysis (PCA) of filtered light-curves.
 That is, it exploits statistical dependences between different time series, regularizing the fit (and avoiding over-fitting) 
@@
 \item
-\name\ works in the pixel domain, not the lightcurve domain, so it has access to more fine-grained information
+\name\ works in the pixel domain, not the light-curve domain, so it has access to more fine-grained information
 \item
 \name\ has far more freedom (far more parameters) than the PDC
-  but it strictly avoids over-fitting the lightcurves on exoplanet-transit time-scales
+  but it strictly avoids over-fitting the light-curves on exoplanet-transit time-scales
   through strong regularization and a train-and-test framework.
@@
 \item 
-\name\ uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion, while PDC works with time series (lightcurves) of the other stars.
+\name\ uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion, while PDC works with time series (light-curves) of the other stars.
 \end{enumerate}
@@
 The two methods (\name\ and PDC) are similar however,
-  in that they both make the (implicit or explicit) assumption that whatever spacecraft effects are imprinting variability on a stellar lightcurve
-  must also be imprinting similar or related variability on other lightcurves.
+  in that they both make the (implicit or explicit) assumption that whatever spacecraft effects are imprinting variability on a stellar light-curve
+  must also be imprinting similar or related variability on other light-curves.
 In their current versions, they also assume that the relationships can be captured with linear models (although we have also used nonlinear predictions methods for \name, which would be harder to do in PDC).
@@
   if we examine two arbitrary stars far away from each other 
-  on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light curve time series), 
+  on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light-curve time series), 
   we can obviously see that the two stars that are hundreds pixel away from each other do have similar trends. 
@@
   we expect the \name\ prediction $S_{n}$ to be a prediction of
-  what the star lightcurve would have under the influence of the spacecraft but with no exoplanet signal 
+  what the star light-curve would have under the influence of the spacecraft but with no exoplanet signal 
 Based on this idea, 
@@
 following experiments on \Kepler\ data as shown in Fig~\ref{distortion}
-In the light curve of single pixel (1, 2) of KIC 9822284, a 10-hrs fake signal 
-with amplitude 1.0005 is inserted. To insert the signal, we simply multiply the light curve 
-by the factor of 1.0005, which makes the little bump in the middle of the SAP light curve 
-(black points in the first panel). With the distorted light curve, we both applied the 
+In the light-curve of single pixel (1, 2) of KIC 9822284, a 10-hrs fake signal 
+with amplitude 1.0005 is inserted. To insert the signal, we simply multiply the light-curve 
+by the factor of 1.0005, which makes the little bump in the middle of the SAP light-curve 
+(black points in the first panel). With the distorted light-curve, we both applied the 
 \name\ and ordinary fitting to the data. In the result, we can see that both \name and 
-ordinary fit the light curve quite well outside the range of inserted signal. However, 
+ordinary fit the light-curve quite well outside the range of inserted signal. However, 
 when examine how these two models preserve the signal that we care, the ordinary
@@
 exoplanets, especially the small ones such as earth-like planets, which only have  
-about tens of parts per million signal in the light curve.
+about tens of parts per million signal in the light-curve.
 
@@
 The results illustrate that for these quiet stars our approach removes 
-a major part of the variability present in the PDC light curves, while preserving the transit signals. 
+a major part of the variability present in the PDC light-curves, while preserving the transit signals. 
 To provide a quantitative comparison, we ran \name\ on 1000 stars from the whole Kepler input catalog 
@@
 We have presented a simple yet highly effective method---the \name\ that works in pixel-level 
-  based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ lightcurves, 
+  based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ light-curves, 
   which is intended to search exoplanets.
 In \name, systematics and stellar variabilities are removed by
-  either fitting with other stars' lightcures or auto-regressive components,
+  either fitting with other stars' light-curves or auto-regressive components,
   while transit signals can still be perfectly preserved by train-and-test framework.
-Low variable clean lightcurves can be produced by \name\,  which is ideal for transit planet searching. 
+Low variable clean light-curves can be produced by \name\,  
+  which is ideal for transit planet searching. 
 The CDPP noise level estimation is also presented in the paper to show the performance of \name.
 
-\todo{Compare with PDC, median filter, pre-whitening}
+Apart from the \name, as mentioned in the beginning of the paper, 
+  there exist several other methods that are effective in de-trending the light-curve.
+Methods like median filter are quite successful in smoothing all the unwanted features 
+  either from spacecraft or intrinsic stellar variability, 
+  but the problem is that this kind of methods filter everything in the data including the transit signal. 
+This is not a big deal for searching giant planets, since the signal is quite strong. 
+However, 
+  when it comes to earth-like planets (only about 20 ppm transit signal around a sun-like star),
+  any reduction or distortion of the signal is unacceptable. 
+In comparison, in order to achieve higher precision for earth-like planet searching, 
+  \name\  not only exploits the causal structure of the \Kepler\ data,
+  but also apply effective approaches (strong regularization and train-and-test framework)
+  to avoid over-fitting the transit signal.
+There also exists more sophisticated method like PDC.
+As mentioned earlier in this paper, 
+  \name\ is very similar to PDC, 
+  in that they both make use of the correlation between light-curves,
+  which is assumed to be caused by the spacecraft effects (or systematics).
+However, in section 4, we show that \name\ performs better than PDC, 
+  in that it has a overall low noise level (CDPP).
+We think the outperformance mainly caused by two factor.
+One is that \name\ calibrates every single pixel separately, 
+  while PDC works in the photometry level.
+It is no doubt that pixel-level modelling enables \name\ capture more variability, such as 
+variations in the centroids and point-spread function from spacecraft pointing, roll, and temperature.
+The other reason is that,  
+  in PDC,  only leading eight principal components of some relative light-curves are used.
+Although restricting the number of components can prevent over-fitting, we think with this limited number of components, 
+  it is insufficient to capture all the variabilities in the light-curve.
+In \name\, hundreds of stars' light-curves (or thousands of pixels) are used 
+  to capture relatively complete information of the variabilities, 
+  while strong regularization and train-and-test framework are applied to prevent over-fitting.
+Although we present the comparison between \name\ and PDC, 
+  we still want to emphasis that PDC is a method intended to preserve stellar variabilities, 
+  while the \name\ is optimized for exoplanet searching. 
+The comparison is only based on our objective (search for earth-like planet), 
+  and should not be regard as standard of a best model for \Kepler\ data.
 
-However, based on our assumption of the causal structure of the \Kepler\ data, 
+However, apart from the outstanding performance in calibrating the data,  
+  the \name\ still has several issues. 
+Based on our assumption of the causal structure of the \Kepler\ data, 
   if we turn off the auto-regressive components and keep the predictors from other stars working in the \name, 
@@
   because we do not have enough knowledge of the true stellar variability. 
-Thus for the time being, we just focus on producing well-calibrated light curves for searching exoplanets, 
+Thus for the time being, we just focus on producing well-calibrated light-curves for searching exoplanets, 
   but in long term, we are looking forward to find a method to preserve the stellar variability.
 
-Another issue of the \name\ is that when there are strong transit signals in the lightcurve,  
+Another issue of the \name\ is that when there are strong transit signals in the light-curve,  
   one can find distortion around the these signals.
@@
   instead of only modelling the systematics 
-  and then subtracting it from the raw data to produce some de-trended lightcurves,
+  and then subtracting it from the raw data to produce some de-trended light-curves,
   a comprehensive model for all components in the data (systematics, stellar variabilities and transits)  can be made. In this kind of model, there is no need for train-and-test framework,
   since all transit signals have already been modelled 
-  and no de-trended lightcurve will be produced. Planets will be found directly in the model itself.
+  and no de-trended light-curve will be produced. Planets will be found directly in the model itself.
 

### 2015-04-03 documents/cpm.tex
plot for black-and-white printer

@@
 \centering
-\includegraphics[width=\columnwidth]{compare_10187017}
+\includegraphics[width=\columnwidth]{compare_10187017_bw}
 \caption{
@@
   Comparison between default and optimized hyper-parameters. 
-  In the top panel, SAP flux is plotted in black, \name\ prediction of default hyper parameters is in red line, 
-    \name\ prediction of optimized hyper-parameters is in green line. 
+  In the top panel, SAP flux is plotted in black, 
+    \name\ prediction of default hyper parameters is in thin red line, 
+    \name\ prediction of optimized hyper-parameters is in bold grey line. 
   The middle panel shows the \name\ flux of the optimized hyper-parameters, 
@@
 \centering
-\includegraphics[width=\columnwidth]{distortion_9822284_normal}
+\includegraphics[width=\columnwidth]{distortion_9822284_normal_bw}
 \caption{
@@
   In the top panel, the black points shows the SAP flux of the pixel with the injected signal, 
-    the green line is the fitting of the SAP flux, and the red line is the \name\ prediction. 
-  In the bottom panel, red and green points represent the \name\ flux and fit flux, 
+    the bold grey line is the fitting of the SAP flux, and the thin red line is the \name\ prediction. 
+  In the bottom panel, red points and grey cross represent the \name\ flux and the fit flux, 
     while the signal value is indicated by the horizontal line. 

### 2015-06-29 documents/cpm.tex
plot explanation

@@
   we present a few comparison between optimized and default hyper-parameters 
-  in Fig~\ref{hyperparameter}.\Bernhard{maybe explain somewhere how SNR is calculated}  
+  in Fig~\ref{hyperparameter}.
 We can see that, in Fig~\ref{hyperparameter}, 
@@
   The optimized hyper-parameter performs better than the default one, 
-    but the results from both situation are close.}
+    but the results from both situation are close.
+  Here the signal strength is determined by mean depth of the transit signal,
+    while the noise level is valued by 
+    using the root-mean-square deviation of every points in a 6-day running window.}
 \end{figure}

### 2015-06-30 documents/cpm.tex
tiny abstract changes

@@
 there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
-The precision of NASA \Kepler\ photometry for exoplanet science ---
-the most precise photometric measurements of stars ever made ---
+The precision of NASA \Kepler\ photometry for exoplanet science---% no spaces around ---
+the most precise photometric measurements of stars ever made---%
 appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
@@
 a data-driven model intended to capture variability but preserve transit signals. 
-The \name\ works at the pixel level; So that
-it can capture more fine-grained information about the variation of the spacecraft.
+The \name\ works at the pixel level so that
+it can capture very fine-grained information about the variation of the spacecraft.
 The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 

### 2015-08-05 documents/cpm.tex
the ' typo
figures caption and citation

@@
 
-\graphicspath{{figures/}}
+\graphicspath{{figures/png/}}
 
@@
 The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
-while not containing any information on possible transits in the target star. In addition, we use the target star’s future and past (auto-regression). 
+while not containing any information on possible transits in the target star. In addition, we use the target star's future and past (auto-regression). 
 By appropriately separating, for each data point, the data into training and test sets, 
@@
   Stars on the same CCD share systematic errors. 
-  The two panels show pixel fluxes (brightnesses) for two stars: (a) KIC 5088536, (b) KIC 5949551; 
+  The two panels show pixel fluxes (brightnesses) for two stars in quarter 5: (a) KIC 5088536, (b) KIC 5949551; 
   here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD, 
@@
   (either in science data or engineering data) and no external information, 
-  for example, measurements from other device, are needed
+  for example, measurements from other device, are needed.
+  And a description of the method in the machine learning context can be found in \cite{icml}
 

### 2015-11-29 documents/ms/ms.tex
PASP main script

--- 2015-06-30 documents/cpm.tex
@@
 \usepackage{graphicx}
-\usepackage{caption} 
-\usepackage{subcaption} 
+\usepackage{subfigure}
+\usepackage[normalem]{ulem}
+%\usepackage{caption} 
+%\usepackage{subcaption} 
+\usepackage{epstopdf}
 \usepackage{color}
@@
 
-\graphicspath{{figures/}}
+%\graphicspath{{figures/png/}}
 
@@
 \newcommand{\todo}[1]{\textbf{#1}}
+\newcommand{\revise}[1]{\textcolor{green}{#1}}
+\newcommand{\remove}[1]{\sout{#1}}
 
@@
 
-\title{
-  Calibrating the pixel-level Kepler imaging data with a causal data-driven model
- \\ 
+\title{ \remove{Calibrating the pixel-level Kepler imaging data with a causal data-driven model\\}
+  \revise{
+  A Causal, Data-Driven Approach to Modeling the Kepler Image Data
+ \\ }
 }
@@
   Dun~Wang\altaffilmark{\ref{CCPP}},
-  Dan~Foreman-Mackey\altaffilmark{\ref{CCPP}},
   David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{CDS},\ref{MPIA},\ref{email}},
+  Daniel~Foreman-Mackey\altaffilmark{\ref{UW},\ref{SF}},
   Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}}
@@
   Max-Planck-Institut f\"ur Intelligente Systeme, T\"ubingen}
+\altaffiltext{\theaddress}{\stepcounter{address}\label{UW}%
+ Astronomy Department, University of Washington, Seattle, WA 98195}
+\altaffiltext{\theaddress}{\stepcounter{address}\label{SF}%
+Sagan Fellow}
 
@@
 it can capture very fine-grained information about the variation of the spacecraft.
-The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
-while not containing any information on possible transits in the target star. In addition, we use the target star’s future and past (auto-regression). 
+\remove{The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
+while not containing any information on possible transits in the target star.} \revise{The CPM models the systematic effects in the time series of a pixel using the pixels
+around many other stars and the assumption that any shared signal in
+these causally disconnected light curves is caused by instrumental
+effects.} In addition, we use the target star's future and past (auto-regression). 
 By appropriately separating, for each data point, the data into training and test sets, 
   we ensure that information about any transit will be perfectly isolated from the model. 
-The method has four hyper-parameters (the number of predictor stars, the auto-regressive window size, 
-and two L2-regularization amplitudes for model components), which we set by cross-validation. 
-We determine a generic set of hyper-parameters that works well for most of the stars and apply the method to a corresponding set of target stars. 
-We find that we can consistently outperform (for the purposes of exoplanet detection) 
-  the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.
+The method has four \remove{hyper-parameters (the number of predictor stars, the auto-regressive window size, 
+and two L2-regularization amplitudes for model components),}
+\revise{tuning parameters---the number of predictor stars, the auto-regressive window size, 
+and two L2-regularization amplitudes for model components,}
+ which we set by cross-validation. 
+We determine a generic set of \remove{hyper-parameters}\revise{tuning parameters} that works well for most of the stars and apply the method to a corresponding set of target stars.
+\remove{We find that we can consistently outperform (for the purposes of exoplanet detection) 
+  the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.} 
+\revise{We find that \name\ can consistently produce relatively low-noise (CDPP) light-curves.
+In this paper, we demonstrate that pixel-level de-trending is possible while retaining transit signals (with a train-and-test framework) and we think that methods like \name\ is generally applicable and might be useful for  K2, TESS, etc, where the data aren't these clean postage stamps like \Kepler.}
 
@@
 
-\section{Ultra-precise photometry}
+\section{Introduction}
 
-The photometric measurements of stars made by the \Kepler\ Satellite are precise enough
+The photometric measurements of stars made by the \Kepler\ \remove{satellite}\revise{space craft} are precise enough
   to permit discovery of exoplanet transits with depths smaller than $10^{-4}$.
@@
   supplemented by various methods for removing small residual spacecraft-induced and stellar-variability trends in the brightnesses,
-  either filtering the data (with things like median filters; \cite{trendfilter})
+  either filtering the data (with things like median filters)
   or fitting the data with flexible models (like polynomials or splines or Gaussian Processes; 
@@
   and thus different sensitivity to variations in the device.
-There are also \emph{intra-pixel} sensitivity variations that can contribute \citep{whitepaper}.
+There are also \emph{intra-pixel} sensitivity variations that can contribute, which was first measured by \revise{\cite{subpixel}}.
 There are small changes in spacecraft temperature,
-  which lead to point-spread function (PSF) and differential (across the focal plane) pointing changes.
+  which lead to point-spread function (PSF) and differential \remove{(across the focal plane)} pointing changes.
 These also lead to changes in pixel and intra-pixel illumination.
@@
   these can effectively transfer variability from one source to another.
-There are additional electronics effects like ``rolling bands'' that put additional features into light-curves.
-There are also probably changes to the detector sensitivity with temperature and time,
+There are additional electronics effects like ``rolling bands'' that put additional features into light-curves \revise{\citep{handbook}}.
+There are also \remove{probably} changes to the detector sensitivity with temperature and time,
   possibly illimunation-history effects,
@@
 
-We propose and advise dealing with these variations in \Kepler\ light-curves by \emph{modeling} them.
-In this context, a model is (at least) a parameterized function that can predict data, given parameter settings,
+\remove{We propose and advise dealing with}\revise{We propose to deal with} these variations in \Kepler\ light-curves by \emph{modeling} them.
+In this context, a model is \remove{(at least)} a parameterized function that can predict data, given parameter settings,
   and an objective function that can be used to set or sample those parameters.
@@
   but \emph{not} interfere with measurements of stellar variability---%
-  is the \Kepler\ Presearch (\sic) Data Conditioning (PDC, \cite{pdc1}).
+  is the \Kepler\ Presearch \remove{(\sic)} Data Conditioning (PDC, \cite{pdc1}).
 The PDC builds on the idea that systematic errors have a temporal structure that can be extracted from ancillary quantities. 
@@
 These data include the temperatures at the local detector electronics below the CCD array, 
-  and polynomials describing the centroid motion of the targets from PA.
+  and polynomials describing the centroid motion of the targets from PA\revise{(Photometric Analysis)}.
 
-In \cite{pdc2,pdc3}, filtered light-curves of other stars are used instead. 
+In \cite{pdc2,pdc3}\remove{, filtered light-curves of other stars are used instead. 
 The light-curve of a target star is projected on the leading eight principal components of these light-curves. 
@@
 The principal components are computed from a set of relatively quiet stars close in position and magnitude. 
-This was done since it was observed that otherwise, too much of the stellar variability was being removed.
+This was done since it was observed that otherwise, too much of the stellar variability was being removed.}
 
-From the point of view of the present paper, 
+\revise{In the most recent version of PDC (PDC-MAP, \cite{pdc2,pdc3}), filtered light-curves of other stars are used
+instead. Using a set of relatively quiet stars on each detector, the
+top 8 principle components are computed for every quarter of Kepler
+data. The maximum a posteriori linear combination of these basis light
+curves---computed using an empirical prior on the trend
+magnitudes---are used to model and remove the systematics in all the
+Kepler light curves. The choice to use such a small number of
+components and to apply priors was made in order to reduce
+over-fitting and retain physical signals after systematics removal.}
+
+\remove{From the point of view of the present paper, 
 one can only guarantee that {\em no} stellar variability is removed if the stars do not depend on time at all.
@@
   and thus the target signal may be compromised. 
-We suspect that this effect is limited in \cite{pdc2,pdc3}, 
-  since only eight principal components are used, which limits the capacity of the model.
+We suspect that this effect is limited in} \cite{pdc2,pdc3}, 
+  \remove{since only eight principal components are used, which limits the capacity of the model.}
 
-PDC ``de-trends'' the \Kepler\ light-curves by removing those parts that are explained by the basis light-curves
+PDC \remove{``de-trends''}\revise{"co-trends" or calibrates} the \Kepler\ light-curves by removing those parts that are explained by the basis light-curves
   generated from a principal components analysis (PCA) of filtered light-curves.
@@
   through strong regularization and a train-and-test framework. 
+  \revise{PDC mitigates overfitting by
+reducing the freedom of the model and applying empirical priors to the
+fit coefficients.}
 \item 
@@
 \item
-the purpose of \name\ is to search for exoplanets, so in \name, intrinsic stellar
-  variability is also removed as well as the systematics.
+\remove{the purpose of \name\ is to search for exoplanets, so in \name, intrinsic stellar
+  variability is also removed as well as the systematics.}
+  \revise{The current version of \name\ is
+tuned to remove systematics while minimizing the impact on exoplanet
+transit signals. It makes no attempt to retain lower frequency signals
+that can be produced by other astrophysical signals.}
 \item 
@@
 The two methods (\name\ and PDC) are similar however,
-  in that they both make the (implicit or explicit) assumption that whatever spacecraft effects are imprinting variability on a stellar light-curve
+  in that they both make the \remove{(implicit or explicit)} assumption that whatever spacecraft effects are imprinting variability on a stellar light-curve
   must also be imprinting similar or related variability on other light-curves.
-In their current versions, they also assume that the relationships can be captured with linear models (although we have also used nonlinear predictions methods for \name, which would be harder to do in PDC).
+\remove{In their current versions, they also assume that the relationships can be captured with linear models (although we have also used nonlinear predictions methods for \name, which would be harder to do in PDC).}
 By going to the pixel level (unlike the PDC, which works at the photometry level),
@@
 Before we start, a few reminders about the \Kepler\ data are in order:
-The satellite always observes precisely the same field, at fixed pointing (as closely as possible).
-Only a few percent of the 80 million pixels in the focal plane are telemetered down
+The \remove{satellite}\revise{space craft} \remove{always observes}\revise{observed} precisely the same field, at fixed pointing (as closely as possible).
+\revise{About 6\% of the 96,465,600 pixels}\remove{Only a few percent of the 80 million pixels} in the focal plane are telemetered down
   to Earth from each 30-min exposure;
-  the telemetered pixels are associated with \Kepler\ target stars chosen for study by the \Kepler\ Team.
-The satellite is rolled by 90~deg every 90-ish days (to satisfy Solar-Angle constraints).
+  the telemetered pixels are associated with \Kepler\ target stars chosen for study by the \Kepler\ Team \revise{(along with a non-trivial set collateral pixels used for calibration)}.
+The \remove{satellite}\revise{space craft} is rolled by 90~deg every \remove{90-ish}\revise{93} days (to satisfy Solar-Angle constraints).
 The focal plane contains many CCDs;
   this plus the 90-deg rotations means that each star is at a particular location
-  on a particular CCD for 90-ish-day contiguous periods of time.
+  on a particular CCD for \remove{90-ish-day}\revise{quarter} contiguous periods of time.
 The PSF varies strongly across the field and is badly sampled.
@@
 
-The scope of this project is an intervention---\name---that makes the \Kepler\ transit photometry more precise.
+\remove{The scope of this project is an intervention---\name---that makes the \Kepler\ transit photometry more precise.}
 
 We describe the method and deliver all the relevant code in a public, open-source repository.
-We also provide an interface to the \Kepler\ data that delivers improved ``\name\ photometry''
+We also provide an interface to the \Kepler\ data that \remove{delivers improved ``\name\ photometry''}\revise{can be used
+to produce ''\name\ photometry''}
   for every \Kepler\ target.
@@
 
-The second general idea about data-driven modelling is the investigator's beliefs
-  about the causal processes that generate the data
-  are crucial in restricting the kinds of data that can be used as input to the model.
-That is, different assumptions about the physical properties of the data
-  and the data-taking system
-  lead to different structures for the data-driven model.
+The second general idea about data-driven modelling is the investigator's beliefs about the causal processes that generate the data are crucial in restricting the kinds of data that can be used as input to the model.
+That is, different assumptions about the physical properties of the data and the data-taking system lead to different structures for the data-driven model.
 In the case of \Kepler\ data, 
@@
   is that both stars are being observed by the same device or spacecraft.
-That is, one star's pixels can be used to predict another star's pixels
-  inasmuch as spacecraft issues imprint on both stars in related ways;
+That is, one star's pixels can be used to predict another star's pixels inasmuch as spacecraft issues imprint on both stars in related ways;
   they share a common cause---the systematics.  
@@
   but also intrinsic stellar variability,
-  the predictive model will be permitted to use as input pixels that \emph{do} overlap the 
-  target star.
-In what follows, we are going to use input data both from pixels of other stars and the  
-target star pixels' past and future.
-These models ought to remove both spacecraft variability and intrinsic stellar variability, 
-which is optimal for exoplanet transit searching.
+  the predictive model will be permitted to use as input pixels that \emph{do} overlap the target star.
+In what follows, we are going to use input data both from pixels of other stars and the target star pixels' past and future.
+These models ought to remove both spacecraft variability and intrinsic stellar variability, which is \remove{optimal}\revise{optimized} for exoplanet transit searching.
 
-\begin{figure}[htb]
-\centering
-\begin{subfigure}[htb]{0.48\columnwidth}
-\includegraphics[width=\columnwidth]{5088536-5}
-\caption{}
-\end{subfigure}%
-\hfill
-\begin{subfigure}[htb]{0.48\columnwidth}
-\includegraphics[width=\columnwidth]{5949551-5}
-\caption{}
-\end{subfigure}
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=0.4\textwidth]{f1a}
+\includegraphics[width=0.4\textwidth]{f1b}
+\end{center}
 \caption{
@@
   Stars on the same CCD share systematic errors. 
-  The two panels show pixel fluxes (brightnesses) for two stars: (a) KIC 5088536, (b) KIC 5949551; 
+  The two panels show pixel fluxes (brightnesses) for two stars in quarter 5. \emph{Left:} KIC 5088536, \emph{Right:} KIC 5949551; 
   here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD, 
@@
   that effectively reduce freedom without explicitly reducing the number of parameters).
-In each case, the restriction on model freedom is controlled by some \emph{hyper-parameter}
+In each case, the restriction on model freedom is controlled by some \emph{\remove{hyper-parameter}\revise{tuning parameters}}
   (such as the number of inputs, or number of principal components, or the strength of the smoothness prior).
-The hyper-parameters can be set or tested with tools like cross-validation,
+The \remove{hyper-parameters}\revise{tuning parameters} can be set or tested with tools like cross-validation,
   the fully marginalized likelihood (Bayes factor or evidence),
@@
 What we will show in what follows is that the \name\ photometry does not distort
-  artificial exoplanet transit signals injected into real \Kepler\ pixel-level data.
-  and promising properties of the \name\ outputs.
+  artificial exoplanet transit signals injected into real \Kepler\ pixel-level data
+  and promising properties of the \name\ outputs \revise{on real Kepler light-curves}.
 In the end, the value of the \name\ will be demonstrated by the scientific projects it enables.
@@
 We also want to emphasis that all the calibration in this paper for \Kepler is 
-  based on the assumption that the device is 'self-calibratable', 
+  based on the assumption that the device is \remove{'self-calibratable'}\revise{can be self-calibrated}, 
   which means all the information we need to calibrate the device are contained in the device itself 
   (either in science data or engineering data) and no external information, 
-  for example, measurements from other device, are needed
+  for example, measurements from other device, are needed.
+  And a description of the method in the machine learning context can be found in \cite{icml2015}
 
-\section{\name\ specification and hyper-parameters}
+\section{\name\ specification and \revise{tuning parameters}}
 \subsection{\name\ model}
-Each individual \Kepler\ target star is, for each quarter (each 90-ish-day period)
+Each individual \Kepler\ target star is, for each quarter (each \remove{90-ish-day})
   on a particular CCD on the \Kepler\ focal plane.
 Associated with each target star is some set of pixels,
-  located in a small contiguous patch more-or-less centered on the target star,
+  located in a small contiguous patch \remove{more-or-less} centered on the target star,
   and telemetered down once for every 30-min exposure.
-(Here we are ignoring all short-cadence data that is taken in a different mode with shorter exposures.)
+Here we are ignoring all short-cadence data that is taken in a different mode with shorter exposures.
 That is, each telemetered pixel in each CCD is associated with a particular \Kepler\ target star.
@@
 Let's consider a particular pixel $m$ in the focal plane in one particular month
-  (here we always use data per month rather than quarter,  since there are discontinuities between every 30-ish-day period).
+  (here we always use data per month rather than quarter,  since there are discontinuities between every \remove{30-ish-day period}\revise{month}).
 In that month, the spacecraft delivers $N\sim 1300$ measurements $I_{m,n}$
   of the intensity falling in pixel $m$ at the $N$ times $t_n$ at which exposures were taken during the month.
-(For intensity measurements $I_{m,n}$ here we are using pixels from the Target Pixel Files on MAST
+(For intensity measurements $I_{m,n}$ here we are using pixels from \revise{the FLUX column of Target Pixel File, which is flux of each pixel after processed by the pipeline module CAL, the removal of the interpolated background, and the removal of cosmic rays} on MAST
   \footnote{\url{http://archive.stsci.edu/kepler/}}, for details of the TPF, 
@@
   is the \emph{pixel set} $\set{M}_m$ associated with pixel $m$.
-   To rule out any direct optical cross-talk by starry 
-light, we require that the predictor pixels are from stars
-sufficiently far away from the target star (at least 20 pixels distance on the CCD).
+  \remove{To rule out any direct optical cross-talk by starry light}
+  \revise{To minimize the effects of blending with and crosstalk from nearby stars}, we require that the predictor pixels are \remove{from stars
+sufficiently far away from the target star (at least 20 pixels distance on the CCD).}
+\revise{from stars at least 20 pixels away from the target star.}
 Note that because the set $\set{M}_m$ is of pixels associated with \emph{different} stars
@@
   nor any of its neighbors in a time window of half-width $\Delta_t$. 
+\revise{The width of the window $\Delta t$ is set to be the duration of the transits to preserve transits while still predicting the systematics and stellar variability well.}
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.8\columnwidth]{train_and_test}
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=0.8\textwidth]{f2}
+\end{center}
 \caption{
@@
 \begin{eqnarray}
-I_{v,n} = I_{m,n-R-k}\ or\ I_{v,n} = I_{m,n+R+k},
+I_{v,n} = I_{m,n-R-k}\ or\ I_{v,n} = I_{m,n+R+k}
 \quad,
@@
   that is, there will be a separate best-fit value for the parameters for every $I_{m,n}$.
-If we presume that the residuals away from the prediction are normally distributed with zero mean
-  and known variance,
-  likelihood optimization reduces to $\chi^2$ minimization.
+\revise{And the pixel $I_{m',n}$ from other stars at the same time point n is used as input to make prediction.}
+If we presume that the residuals away from the prediction are normally distributed with zero mean and known variance, likelihood optimization reduces to $\chi^2$ minimization.
 We add to the standard chi-squared definition a regularization term
@@
 \begin{eqnarray}
-\chi^2_{m,n}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{m,n'} - I^{\ast}_{m,n',n}]^2}{\sigma^2_{m,n'}}
+\chi^2_{m,n}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{m,n'} - \revise{I^{\ast\ast}_{m,n',n}}]^2}{\sigma^2_{m,n'}}
                  + \lambda_{a}\sum_{m'\in\set{M}_m}a_{m,n,m'}^2 + \lambda_{b}\sum_{v\in\set{V}_m}b_{m,n,v}^2
 \\
-I^{\ast}_{m,n',n} &=& \sum_{m'\in\set{M}_m} a_{m,n,m'}\,I_{m',n'} + \sum_{v\in\set{V}_m} b_{m,n,v}\,I_{v,n'}
+\revise{I^{\ast\ast}_{m,n',n}} &=& \sum_{m'\in\set{M}_m} a_{m,n,m'}\,I_{m',n'} + \sum_{v\in\set{V}_m} b_{m,n,v}\,I_{v,n'}
 \quad,
@@
   In general, $\lambda_a$ and $\lambda_b$ could depend on $m,n$, however, we do not make use of this freedom. 
-  Here the prediction $I^{\ast}_{m,n',n}$ has three indices, 
+  Here the pixel \revise{value $I^{\ast\ast}_{m,n',n}$ is different from the prediction $I^{\ast}_{m,n}$.
+It is not the prediction for time $n'$ using $a_{m,n',m'}, b_{m,n',v}$ as coefficient, but using the coefficient $a_{m,n,m'}, b_{m,n,v}$ that is trained for prediction in time n to set the value.
+It is purely a median product in the process of training the model.} It has three indices,
   because in \name\ the $\chi^2$ minimization for every time
   point is independent and the third index--$n$ indicates 
-  which time point the prediction $I^{\ast}_{m,n',n}$ is being trained for, 
+  which time point the model\remove{prediction $I^{\ast}_{m,n',n}$} is being trained for, 
   the detail of the independent $\chi^2$ minimization will be discussed below.
@@
 When we are computing the objective function $\chi^2_{m,n}$,
-  we are using only time points $n'\in\set{N}_n$ that don't overlap the target (or test) time point $n$.
+  we are using only time points $n'\in\set{N}_n$ that don't overlap the target \remove{(or test)} time point $n$.
 We train the model---that is, set the parameters $a_{m,n,m'}$ and $b_{m,n,v}$---%
@@
 Fortunately, given the form of the model,
-  this minimization is just a linear solve (linear operation on the data).
+  this minimization is just a linear solve \remove{(linear operation on the data)}.
 Importantly however, and perhaps surprisingly, the objective function $\chi^2_{m,n}$ is \emph{different}
   for every target data point (pixel value to be predicted) $I_{m,n}$;
-  we have to do an \emph{independent optimization} (or really linear solve)
+  we have to do an \emph{independent optimization} \remove{(or really linear solve)}
   of the parameters for every pixel value we want to predict at every time.
@@
 By construction of our objective function, this is truly a prediction,
-  in the sense that the optimization (or solve) that produced the parameters
-  (and thus the prediction)
+  in the sense that the optimization \remove{(or solve)} that produced the parameters
+  \remove{(and thus the prediction)}
   did not make use of $I_{m,n}$ itself,
   nor even any of the pixel values that are nearby in angle or time
-  (as described above).
+  \remove{(as described above)}.
   With all the predicted pixel values $I^{\ast}_{m,n}$ of the target star,  
@@
 aperture while zero outside the optimal aperture.
-As we have noted above and below, these photometric estimators are not optimal for any purpose,
+As we have noted above and below, these photometric estimators are not optimal for any purpose, \revise{and chances are that the aperture may not be able to capture all the light from the star or there can be issues of crowding and consequent contamination flux from nearby stars,}
   but improving them is beyond the scope of this project.
@@
 
-\subsection{Hyper-parameters}
-The \name\ has 4 hyper-parameters--- 
+\subsection{\revise{Tuning parameters}}
+The \name\ has 4 \remove{hyper-parameters}\revise{tuning parameters}--- 
   the number of predictor stars Q (or number of predictor pixels P), 
@@
   and the two regularization strength $\lambda_{a}$ and $\lambda_{b}$.
-To set these 4 hyper-parameters, 
+To set these 4 \remove{hyper-parameters}\revise{tuning parameters}, 
   in principle we need to run something like a cross-validation on every single star to optimize performance.
@@
 Therefore, in this paper, 
-  we just set a general set of ``default'' hyper-parameters ($P=4000$, $Q=3$, $\lambda_a=1e5$, $\lambda_a=1e5$), 
+  we just set a general set of ``default'' \remove{hyper-parameters}\revise{tuning parameters} ($P=4000$, \remove{$Q=3$}\revise{$S=3$}, $\lambda_a=1e5$, $\lambda_a=1e5$), 
   which works well in most of the stars without high variability. 
-To show how this general set of hyper-parameters performs, 
-  we present a few comparison between optimized and default hyper-parameters 
+To show how this general set of \remove{hyper-parameters}\revise{tuning parameters} performs, 
+  we present a few comparison between optimized and default \remove{hyper-parameters}\revise{tuning parameters} 
   in Fig~\ref{hyperparameter}.
@@
   there is less variation in the \name\ flux 
-  when we use optimized hyper-parameters (green points in second panel) 
+  when we use optimized \remove{hyper-parameters}\revise{tuning parameters} (grey points in second panel, \revise{$Q=60$, $S=3$, $\lambda_a=1e7$, $\lambda_a=1e5$}) 
   than when we use the default one (red points in the bottom panel). 
 In addition, the optimized flux has higher signal to noise ratio of the known transit than the default. 
-However, the performance of default hyper-parameters is acceptable 
-  and we will use this set of hyper-parameters throughout the rest of the paper 
+However, the performance of default \remove{hyper-parameters}\revise{tuning parameters} is acceptable 
+  and we will use this set of \remove{hyper-parameters}\revise{tuning parameters} throughout the rest of the paper 
   to show the general performance of \name. 
+\revise{It is also worth to mention that the tuning parameters are optimized in a relatively coarse grid, which means the performance can still be improved when setting the tuning parameters more precisely.}
+\revise{There are also parameters such as train-and-test window size, the CCD constraint on the predictor stars, the minimum distance of the predictor stars and the ranking algorithm to select predictor stars.
+In \name\ we set these parameters heuristically, but they could be open for discussion.}
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=\columnwidth]{compare_10187017_bw}
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=\textwidth]{f3}
+\end{center}
 \caption{
   \label{hyperparameter} 
-  Comparison between default and optimized hyper-parameters. 
+  Comparison between default and optimized \remove{hyper-parameters}\revise{tuning parameters}. 
   In the top panel, SAP flux is plotted in black, 
-    \name\ prediction of default hyper parameters is in thin red line, 
-    \name\ prediction of optimized hyper-parameters is in bold grey line. 
-  The middle panel shows the \name\ flux of the optimized hyper-parameters, 
-    while \name\ flux of the default hyper-parameters is in the bottom panel, 
+    \name\ prediction of default \remove{hyper-parameters}\revise{tuning parameters} is in thin red line, 
+    \name\ prediction of optimized \remove{hyper-parameters}\revise{tuning parameters} is in bold grey line. 
+  The middle panel shows the \name\ flux of the optimized \remove{hyper-parameters}\revise{tuning parameters}, 
+    while \name\ flux of the default \remove{hyper-parameters}\revise{tuning parameters} is in the bottom panel, 
     the two vertical blue lines indicate the location of the transit signal, 
     and signal to noise ratio is calculated in both situation. 
-  The optimized hyper-parameter performs better than the default one, 
+  The optimized \remove{hyper-parameters}\revise{tuning parameters} performs better than the default one, 
     but the results from both situation are close.
@@
 
-\clearpage
+\section{Examples and results}
 
-\subsection{Transit signal in \name}
+\subsection{\name's effect on transit signals}
 One important feature of \name\ is that we use the train-and-test framework to preserve 
 the transit signal. To show how well train-and-test framework performs, we make the
-following experiments on \Kepler\ data as shown in Fig~\ref{distortion}
-In the light-curve of single pixel (1, 2) of KIC 9822284, a 10-hrs fake signal 
+following experiments on \Kepler\ data as shown in Fig~\ref{distortion}.
+In the light-curve of \revise{KIC 9822284, simpy box model with different depth (from 100 ppm to 1\%) is injected}\remove{single pixel (1, 2) of KIC 9822284, a 10-hrs fake signal 
 with amplitude 1.0005 is inserted. To insert the signal, we simply multiply the light-curve 
 by the factor of 1.0005, which makes the little bump in the middle of the SAP light-curve 
-(black points in the first panel). With the distorted light-curve, we both applied the 
-\name\ and ordinary fitting to the data. In the result, we can see that both \name and 
-ordinary fit the light-curve quite well outside the range of inserted signal. However, 
-when examine how these two models preserve the signal that we care, the ordinary
-fitting fit out about 30 percent of the signal, while \name\ almost preserve the whole 
-original amplitude. Therefore,  by this simple experiment, we are able to show that 
-the train-and-test framework used here is capable to keep the transit signal with 
-a particular time scale. And we want to emphasise that it is crucial for searching for
-exoplanets, especially the small ones such as earth-like planets, which only have  
-about tens of parts per million signal in the light-curve.
+(black points in the first panel).} With the distorted light-curve, both \name\ and "ordinary fitting" are applied the to the data. 
+\revise{By "ordinary fitting", we mean fitting with all the data,  in comparison with the \name\, in which for each data point prediction is made without the data in the excluded region.}  
+In the result, we can see that both methods fit the light-curve quite well outside the range of inserted signal. 
+However, when examine how these two models preserve the signal that we care, the ''ordinary fitting'' fit out a large portion of the signal, while \name\ can preserve the whole 
+original amplitude. Therefore,  by this simple experiment, we are able to show that the train-and-test framework used here is capable to keep the transit signal with a particular time scale. 
+Also we want to emphasise that it is crucial for searching for
+exoplanets, especially the small ones such as earth-like planets, which only have \remove{about tens of parts per million}\revise{$\backsim 100\ ppm$} signal in the light-curve.
+\revise{But there still exits some issue in the \name.
+The \name\ does not predict the light-curve very well around the box model, since in these regions the prediction is under the strong influence of the box model or "transit signal". 
+Thus \name\ will introduce some distortion around the transit signal and the distortion increases with the depth of the signal. This issue will be discussed in detail in section 5.}
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=\columnwidth]{distortion_9822284_normal_bw}
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=0.32\textwidth]{f4a}
+\includegraphics[width=0.32\textwidth]{f4b}
+\includegraphics[width=0.32\textwidth]{f4c}
+\end{center}
 \caption{
@@
   \name\ preserves transit signals.
-  Fake signal with amplitude 1.0005 is inserted into the single pixel (1, 2) of star KIC 9822284. 
-  In the top panel, the black points shows the SAP flux of the pixel with the injected signal, 
-    the bold grey line is the fitting of the SAP flux, and the thin red line is the \name\ prediction. 
-  In the bottom panel, red points and grey cross represent the \name\ flux and the fit flux, 
-    while the signal value is indicated by the horizontal line. 
+  \remove{Fake signal with amplitude 1.0005 is inserted into the single pixel (1, 2) of star KIC 9822284.}\revise{Simply box models with depth from $100 ppm to 1\%$ is injected into the light-curve of star KIC 9822284.
+Plot (a) and (b) show the results from box model depth to be 500 ppm and 3000 ppm.}
+  In the top panel, the black points shows the SAP flux of the pixel with the injected signal, the bold grey line is the fitting of the SAP flux, and the thin red line is the \name\ prediction. 
+  In the bottom panel, red points and grey cross represent the \name\ flux and the fit flux, while the signal value is indicated by the horizontal line. 
   \name\ largely preserves the signal while the fitting flux overfit the signal.} 
+  \revise{But the \name\ flux is distorted a little around the box model. 
+  And there is more distortion with a strong signal.
+  Plot (c) shows the signal depth measured in \name\ and fitting flux relative to the true depth with different box model depth.
+\name\ can consistently preserve more signal than the "ordinary fitting".}
 \end{figure}
-
-\clearpage
-
-\section{Examples and results}
 
@@
 indicating the noise level seen by a transit signal with a given duration. 
+\revise{In this paper, the CDPP is calculated with 12 bandpass filter using the equations 6-8 in section 3.3 of \citep{cdpp1}.
+And the CDPP of both PDC and \name\ is estimated with the same algorithm.}
 The duration is typically chosen to be 3, 6, or 12 hours. 
@@
   since PDC is not designed to remove stellar variability, 
-  and we want to compare \name\ and PDC on the same footing.
+  and we want to compare \name\ and PDC on the close footing.
 Fig.~\ref{cdpp} presents our CDPP comparison of \name\ and PDC, 
-  showing that our method (\name) outperforms PDC.
+  \remove{showing that our method (\name) outperforms PDC.}\revise{4 quarters' (quarter 5, 6, 7, 8.
+Data of quarter 5 are from Kepler data release 21 and other data are from Kepler data release 24---the current version) data are used to show that \name\ has a consistent performance over a whole orbital period of the Kepler photometer (372 days).
+We also want to emphasis that both \name\ and PDC are presented here does not mean that it is a competition.
+Since PDC is designed to preserve stellar variability, it is not fair to put \name\ and PDC into competition.
+The CDPP comparison is made only to give a relative reference how \name\ can perform according to PDC, the Kepler "gold standard"}
 
-\begin{figure}[htb]
-\centering
-\begin{subfigure}[htb]{0.33\textwidth}
-\includegraphics[width=\textwidth]{kic_11295426_pdc}
-\end{subfigure}%
+\revise{In order to show the overall ability that \name\ have in exoplanet searching, a comparison between \name\ and median filter (a widely used de-trend method) is presented in Fig.~\ref{filter}.
+This is a more comprehensive comparison, since not only noise level (CDPP) is evaluated,  but how well both methods can retrieve signal from the light curve is also under consideration.
+In the example, a 200 ppm box model signal is injected into a quiet star KIC 8846139 in quarter 5.
+With the signal injected light curve,  both methods---median filter and \name\ are applied.
+As shown in Fig.~\ref{filter}, when  the window size is bigger than 24 hours, \name\ performs better both in terms of CDPP and signal strength.
+As expected, when the window size gets smaller, CDPP decreases,  while the signal strength retrieved from the light curve also falls off.
+Although median filter with window size smaller than 24 hours is able to generate cleaner light curves (lower CDPP level) than \name, it largely distorts the signal that we care about.
+Imagining in an extreme case, light curves generated by a half hour median filter will have zero CDPP, as well as zero signal strength.
+If we examined the ratio of the signal strength to the CDPP (signal to noise ratio) in this example, it results that \name\ can always have a signal to noise ratio around 8, while the median filter method can only achieve a ratio around 6 in the best circumstance, when window size is 24 hours.
+Therefore, the example intuitively exhibits that \name\ is able to generate light curves with low noise level as well as preserve the transit signal.}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=0.32\textwidth]{f5a}
 \hfill
-\begin{subfigure}[htb]{0.33\textwidth}
-\includegraphics[width=\textwidth]{kic_11401755_pdc}
-\end{subfigure}%
+\includegraphics[width=0.32\textwidth]{f5b}
 \hfill
-\begin{subfigure}[htb]{0.33\textwidth}
-\includegraphics[width=\textwidth]{kic_5966154_pdc}
-\end{subfigure}
+\includegraphics[width=0.32\textwidth]{f5c}
 
-\begin{subfigure}[htb]{0.33\textwidth}
-\includegraphics[width=\textwidth]{kic_3544595_pdc}
-\end{subfigure}%
+\includegraphics[width=0.32\textwidth]{f5d}
 \hfill
-\begin{subfigure}[htb]{0.33\textwidth}
-\includegraphics[width=\textwidth]{kic_4914423_pdc}
-\end{subfigure}%
+\includegraphics[width=0.32\textwidth]{f5e}
 \hfill
-\begin{subfigure}[htb]{0.33\textwidth}
-\includegraphics[width=\textwidth]{kic_9892816_pdc}
-\end{subfigure}
+\includegraphics[width=0.32\textwidth]{f5f}
 
-\begin{subfigure}[htb]{0.33\textwidth}
-\includegraphics[width=\textwidth]{kic_8866102}
-\end{subfigure}%
+\includegraphics[width=0.32\textwidth]{f5g}
 \hfill
-\begin{subfigure}[htb]{0.33\textwidth}
-\includegraphics[width=\textwidth]{kic_5695396}
-\end{subfigure}%
+\includegraphics[width=0.32\textwidth]{f5h}
 \hfill
-\begin{subfigure}[htb]{0.33\textwidth}
-\includegraphics[width=\textwidth]{kic_9950612}
-\end{subfigure}
-\begin{subfigure}[htb]{0.33\textwidth}
-\includegraphics[width=\textwidth]{kic_8292840}
-\end{subfigure}%
+\includegraphics[width=0.32\textwidth]{f5i}
+
+\includegraphics[width=0.32\textwidth]{f5j}
 \hfill
-\begin{subfigure}[htb]{0.33\textwidth}
-\includegraphics[width=\textwidth]{kic_9451706}
-\end{subfigure}%
+\includegraphics[width=0.32\textwidth]{f5k}
 \hfill
-\begin{subfigure}[htb]{0.33\textwidth}
-\includegraphics[width=\textwidth]{kic_6677841}
-\end{subfigure}
+\includegraphics[width=0.32\textwidth]{f5l}
+\end{center}
 
@@
 
-\begin{figure*}[htb]
-\centering
-\begin{subfigure}[htb]{0.33\columnwidth}
-\includegraphics[width=\columnwidth]{pdc_cdpp12_r}
-\caption{}
-\end{subfigure}%
-%\hfill
-\begin{subfigure}[htb]{0.33\columnwidth}
-\includegraphics[width=\columnwidth]{boxplot_r}
-\caption{}
-\end{subfigure}%
-%\hfill
-\begin{subfigure}[htb]{0.33\columnwidth}
-\includegraphics[width=\columnwidth]{pdc_cdpp12_hist_r100}
-\caption{}
-\end{subfigure}
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=0.32\textwidth]{f6a}
+\includegraphics[width=0.32\textwidth]{f6b}
+\includegraphics[width=0.32\textwidth]{f6c}
+
+\includegraphics[width=0.32\textwidth]{f6d}
+\includegraphics[width=0.32\textwidth]{f6e}
+\includegraphics[width=0.32\textwidth]{f6f}
+
+\includegraphics[width=0.32\textwidth]{f6g}
+\includegraphics[width=0.32\textwidth]{f6h}
+\includegraphics[width=0.32\textwidth]{f6i}
+
+\includegraphics[width=0.32\textwidth]{f6j}
+\includegraphics[width=0.32\textwidth]{f6k}
+\includegraphics[width=0.32\textwidth]{f6l}
+\end{center}
 \caption{
@@
   Comparison of the proposed method (\name) to the \Kepler\ Pre-search Data Conditioning (PDC) method 
-    in terms of Combined Differential Photometric Precision (CDPP) (see text). 
+    in terms of Combined Differential Photometric Precision (CDPP).
+  \revise{Row 1-4 shows the CDPP estimation throgh quarter 5 to quarter 8. In each row:} 
   Plot (a) shows our performance (red) vs.\ the PDC performance in a scatter plot, as a function of star magnitude 
     (note that larger magnitude means fainter stars, 
-    and smaller values of CDPP indicate a higher quality as measured by CDPP.  
+    and smaller values of CDPP indicate a higher quality as measured by CDPP.)
   Plot (b) bins the same dataset and shows box plots within each bin, 
@@
   Note that the red histogram has more mass towards the left, i.e., smaller values of CDPP, 
-    indicating that our method overall outperforms PDC, the Kepler ``gold standard.'' 
+    indicating that our method \remove{overall outperforms PDC, the Kepler ``gold standard.'' } \revise{process the \Kepler\ light-curve to a lower noise level.}
 }
-\end{figure*}
+\end{figure}
 
-\clearpage
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=\textwidth]{f7a}
+\end{center}
+\caption{
+  \label{filter} 
+\revise{Comparison of \name\ to the median filter method (based on PDC light curve) with different filter window size.
+200 ppm box model signal is injected into the light curve of KIC 8846139 in quarter 5.
+Both \name\ and median filter method are applied to the light curve after injection.
+In the first panel, CDPP estimate of the median filtered light curve is plotted as a function of the filter window size (blue dots) and the red dash line indicates the CDPP level of CPM.
+In the second panel, the signal strength measured from the median filtered light curve is plotted as a function of the filter window size (blue dots), while the red dash line indicates the signal strength retrieved from the \name\ light curve.
+The grey dash line shows the injected signal strength.
+Smaller window size reduces the noise level (CDPP) of the median filtered light curve, while distort the signal more.
+\name\ outperforms median filter in terms of signal to noise ratio.}
+}
+\end{figure}
 
@@
 However, 
-  when it comes to earth-like planets (only about 20 ppm transit signal around a sun-like star),
-  any reduction or distortion of the signal is unacceptable. 
+  when it comes to earth-like planets (only about \remove{20 ppm}\revise{$\backsim 100\ ppm$} transit signal around a sun-like star),
+  \remove{any reduction or distortion of the signal is unacceptable.}
+  \revise{preventing transit signal from reduction or distortion is important.} 
 In comparison, in order to achieve higher precision for earth-like planet searching, 
@@
   which is assumed to be caused by the spacecraft effects (or systematics).
-However, in section 4, we show that \name\ performs better than PDC, 
+\remove{However, in section 4, we show that \name\ performs better than PDC, 
   in that it has a overall low noise level (CDPP).
-We think the outperformance mainly caused by two factor.
+We think the outperformance mainly caused by two factor.}
+\revise{However, the main difference between \name\ and PDC lays on two factor.}
 One is that \name\ calibrates every single pixel separately, 
@@
 
-However, apart from the outstanding performance in calibrating the data,  
-  the \name\ still has several issues. 
+However, apart from the outstanding performance in calibrating the data, the \name\ still has several issues. 
 Based on our assumption of the causal structure of the \Kepler\ data, 
@@
 Another issue of the \name\ is that when there are strong transit signals in the light-curve,  
-  one can find distortion around the these signals.
+  one can find distortion around these signals.
 We think this problem is caused by the train-and-test framework.
@@
 
+\revise{Another issue or improvement that can be considered for \name\ is the predictor selection algorithm. 
+In \name\, a simple selection policy is applied, in which closest stars in magnitude on the same CCD channel are selected.
+This algorithm might be reasonable, since intuitively, the response function of CCD might be similar for stars with similar brightness.
+However, Kepler is a complicated system.
+Systematics like rolling bands may affect only some of the stars.
+Chances are that "bad predictors" may be included into the set of predictor stars to distort the \name\ prediction or \name\ might miss some of the "good predictors", in which case, it can not capture some of the systematics signature.
+Although we also want to mention that in \name\, a huge set of predictors (4000 pixels from other stars) are used, which somehow ensures the model perform well in general, it still remains an unsolved issue for \name.
+In this paper, we did not purse the optimized selection algorithm, because we want to make the model as simple as possible.
+But in order to get an optimized performance for \name, how to select and rank the predictor stars is an important and unavoidable issue.}
+
+\revise{As we have mentioned before in this paper,  since \name\ needs to make prediction for every data points in the light curve, it is quite time-cosuming to process the complete Kepler data set with \name.
+Here we presents an \name\ runtime estimation based on our experience.
+For a light curve of duration three months (one quarter), \name\ took about 7 hours on a single core (Ivy Bridge x86 64 3.0GHz).}
+
 However, despite all the problems mentioned in the \name,
@@
 As we know, \Kepler\ \project{K2} \citep{k2} data are suffering from the broken-down of reaction wheels, 
-  which makes the satellite hard to control and introduce significant systematics. 
+  which makes the \remove{satellite}\revise{space craft} hard to control and introduce significant systematics. 
 Flexible data-driven model \citep{dfm} has already shown the power on the \project{K2} data 
@@
 Moreover, in 2017, NASA is planning the launch of another space telescope---
-  \project{TESS} (Transiting Exoplanet Survey Satellite, \cite{tess}), 
+  \project{TESS} (Transiting Exoplanet Survey \remove{satellite}\revise{space craft}, \cite{tess}), 
   which will perform an all-sky survey for small (earth-like) planets of nearby M stars. 
@@
 \clearpage
-
 \bibliography{cpm}
+%\input{cpm.bbl}
+\clearpage
 

### 2016-02-08 documents/ms/ms.tex
Hogg's first 12 pages of comments

@@
 \usepackage{natbib}
-
+\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
 %\graphicspath{{figures/png/}}
+\definecolor{darkgreen}{RGB}{0, 64, 0}
 
@@
 \newcommand{\todo}[1]{\textbf{#1}}
-\newcommand{\revise}[1]{\textcolor{green}{#1}}
+\newcommand{\revise}[1]{\textcolor{darkgreen}{#1}}
 \newcommand{\remove}[1]{\sout{#1}}
@@
 while not containing any information on possible transits in the target star.} \revise{The CPM models the systematic effects in the time series of a pixel using the pixels
-around many other stars and the assumption that any shared signal in
+of many other stars and the assumption that any shared signal in
 these causally disconnected light curves is caused by instrumental
@@
 and two L2-regularization amplitudes for model components),}
-\revise{tuning parameters---the number of predictor stars, the auto-regressive window size, 
+\revise{tuning parameters---the number of predictor stars or pixels, the auto-regressive window size, 
 and two L2-regularization amplitudes for model components,}
  which we set by cross-validation. 
-We determine a generic set of \remove{hyper-parameters}\revise{tuning parameters} that works well for most of the stars and apply the method to a corresponding set of target stars.
+We determine  \remove{a generic set ofhyper-parameters}\revise{values for tuning parameters} that works well for most of the stars and apply the method to a corresponding set of target stars.
 \remove{We find that we can consistently outperform (for the purposes of exoplanet detection) 
   the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.} 
-\revise{We find that \name\ can consistently produce relatively low-noise (CDPP) light-curves.
-In this paper, we demonstrate that pixel-level de-trending is possible while retaining transit signals (with a train-and-test framework) and we think that methods like \name\ is generally applicable and might be useful for  K2, TESS, etc, where the data aren't these clean postage stamps like \Kepler.}
+\revise{We find that \name\ can consistently produce low-noise light-curves.
+In this paper, we demonstrate that pixel-level de-trending is possible while retaining transit signals and we think that methods like \name\ are generally applicable and might be useful for  K2, TESS, etc, where the data aren't clean postage stamps like \Kepler.}
 
@@
 
-The photometric measurements of stars made by the \Kepler\ \remove{satellite}\revise{space craft} are precise enough
+The photometric measurements of stars made by the \Kepler\ \remove{satellite}\revise{spacecraft} are precise enough
   to permit discovery of exoplanet transits with depths smaller than $10^{-4}$.
@@
   or fitting the data with flexible models (like polynomials or splines or Gaussian Processes; 
-  \cite{gaussian}).
+  \citealt{gaussian}).
 When employed in the service of exoplanet search and characterization,
@@
   and thus different sensitivity to variations in the device.
-There are also \emph{intra-pixel} sensitivity variations that can contribute, which was first measured by \revise{\cite{subpixel}}.
+There are also \emph{intra-pixel} sensitivity variations that can contribute\revise{(\citealt{subpixel})}.
 There are small changes in spacecraft temperature,
@@
   possibly illimunation-history effects,
-  and possibly sources of variability not yet considered.
+  and possibly other sources of variability not yet considered.
 The remarkable thing about \Kepler\ is that it is trying to measure stars at a level of precision
@@
   but \emph{not} interfere with measurements of stellar variability---%
-  is the \Kepler\ Presearch \remove{(\sic)} Data Conditioning (PDC, \cite{pdc1}).
+  is the \Kepler\ Presearch \remove{(\sic)} Data Conditioning (PDC, \citealt{pdc1}).
 The PDC builds on the idea that systematic errors have a temporal structure that can be extracted from ancillary quantities.
-%This seems the original paper on PDC:
-%[PDC1] https://kepler.nasa.gov/science/ForScientists/papersAndDocumentation/SOCpapers/7740-67-pdc-jtwicken-copyright.pdf
-%
-%This describes the later version of PDC:
-%[PDC2] http://arxiv.org/pdf/1203.1382v1.pdf
-%[PDC3] http://arxiv.org/pdf/1203.1383v1.pdf
 
@@
 
-In \cite{pdc2,pdc3}\remove{, filtered light-curves of other stars are used instead. 
+\remove{In \cite{pdc2,pdc3}, filtered light-curves of other stars are used instead. 
 The light-curve of a target star is projected on the leading eight principal components of these light-curves. 
@@
 
-\revise{In the most recent version of PDC (PDC-MAP, \cite{pdc2,pdc3}), filtered light-curves of other stars are used
-instead. Using a set of relatively quiet stars on each detector, the
-top 8 principle components are computed for every quarter of Kepler
+\revise{In the most recent version of PDC (PDC-MAP, \citealt{pdc2,pdc3}), filtered light-curves of other stars are used. Using a set of relatively quiet stars on each detector, the
+top 8 principal components are computed for every quarter of Kepler
 data. The maximum a posteriori linear combination of these basis light
@@
 
-PDC \remove{``de-trends''}\revise{"co-trends" or calibrates} the \Kepler\ light-curves by removing those parts that are explained by the basis light-curves
+PDC \remove{``de-trends''}\revise{``co-trends'' or calibrates} the \Kepler\ light-curves by removing those parts that are explained by the basis light-curves
   generated from a principal components analysis (PCA) of filtered light-curves.
@@
 
-The method proposed here, \name, shares the motivation of PDC.
+The method proposed here, The Causal Pixel Model(\name), shares the motivation of PDC.
 The main differences are that
@@
 \remove{In their current versions, they also assume that the relationships can be captured with linear models (although we have also used nonlinear predictions methods for \name, which would be harder to do in PDC).}
-By going to the pixel level (unlike the PDC, which works at the photometry level),
+By going to the pixel level (unlike the PDC, which works at the stellar-photometry level),
   \name\ makes it easier for the model to capture variability
@@
 Before we start, a few reminders about the \Kepler\ data are in order:
-The \remove{satellite}\revise{space craft} \remove{always observes}\revise{observed} precisely the same field, at fixed pointing (as closely as possible).
-\revise{About 6\% of the 96,465,600 pixels}\remove{Only a few percent of the 80 million pixels} in the focal plane are telemetered down
+The \remove{satellite}\revise{spacecraft} \remove{always observes}\revise{observed} precisely the same field, at fixed pointing (as closely as possible).
+\revise{About 6 percent of the 96,465,600 pixels}\remove{Only a few percent of the 80 million pixels} in the focal plane are telemetered down
   to Earth from each 30-min exposure;
-  the telemetered pixels are associated with \Kepler\ target stars chosen for study by the \Kepler\ Team \revise{(along with a non-trivial set collateral pixels used for calibration)}.
-The \remove{satellite}\revise{space craft} is rolled by 90~deg every \remove{90-ish}\revise{93} days (to satisfy Solar-Angle constraints).
+  the telemetered pixels are associated with \Kepler\ target stars chosen for study by the \Kepler\ Team \revise{(along with a non-trivial set of collateral pixels used for calibration)}.
+The \remove{satellite}\revise{spacecraft} is rolled by 90~deg every \remove{90-ish}\revise{93} days (to satisfy Solar-Angle constraints).
 The focal plane contains many CCDs;
@@
   on a particular CCD for \remove{90-ish-day}\revise{quarter} contiguous periods of time.
-The PSF varies strongly across the field and is badly sampled.
+The PSF varies strongly across the field and is poorly sampled.
 The stars span a huge range in brightness;
@@
   or along directions in parameter space in which the data are not constraining.
-General regularizations or priors will break the convexity of linear model fitting;
+\remove{General} Regularizations or priors \remove{will}\revise{can} break the convexity of linear model fitting;
   if convexity is to be maintained, these regularizations also have to be quadratic,
@@
   Stars on the same CCD share systematic errors. 
-  The two panels show pixel fluxes (brightnesses) for two stars in quarter 5. \emph{Left:} KIC 5088536, \emph{Right:} KIC 5949551; 
+  The two panels show pixel fluxes (brightnesses) for two stars in quarter 5. \emph{Left:} KIC 11351420, \emph{Right:} KIC 11401755; 
   here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD, 
@@
 Because we are concerned with detecting exoplanet transits,
-  which take few hours,
+  which take a few hours,
   we adopt an extreme version of the train-and-test framework,
-  in which the training data are always separated from the test data by couple of hours.
+  in which the training data are always separated from the test data by \remove{several}\revise{many} hours.
 That is, when we are using the model to predict a particular pixel in the target data taken at time $t$,
@@
   that comes either at times prior to $t-\Delta t$ or after $t+\Delta t$,
-  where $\Delta t$ is a tunable parameter but which we will set to $9$~h.
-This ensures that no information about any exoplanet transit itself
+  where $\Delta t$ is a tunable parameter \remove{but} which we will set to $9$~h.
+This ensures that no information about any \revise{sufficiently short} exoplanet transit itself
   can be entering into the prediction of the pixels contributing to the stellar photometry.
@@
 Short-period exoplanets and certain kinds of stellar variability
-  could be wiped out by a model with these settings of the training-data regime.
+  could be wiped out by a model with these settings of the training-data \remove{regime}\revise{bounaries}.
 
@@
   but it does so without ever \emph{explicitly} creating any of those objects.
-We have to make some kind of heuristic or interpretive move to extract from the data-driven model the quanitites of interest.
+We have to make some kind of heuristic or interpretive move to extract from the data-driven model the quantities of interest.
 
@@
   artificial exoplanet transit signals injected into real \Kepler\ pixel-level data
-  and promising properties of the \name\ outputs \revise{on real Kepler light-curves}.
+  \remove{and promising properties of the \name\ outputs}.
 In the end, the value of the \name\ will be demonstrated by the scientific projects it enables.
 
-We also want to emphasis that all the calibration in this paper for \Kepler is 
-  based on the assumption that the device is \remove{'self-calibratable'}\revise{can be self-calibrated}, 
-  which means all the information we need to calibrate the device are contained in the device itself 
-  (either in science data or engineering data) and no external information, 
-  for example, measurements from other device, are needed.
-  And a description of the method in the machine learning context can be found in \cite{icml2015}
+We also want to emphasis that all the calibration in this paper for \Kepler\ is 
+  based on the assumption that the device \remove{is 'self-calibratable'}\revise{can be self-calibrated}, 
+  which means all the information we need to calibrate the device are contained in the \remove{device itself 
+  (either in} science data \remove{or engineering data)} and no external information, 
+  for example, measurements from \revise{any} other device, are needed.
+\remove{Description}\revise{Elaboration} of the method in \remove{the}\revise{a} machine learning context can be found in \cite{icml2015}
 
@@
 \subsection{\name\ model}
-Each individual \Kepler\ target star is, for each quarter (each \remove{90-ish-day})
-  on a particular CCD on the \Kepler\ focal plane.
+Each individual \Kepler\ target star is, for each quarter \remove{(each 90-ish-day)},
+  \revise{in a particular location} on a particular CCD on the \Kepler\ focal plane.
 Associated with each target star is some set of pixels,
@@
   and telemetered down once for every 30-min exposure.
-Here we are ignoring all short-cadence data that is taken in a different mode with shorter exposures.
+Here we are ignoring all short-cadence data that \remove{is}\revise{are} taken in a different mode with shorter exposures.
 That is, each telemetered pixel in each CCD is associated with a particular \Kepler\ target star.
 
-Let's consider a particular pixel $m$ in the focal plane in one particular month
-  (here we always use data per month rather than quarter,  since there are discontinuities between every \remove{30-ish-day period}\revise{month}).
+\remove{Let's} Consider a particular pixel $m$ in the focal plane in one particular month
+  (here we always use data per month rather than quarter,  since there are discontinuities between every \remove{30-ish-day period}\revise{months}).
 In that month, the spacecraft delivers $N\sim 1300$ measurements $I_{m,n}$
   of the intensity falling in pixel $m$ at the $N$ times $t_n$ at which exposures were taken during the month.
-(For intensity measurements $I_{m,n}$ here we are using pixels from \revise{the FLUX column of Target Pixel File, which is flux of each pixel after processed by the pipeline module CAL, the removal of the interpolated background, and the removal of cosmic rays} on MAST
+(For intensity measurements $I_{m,n}$ \remove{here} we are using pixels from \revise{the FLUX column of Target Pixel File, which is flux of each pixel after processed by the pipeline module CAL, the removal of the interpolated background, and the removal of cosmic rays} on MAST
   \footnote{\url{http://archive.stsci.edu/kepler/}}, for details of the TPF, 
@@
   \remove{To rule out any direct optical cross-talk by starry light}
-  \revise{To minimize the effects of blending with and crosstalk from nearby stars}, we require that the predictor pixels are \remove{from stars
+  \revise{To minimize the effects of blending with, and crosstalk from, nearby stars}, we require that the predictor pixels are \remove{from stars
 sufficiently far away from the target star (at least 20 pixels distance on the CCD).}
@@
 When the measurement $I_{m,n}$ is being predicted from pixel $m$ at a particular time $t_n$,
-  train-and-test framework is used, in which not only
+  a train-and-test framework is used, in which not only
   data at time $t_n$ are not used in optimizing the parameters of the regression or fit,
   but we don't even use any times $t$ such that $|t-t_n| < \Delta t$,
-  where $\Delta t\sim 10$\,h as shown in Fig.~\ref{train-and-test}.
-That is, the model is trained (optimize fit parameters) by using the \emph{time set} $\set{N}_n$ of time
+  where $\Delta t=9$\,h as shown in Fig.~\ref{train-and-test}.
+That is, the model is trained (\remove{optimize}fit parameters\revise{are optimized}) by using the \emph{time set} $\set{N}_n$ of time
   indices $n'$ such that for all $n'\in\set{N}_n$,
@@
 The time set of indices $\set{N}_n$ therefore does not overlap the time point $t_n$,
-  nor any of its neighbors in a time window of half-width $\Delta_t$. 
-\revise{The width of the window $\Delta t$ is set to be the duration of the transits to preserve transits while still predicting the systematics and stellar variability well.}
+  nor any of its neighbors in a time window of half-width $\Delta t$. 
+\revise{The width of the window $\Delta t$ is set to be at least the duration of the transits to preserve transits while still predicting the systematics and stellar variability well.}
 
@@
 In addition to the pixel set $m'\in\set{M}_m$ from other stars,  
-  we also include the past and future of the target star --- autoregressive (AR) component as input 
+  we also include the past and future of the target star, i.e., an autoregressive (AR) component, as input 
   to remove more of the stellar variability and thus increase the sensitivity for transits. 
 To do this, we select an exclusion window of half-width $\Delta t$ including R data points, 
-  where $\Delta t\sim 10$\, h (as big as the window in the train-and-test framework) 
+  where $\Delta t=9$\, h (as big as the window in the train-and-test framework) 
   around the point of time $t_{n}$ being corrected, 
@@
   and then use $S$ closest future and past time points subject to that exclusion. 
-That is, for every pixel $m$ in the target star , we construct $S$ virtual time series, 
+That is, for every pixel $m$ in the target star we construct $S$ virtual time series, 
   in which every component $v$ is defined to be     
@@
   we will finally add $2\cdot M\cdot S$
-  autoregressive components into the predictors, which constructs the autoregressive set $\set{V}_m$
+  autoregressive components into the predictors, which constructs the autoregressive set $\set{V}_m$.
 
@@
   and an objective function that can be used to find best values for those parameters.
-It is often preferable to work in a probabilistic mode in which the objective function can be justified
+\remove{It is often preferable to work in a probabilistic mode in which the objective function can be justified
   in terms of a likelihood (probability for the data given the model)
-  or a posterior probability density function (likelihood times a prior pdf).
+  or a posterior probability density function (likelihood times a prior pdf).}
 The \name\ treats each \Kepler\ data point $I_{m,n}$ as being
@@
 \revise{And the pixel $I_{m',n}$ from other stars at the same time point n is used as input to make prediction.}
-If we presume that the residuals away from the prediction are normally distributed with zero mean and known variance, likelihood optimization reduces to $\chi^2$ minimization.
+If we presume that the residuals away from the prediction are normally distributed with zero mean and known variance, \revise{then} likelihood optimization reduces to $\chi^2$ minimization.
 We add to the standard chi-squared definition a regularization term
@@
 It is not the prediction for time $n'$ using $a_{m,n',m'}, b_{m,n',v}$ as coefficient, but using the coefficient $a_{m,n,m'}, b_{m,n,v}$ that is trained for prediction in time n to set the value.
-It is purely a median product in the process of training the model.} It has three indices,
-  because in \name\ the $\chi^2$ minimization for every time
-  point is independent and the third index--$n$ indicates 
-  which time point the model\remove{prediction $I^{\ast}_{m,n',n}$} is being trained for, 
-  the detail of the independent $\chi^2$ minimization will be discussed below.
+It is purely an intermediate product in the process of training the model.} It has three indices,
+  because in the \name\ the $\chi^2$ minimization for every time
+  point is independent. Details of the independent $\chi^2$ minimization will be discussed below.
 
@@
   the number of autoregressive components S, 
-  and the two regularization strength $\lambda_{a}$ and $\lambda_{b}$.
+  and the two regularization strengths $\lambda_{a}$ and $\lambda_{b}$.
 To set these 4 \remove{hyper-parameters}\revise{tuning parameters}, 
@@
 To show how this general set of \remove{hyper-parameters}\revise{tuning parameters} performs, 
-  we present a few comparison between optimized and default \remove{hyper-parameters}\revise{tuning parameters} 
+  we present a few comparisons between optimized and default \remove{hyper-parameters}\revise{tuning parameters} 
   in Fig~\ref{hyperparameter}.
-We can see that, in Fig~\ref{hyperparameter}, 
+We can see that in Fig~\ref{hyperparameter}, 
   there is less variation in the \name\ flux 
@@
 \hfill
-\includegraphics[width=0.32\textwidth]{f5b}
-\hfill
-\includegraphics[width=0.32\textwidth]{f5c}
-
-\includegraphics[width=0.32\textwidth]{f5d}
-\hfill
 \includegraphics[width=0.32\textwidth]{f5e}
@@
   \label{fluxes} 
-  Corrected fluxes using \name, for 12 example stars, 
+  Corrected fluxes using \name, for 9 example stars, 
     spanning the main magnitude (brightness) range encountered. 
@@
     and the third column are faint stars with magnitude above 13. 
-  In the first two rows, we present some quiet stars. 
+  In the first row, we present some quiet stars. 
   In all three panels, the top panel shows the SAP flux (black) and the \name\ regression (red), 

### 2016-02-09 documents/ms/ms.tex
comments from Hogg

@@
 There are also \remove{probably} changes to the detector sensitivity with temperature and time,
-  possibly illimunation-history effects,
+  possibly illimination-history effects,
   and possibly other sources of variability not yet considered.
@@
 
-\remove{We propose and advise dealing with}\revise{We propose to deal with} these variations in \Kepler\ light-curves by \emph{modeling} them.
+\remove{We propose and advise dealing with}\revise{We propose to militate} these variations in \Kepler\ light-curves by \emph{modeling} them.
 In this context, a model is \remove{(at least)} a parameterized function that can predict data, given parameter settings,
@@
 We also provide an interface to the \Kepler\ data that \remove{delivers improved ``\name\ photometry''}\revise{can be used
-to produce ''\name\ photometry''}
+to produce ``\name\ photometry''}
   for every \Kepler\ target.
@@
   we expect the \name\ prediction $S_{n}$ to be a prediction of
-  what the star light-curve would have under the influence of the spacecraft but with no exoplanet signal 
+  what the star light-curve would have under the influence of the spacecraft but with no exoplanet signal. 
 Based on this idea, 
@@
 \end{eqnarray} 
-In some sense, it is this relative residual--- the \name\ flux that contains the exoplanet transit signals we seek. 
+In some sense, it is this relative residual\revise{---}the \name\ flux\revise{---}that contains the exoplanet transit signals we seek. 
 That is, a transit creates a negative residual away from the prediction, 
@@
   which works well in most of the stars without high variability. 
-To show how this general set of \remove{hyper-parameters}\revise{tuning parameters} performs, 
+To show how this general set of \remove{hyper-parameters}\revise{tuning parameters} performs well, 
   we present a few comparisons between optimized and default \remove{hyper-parameters}\revise{tuning parameters} 
@@
   when we use optimized \remove{hyper-parameters}\revise{tuning parameters} (grey points in second panel, \revise{$Q=60$, $S=3$, $\lambda_a=1e7$, $\lambda_a=1e5$}) 
-  than when we use the default one (red points in the bottom panel). 
-In addition, the optimized flux has higher signal to noise ratio of the known transit than the default. 
+  than when we use the default \remove{one}\revise{values} (red points in the bottom panel). 
+In addition, the optimized flux has higher signal-to-noise ratio \remove{of}\revise{on} the known transit than the default. 
 However, the performance of default \remove{hyper-parameters}\revise{tuning parameters} is acceptable 
@@
   to show the general performance of \name. 
-\revise{It is also worth to mention that the tuning parameters are optimized in a relatively coarse grid, which means the performance can still be improved when setting the tuning parameters more precisely.}
+\revise{It is also worth mentioning that the tuning parameters are optimized only on a relatively coarse grid, which means the performance can still be improved when setting the tuning parameters more precisely.}
 \revise{There are also parameters such as train-and-test window size, the CCD constraint on the predictor stars, the minimum distance of the predictor stars and the ranking algorithm to select predictor stars.
@@
     while \name\ flux of the default \remove{hyper-parameters}\revise{tuning parameters} is in the bottom panel, 
-    the two vertical blue lines indicate the location of the transit signal, 
-    and signal to noise ratio is calculated in both situation. 
-  The optimized \remove{hyper-parameters}\revise{tuning parameters} performs better than the default one, 
-    but the results from both situation are close.
-  Here the signal strength is determined by mean depth of the transit signal,
-    while the noise level is valued by 
-    using the root-mean-square deviation of every points in a 6-day running window.}
+    the two vertical blue lines indicate the location of the \revise{injected} transit signal, 
+    and the signal to noise ratio is calculated in both situations. 
+  The optimized \remove{hyper-parameters}\revise{tuning parameters} perform better than the default\remove{ one}, 
+    but the results from both situations are \remove{close}\revise{similar}.
+  Here the signal strength is determined by the mean depth of the transit signal,
+    while the noise level is \remove{valued by using}\revise{estimated with} the root-mean-square deviation of the points in a 6-day running window.}
 \end{figure}
@@
 
-\subsection{\name's effect on transit signals}
+\subsection{Effect on transit signals}
 One important feature of \name\ is that we use the train-and-test framework to preserve 
-the transit signal. To show how well train-and-test framework performs, we make the
-following experiments on \Kepler\ data as shown in Fig~\ref{distortion}.
-In the light-curve of \revise{KIC 9822284, simpy box model with different depth (from 100 ppm to 1\%) is injected}\remove{single pixel (1, 2) of KIC 9822284, a 10-hrs fake signal 
+the transit signal. To show how well the train-and-test framework performs, we \remove{make}\revise{perform} the
+following experiments on \Kepler\ data shown in Fig~\ref{distortion}:
+In the light-curve of \revise{KIC 9822284, simple rectangular box model with different depth (from 100 ppm to 1\%) is injected}\remove{single pixel (1, 2) of KIC 9822284, a 10-hrs fake signal 
 with amplitude 1.0005 is inserted. To insert the signal, we simply multiply the light-curve 
 by the factor of 1.0005, which makes the little bump in the middle of the SAP light-curve 
-(black points in the first panel).} With the distorted light-curve, both \name\ and "ordinary fitting" are applied the to the data. 
-\revise{By "ordinary fitting", we mean fitting with all the data,  in comparison with the \name\, in which for each data point prediction is made without the data in the excluded region.}  
-In the result, we can see that both methods fit the light-curve quite well outside the range of inserted signal. 
-However, when examine how these two models preserve the signal that we care, the ''ordinary fitting'' fit out a large portion of the signal, while \name\ can preserve the whole 
-original amplitude. Therefore,  by this simple experiment, we are able to show that the train-and-test framework used here is capable to keep the transit signal with a particular time scale. 
-Also we want to emphasise that it is crucial for searching for
-exoplanets, especially the small ones such as earth-like planets, which only have \remove{about tens of parts per million}\revise{$\backsim 100\ ppm$} signal in the light-curve.
-\revise{But there still exits some issue in the \name.
-The \name\ does not predict the light-curve very well around the box model, since in these regions the prediction is under the strong influence of the box model or "transit signal". 
-Thus \name\ will introduce some distortion around the transit signal and the distortion increases with the depth of the signal. This issue will be discussed in detail in section 5.}
+(black points in the first panel).} With the distorted light-curve, both \name\ and ``ordinary fitting" are applied to the data. 
+\revise{By ``ordinary fitting", we mean fitting with all time points,  in comparison with the \name\, in which for each data point the prediction is made without the data in the excluded region.}  
+\remove{In the result, we can see that} Both methods fit the light-curve quite well outside the range of the inserted signal. 
+However, \remove{when examine how these two models preserve the signal that we care,} the ``ordinary fitting'' fits out a large portion of the signal, while the \name\ \remove{can} preserves the \remove{whole} original amplitude.
+\remove{Therefore,  by} This simple experiment\remove{, we are able to} shows that the train-and-test framework \remove{used here} is capable \remove{to keep}\revise{of preserving} the transit signal \remove{with a particular time scale}.
+\remove{Also we want to emphasise that it} This is crucial for searching for
+exoplanets, especially \remove{the small ones such as} Earth-like planets, which only have \remove{about tens of parts per million}\revise{$\backsim$ 100\ ppm} signals \remove{in the light-curve}.
+\revise{But there are issues:
+The \name\ does not predict the light-curve very well around the box model, since in these regions the prediction is under the strong influence of the transit signal. 
+Thus the \name\ will introduce some distortion around the transit signal, and \revise{we expect that} the distortion increases with the depth of the signal.
+This issue will be discussed in detail in Section 5.}
 
@@
 
-To give a view on how our method performs, \name\ is applied on several stars with 
-known transit signals but different variability and magnitudes as shown in Fig.~\ref{fluxes}. 
-From the plots, we can see that \name\ works quite well on these stars, producing the \name\ fluxes 
+\remove{To give a view on how our method performs,}\revise{The} \name\ is applied on several stars with known transit signals but different variability and magnitudes, as shown in Fig.~\ref{fluxes}. 
+\remove{From the plots, we can see that}\revise{The} \name\ works \remove{quite} well on these stars, producing \remove{the} \name\ fluxes 
 with low variation and preserving the transit signals.
-In addition, \name\ and PDC are compared based on 6 quiet stars 
+In addition, \name\ and PDC are compared \remove{based}\revise{for} on 6 quiet stars 
 (non-variable stars, first two rows of Fig.~\ref{fluxes}). 
 The results illustrate that for these quiet stars our approach removes 
-a major part of the variability present in the PDC light-curves, while preserving the transit signals. 
+\remove{a major part}\revise{the majority} of the variability present in the PDC light-curves, while preserving the transit signals. 
 To provide a quantitative comparison, we ran \name\ on 1000 stars from the whole Kepler input catalog 
 (500 chosen randomly from the whole list, and 500 random G-type sun-like stars), 
-and estimate the Combined Differential Photometric Precision (CDPP,  \cite{cdpp1} )for \name\ and PDC.  
+and estimated the Combined Differential Photometric Precision (CDPP,  \citealt{cdpp1} )for the \name\ and PDC.  
 CDPP is an estimate of the relative precision in a time window, 
 indicating the noise level seen by a transit signal with a given duration. 
-\revise{In this paper, the CDPP is calculated with 12 bandpass filter using the equations 6-8 in section 3.3 of \citep{cdpp1}.
-And the CDPP of both PDC and \name\ is estimated with the same algorithm.}
+\revise{In this paper, the CDPP is calculated by using the equations 6-8 in section 3.3 of \citep{cdpp1}. The CDPP of both PDC and \name\ is estimated with the same algorithm.} 
 The duration is typically chosen to be 3, 6, or 12 hours. 
-We use the 12-hours CDPP metric, since the transit duration of an earth-like planet is roughly 10 hours. 
-Before CDPP is estimated, the variability of the stars are evaluated by median differential variability 
-  (MDV, see \cite{basri2013} for details). 
+We use the 12-hour CDPP metric, since the transit duration of an earth-like planet is roughly 10 hours. 
+Before the CDPP is estimated, the variability of the stars \remove{are}\revise{is} evaluated by median differential variability 
+  (MDV, see \citealt{basri2013} for details). 
 Based on the variability, the 100 most variable stars in the list are removed, 

### 2016-02-11 documents/ms/ms.tex
comments from Hogg

@@
   \name\ preserves transit signals.
-  \remove{Fake signal with amplitude 1.0005 is inserted into the single pixel (1, 2) of star KIC 9822284.}\revise{Simply box models with depth from $100 ppm to 1\%$ is injected into the light-curve of star KIC 9822284.
-Plot (a) and (b) show the results from box model depth to be 500 ppm and 3000 ppm.}
-  In the top panel, the black points shows the SAP flux of the pixel with the injected signal, the bold grey line is the fitting of the SAP flux, and the thin red line is the \name\ prediction. 
+  \remove{Fake signal with amplitude 1.0005 is inserted into the single pixel (1, 2) of star KIC 9822284.
+  In the top panel, the black points shows the SAP flux of the pixel with the injected signal, the bold grey line is the fitting of the SAP flux, and the thin red line is the \name\ prediction.}
+  \revise{Simple box models with depth from 100 ppm to 1 percent were injected into the light curve of star KIC 9822284.
+\emph{Left:} An example of light curve with 500 ppm signal injected.
+In the top panel, SAP flux is plotted in black,
+    \name\ prediction is in thin red line, 
+   ``ordinary fitting'' is in bold grey line.} 
   In the bottom panel, red points and grey cross represent the \name\ flux and the fit flux, while the signal value is indicated by the horizontal line. 
-  \name\ largely preserves the signal while the fitting flux overfit the signal.} 
-  \revise{But the \name\ flux is distorted a little around the box model. 
+  \name\ largely preserves the signal while the fitting flux overfit the signal.} \revise{But the \name\ flux is distorted a little around the box model. 
   And there is more distortion with a strong signal.
-  Plot (c) shows the signal depth measured in \name\ and fitting flux relative to the true depth with different box model depth.
+  \emph{Right:} shows the signal depth measured in \name\ and fitting flux relative to the true depth with different box model depth.
 \name\ can consistently preserve more signal than the "ordinary fitting".}
@@
   since PDC is not designed to remove stellar variability, 
-  and we want to compare \name\ and PDC on the close footing.
+  and we want to compare \name\ and PDC on the \remove{close}\revise{same} footing.
 Fig.~\ref{cdpp} presents our CDPP comparison of \name\ and PDC, 
@@
 Data of quarter 5 are from Kepler data release 21 and other data are from Kepler data release 24---the current version) data are used to show that \name\ has a consistent performance over a whole orbital period of the Kepler photometer (372 days).
-We also want to emphasis that both \name\ and PDC are presented here does not mean that it is a competition.
-Since PDC is designed to preserve stellar variability, it is not fair to put \name\ and PDC into competition.
-The CDPP comparison is made only to give a relative reference how \name\ can perform according to PDC, the Kepler "gold standard"}
+We also want to emphasize that both \name\ and PDC are presented here, but since PDC is designed to preserve stellar variability, it is not fair to put \name\ and PDC into competition.
+The CDPP comparison is made only to give a relative reference how \name\ can perform according to PDC, the Kepler ``gold standard"}
 
-\revise{In order to show the overall ability that \name\ have in exoplanet searching, a comparison between \name\ and median filter (a widely used de-trend method) is presented in Fig.~\ref{filter}.
-This is a more comprehensive comparison, since not only noise level (CDPP) is evaluated,  but how well both methods can retrieve signal from the light curve is also under consideration.
-In the example, a 200 ppm box model signal is injected into a quiet star KIC 8846139 in quarter 5.
-With the signal injected light curve,  both methods---median filter and \name\ are applied.
+\revise{In order to show the overall performance of \name\ for exoplanet search, a comparison between the \name\ and a median filter (a widely used de-trending method) is presented in Fig.~\ref{filter}.
+This is a more comprehensive comparison, since not only the noise level (CDPP) is evaluated,  but how well both methods preserve signals in the light curve is also under consideration.
+In the example, a 200 ppm box model signal was injected into a quiet star KIC 8846139 in quarter 5.
+With the signal-injected light curve,  both methods---median filter and \name---are applied.
 As shown in Fig.~\ref{filter}, when  the window size is bigger than 24 hours, \name\ performs better both in terms of CDPP and signal strength.
 As expected, when the window size gets smaller, CDPP decreases,  while the signal strength retrieved from the light curve also falls off.
-Although median filter with window size smaller than 24 hours is able to generate cleaner light curves (lower CDPP level) than \name, it largely distorts the signal that we care about.
-Imagining in an extreme case, light curves generated by a half hour median filter will have zero CDPP, as well as zero signal strength.
+Although the median filter with window size smaller than 24 hours is able to generate cleaner light curves (lower CDPP level) than \name, it largely distorts the signal that we care about.}
+
+\revise{Imagining an extreme case, light curves generated by a half-hour median filter will have zero CDPP, as well as zero signal strength.
 If we examined the ratio of the signal strength to the CDPP (signal to noise ratio) in this example, it results that \name\ can always have a signal to noise ratio around 8, while the median filter method can only achieve a ratio around 6 in the best circumstance, when window size is 24 hours.
@@
 \section{Discussion}
-We have presented a simple yet highly effective method---the \name\ that works in pixel-level 
-  based on the causal structure of the \Kepler\ data to calibrate the \Kepler\ light-curves, 
-  which is intended to search exoplanets.
-In \name, systematics and stellar variabilities are removed by
-  either fitting with other stars' light-curves or auto-regressive components,
-  while transit signals can still be perfectly preserved by train-and-test framework.
+We have presented a simple yet highly effective method---the \name---that works at pixel-level \revise{to remove spacecraft and stellar variability on time-domain imaging.
+It is} based on the causal structure of the \Kepler\ data \remove{to}\revise{; It} calibrates the \Kepler\ light-curves \remove{, which is intended to search exoplanets.} \revise{for the purpose of exoplanet search.}
+In \revise{the} \name, systematics and stellar variabilities are removed by
+  either fitting with other stars' light-curves or auto-regressive components, while transit signals \remove{can still be perfectly preserved} \revise{are preserved with a} \remove{by} train-and-test framework.
 Low variable clean light-curves can be produced by \name\,  

### 2016-02-17 documents/ms/ms.tex
comments from Hogg

@@
 
-\remove{We propose and advise dealing with}\revise{We propose to militate} these variations in \Kepler\ light-curves by \emph{modeling} them.
+\remove{We propose and advise dealing with}\revise{We propose to mitigate} these variations in \Kepler\ light-curves by \emph{modeling} them.
 In this context, a model is \remove{(at least)} a parameterized function that can predict data, given parameter settings,
@@
 In \revise{the} \name, systematics and stellar variabilities are removed by
-  either fitting with other stars' light-curves or auto-regressive components, while transit signals \remove{can still be perfectly preserved} \revise{are preserved with a} \remove{by} train-and-test framework.
+  either fitting with other stars' light-curves or auto-regressive components, while transit signals \remove{can still be perfectly preserved} \revise{are preserved with a} \remove{by} train-and-test framework \revise{to control model freedom}.
 Low variable clean light-curves can be produced by \name\,  

### 2016-02-22 documents/ms/ms.tex
comments from hogg

@@
   for example, measurements from \revise{any} other device, are needed.
-\remove{Description}\revise{Elaboration} of the method in \remove{the}\revise{a} machine learning context can be found in \cite{icml2015}
+\remove{Description}\revise{Elaboration} of the method in \remove{the}\revise{a} machine learning context can be found in \citealt{icml2015}
 
@@
 indicating the noise level seen by a transit signal with a given duration. 
-\revise{In this paper, the CDPP is calculated by using the equations 6-8 in section 3.3 of \citep{cdpp1}. The CDPP of both PDC and \name\ is estimated with the same algorithm.} 
+\revise{In this paper, the CDPP is calculated by using the equations 6-8 in section 3.3 of \citealt{cdpp1}. The CDPP of both PDC and \name\ is estimated with the same algorithm.} 
 The duration is typically chosen to be 3, 6, or 12 hours. 
@@
   \label{fluxes} 
-  Corrected fluxes using \name, for 9 example stars, 
-    spanning the main magnitude (brightness) range encountered. 
-  In first column plots, we consider bright stars with magnitude from 9 to 10.5, 
-    second cloumn are stars with magnitude from 11 to 12.5,  
-    and the third column are faint stars with magnitude above 13. 
+  Corrected fluxes using \name, for 9 example stars, spanning the \Kepler\ magnitude (brightness) range \remove{encountered}. 
+  In first column plots, we consider bright stars with magnitude from 9 to 10.5, second column are stars with magnitude from 11 to 12.5, and the third column are faint stars with magnitude above 13. 
   In the first row, we present some quiet stars. 
-  In all three panels, the top panel shows the SAP flux (black) and the \name\ regression (red), 
-    i.e., our prediction of the star from other stars. 
+  \remove{In all three panels,} The top panel shows the SAP flux (black) and the \name\ regression (red)\remove{, i.e., our prediction of the star from other stars}. 
   The middle panel shows the \name\ flux corrected using the regression, and the bottom shows the PDC flux. 
@@
     while removing a substantial part of the variability present in the PDC flux. 
-  Both the bottom two rows present some variable stars with slow and fast variability. 
+  \remove{Both the bottom two rows present some variable stars with slow and fast variability.} 
   For the variable stars, we did not present the PDC comparison, 
-    since the PDC flux try to preserve intrinsic stellar variability.}
+    since the PDC \remove{flux try to preserve}\revise{method preserves} intrinsic stellar variability.}
 \end{figure}
@@
   \label{cdpp} 
-  Comparison of the proposed method (\name) to the \Kepler\ Pre-search Data Conditioning (PDC) method 
+  Comparison of the \revise{\name\ } \remove{proposed method (\name) }to the \Kepler\ Pre-search Data Conditioning (PDC) method 
     in terms of Combined Differential Photometric Precision (CDPP).
   \revise{Row 1-4 shows the CDPP estimation throgh quarter 5 to quarter 8. In each row:} 
-  Plot (a) shows our performance (red) vs.\ the PDC performance in a scatter plot, as a function of star magnitude 
-    (note that larger magnitude means fainter stars, 
-    and smaller values of CDPP indicate a higher quality as measured by CDPP.)
-  Plot (b) bins the same dataset and shows box plots within each bin, 
-    indicating median, top quartile and bottom quartile. 
+  \emph{Left} \remove{Plot (a)} shows our performance (red) vs.\ the PDC performance (black) in a scatter plot, as a function of star magnitude (note that larger magnitude means fainter stars, and smaller values of CDPP indicate higher quality as measured by CDPP.)
+  \emph{Middle} bins the same dataset and shows box plots within each bin, indicating median, top quartile and bottom quartile. 
   The red box corresponds to \name, while the black box refers to PDC. 
-  Plot (c), finally, shows a histogram of CDPP values. 
+  \emph{Right} shows a histogram of CDPP values. 
   Note that the red histogram has more mass towards the left, i.e., smaller values of CDPP, 
-    indicating that our method \remove{overall outperforms PDC, the Kepler ``gold standard.'' } \revise{process the \Kepler\ light-curve to a lower noise level.}
+    indicating that our method \remove{overall outperforms PDC, the Kepler ``gold standard.'' } \revise{returns the light curves with a lower noise level.}
 }
@@
   \label{filter} 
-\revise{Comparison of \name\ to the median filter method (based on PDC light curve) with different filter window size.
-200 ppm box model signal is injected into the light curve of KIC 8846139 in quarter 5.
-Both \name\ and median filter method are applied to the light curve after injection.
-In the first panel, CDPP estimate of the median filtered light curve is plotted as a function of the filter window size (blue dots) and the red dash line indicates the CDPP level of CPM.
+\revise{Comparison of the \name\ to the median filter method as described in text with different filter window size.
+A 200 ppm amplitude box-model signal was injected into the light curve of KIC 8846139 in quarter 5.
+Both the \name\ and median filter method are applied to the light curve after injection.
+In the first panel, CDPP estimate of the median filtered light curve is plotted as a function of the filter window size (blue dots) and the red dash line indicates the CDPP level of the \name.
 In the second panel, the signal strength measured from the median filtered light curve is plotted as a function of the filter window size (blue dots), while the red dash line indicates the signal strength retrieved from the \name\ light curve.
 The grey dash line shows the injected signal strength.
-Smaller window size reduces the noise level (CDPP) of the median filtered light curve, while distort the signal more.
-\name\ outperforms median filter in terms of signal to noise ratio.}
+Smaller window size reduces the noise level (CDPP) of the median filtered light curve, but distorts the signal more.
+\name\ outperforms the median filter in terms of signal to noise ratio.}
 }
@@
 It is} based on the causal structure of the \Kepler\ data \remove{to}\revise{; It} calibrates the \Kepler\ light-curves \remove{, which is intended to search exoplanets.} \revise{for the purpose of exoplanet search.}
-In \revise{the} \name, systematics and stellar variabilities are removed by
-  either fitting with other stars' light-curves or auto-regressive components, while transit signals \remove{can still be perfectly preserved} \revise{are preserved with a} \remove{by} train-and-test framework \revise{to control model freedom}.
-Low variable clean light-curves can be produced by \name\,  
-  which is ideal for transit planet searching. 
-The CDPP noise level estimation is also presented in the paper to show the performance of \name.
+In \revise{the} \name, systematics and stellar variabilities are removed by either fitting with other stars' light-curves or auto-regressive components, while transit signals \remove{can still be perfectly preserved} \revise{are preserved with a} \remove{by} train-and-test framework \revise{to control model freedom}.
+Low variable clean light-curves can be produced by \name,  
+  which is ideal for \remove{transit} planet search. 
+\remove{The CDPP noise level estimation is also presented in the paper to show the performance of \name.}
 
-Apart from the \name, as mentioned in the beginning of the paper, 
-  there exist several other methods that are effective in de-trending the light-curve.
-Methods like median filter are quite successful in smoothing all the unwanted features 
+Apart from the \name, \remove{as mentioned in the beginning of the paper,}
+  there exist several other methods that are effective in de-trending \remove{the} light curves.
+Methods like \revise{the} median filter are quite successful in smoothing \remove{all the} unwanted features 
   either from spacecraft or intrinsic stellar variability, 
-  but the problem is that this kind of methods filter everything in the data including the transit signal. 
-This is not a big deal for searching giant planets, since the signal is quite strong. 
+  but \remove{the problem is that this kind of methods}\revise{they} filter everything in the data including the transit signal. 
+This is not a big deal for \remove{searching}\revise{searches for} giant planets, since the signal is quite strong. 
 However, 
-  when it comes to earth-like planets (only about \remove{20 ppm}\revise{$\backsim 100\ ppm$} transit signal around a sun-like star),
+  when it comes to Earth-like planets (only \remove{20 ppm}\revise{$\backsim 100$\ ppm} transit signal around a sun-like star),
   \remove{any reduction or distortion of the signal is unacceptable.}
-  \revise{preventing transit signal from reduction or distortion is important.} 
-In comparison, in order to achieve higher precision for earth-like planet searching, 
+  \revise{protecting transit signal from distortion is important.} 
+In comparison, in order to achieve higher precision for Earth-like planet searching, 
   \name\  not only exploits the causal structure of the \Kepler\ data,
-  but also apply effective approaches (strong regularization and train-and-test framework)
-  to avoid over-fitting the transit signal.
-There also exists more sophisticated method like PDC.
+  but also \remove{apply} effectively \remove{approaches} (through strong regularization and train-and-test framework)
+  \remove{to} avoids over-fitting the transit signal.
+There also exists more sophisticated methods like PDC.
+
 As mentioned earlier in this paper, 
@@
   which is assumed to be caused by the spacecraft effects (or systematics).
-\remove{However, in section 4, we show that \name\ performs better than PDC, 
-  in that it has a overall low noise level (CDPP).
+\remove{However, in section 4, we show that \name\ performs better than PDC, in that it has a overall low noise level (CDPP).
 We think the outperformance mainly caused by two factor.}
-\revise{However, the main difference between \name\ and PDC lays on two factor.}
+\revise{However, the main differences between \name\ and PDC are the following:}
 One is that \name\ calibrates every single pixel separately, 
-  while PDC works in the photometry level.
-It is no doubt that pixel-level modelling enables \name\ capture more variability, such as 
+  while PDC works \remove{in}\revise{at} the photometry level.
+\remove{It is no doubt that} Pixel-level modelling enables \revise{the} \name\ \revise{to} capture more variability, such as 
 variations in the centroids and point-spread function from spacecraft pointing, roll, and temperature.
-The other reason is that,  
-  in PDC,  only leading eight principal components of some relative light-curves are used.
-Although restricting the number of components can prevent over-fitting, we think with this limited number of components, 
-  it is insufficient to capture all the variabilities in the light-curve.
-In \name\, hundreds of stars' light-curves (or thousands of pixels) are used 
-  to capture relatively complete information of the variabilities, 
-  while strong regularization and train-and-test framework are applied to prevent over-fitting.
+The other reason is that, in \revise{the} PDC,  only \revise{the} leading eight principal components of some relative light-curves are used.
+Although restricting the number of components can prevent over-fitting, \remove{we think with this limited number of components,} it is insufficient to capture all the variabilities in the light curves.
+In \revise{the} \name\, hundreds of stars' light-curves (or thousands of pixels) are used to capture relatively complete information of the variability, while strong regularization and train-and-test framework are applied to prevent over-fitting.
 Although we present the comparison between \name\ and PDC, 
@@
   while the \name\ is optimized for exoplanet searching. 
-The comparison is only based on our objective (search for earth-like planet), 
-  and should not be regard as standard of a best model for \Kepler\ data.
+The comparison is only based on our objective (searches for Earth-like planets), 
+  and should not be regarded as standard of a best model for \Kepler\ data.
 
-However, apart from the outstanding performance in calibrating the data, the \name\ still has several issues. 
-Based on our assumption of the causal structure of the \Kepler\ data, 
-  if we turn off the auto-regressive components and keep the predictors from other stars working in the \name, 
-  we should be able to still remove the systematics while preserve the intrinsic stellar variability, 
-  since there is no reason that these independent stars can be used to predict the stellar variability of the target star.
+However, apart from the \remove{outstanding}\revise{good} performance in calibrating the data, the \name\ still has several issues. 
+Based on our assumption of the causal structure of the \Kepler\ data, if we turn off the auto-regressive components and keep the predictors from other stars working in the \name, we should be able to still remove the systematics while preserving the intrinsic stellar variability, since there is no reason that these independent stars can be used to predict the stellar variability of the target star.
 However, in fact, we can not preserve the stellar variability just by turning off the auto-regressive components. 
@@
 
-Another issue of the \name\ is that when there are strong transit signals in the light-curve,  
-  one can find distortion around these signals.
+Another issue \remove{of}\revise{with} the \name\ is that when there are strong transit signals in the light curve, one can find distortion around these signals.
 We think this problem is caused by the train-and-test framework.
-Train-and-test framework is applied in the \name\ to preserve the transit signals, 
-  in which data points in a certain excluded window are separated from the model.
-However, for data points half-window size away from the transit signals, 
-  the prediction of these points in \name\ is largely influenced by the strong transit signal.
-That is,  these points are predicted to be a little bit smaller than they should be, 
-  since transit signal (negative points away from the continuum) makes the model think
-  there is a decreasing trend in this region.
-This window edge effect is a trade-off of the train-and-test framework that is crucial for \name,
- and can not be solved in the scope of \name.
+The train-and-test framework is applied in the \name\ to preserve transit signals\remove{, in which data points in a certain excluded window are separated from the model}.
+However, for data points \revise{a} half-window size away from the transit signals, the prediction of these points in \name\ is \remove{largely} influenced by the strong transit signal.
+That is,  these points are predicted to be a little bit smaller than they should be, since \revise{the} transit signal (negative points away from the continuum) makes the model think there is a decreasing trend in this region.
+This window edge effect is a trade-off of the train-and-test framework that is crucial for \name, and can not be solved within the scope of \revise{the} \name.
 
-One possible way to solve this kind of edge effect 
-  but still preserve the transit signals is to do the simultaneous fitting 
-  for both systematics and transit signal together, 
-  like what have been done in \cite{dfm}. 
-That is,  
-  instead of only modelling the systematics 
-  and then subtracting it from the raw data to produce some de-trended light-curves,
-  a comprehensive model for all components in the data (systematics, stellar variabilities and transits)  can be made. In this kind of model, there is no need for train-and-test framework,
-  since all transit signals have already been modelled 
-  and no de-trended light-curve will be produced. Planets will be found directly in the model itself.
+One possible way to solve this kind of edge effect but still preserve the transit signals is to \remove{do the}\revise{perform} simultaneous fitting for both systematics and transit signal together\remove{, like what have been done in}\citep{dfm}.
+That is,  instead of only modelling the systematics and then subtracting \remove{it}\revise{them} from the raw data to produce \remove{some }de-trended light curves, a comprehensive model for all components in the data (systematics, stellar variabilities and transits)  can be made.
+In this kind of model, there is no need for \revise{the} train-and-test framework, since all transit signals have already been modelled and no de-trended light-curve will be produced.
+Planets will be found directly in the model itself.
 
-\revise{Another issue or improvement that can be considered for \name\ is the predictor selection algorithm. 
-In \name\, a simple selection policy is applied, in which closest stars in magnitude on the same CCD channel are selected.
-This algorithm might be reasonable, since intuitively, the response function of CCD might be similar for stars with similar brightness.
+\revise{Another issue or improvement that can be considered for the \name\ is an improved selection algorithm for predictor pixels. 
+In the \name\, a simple selection policy is applied, in which stars closest in magnitude on the same CCD channel are selected.
+This algorithm might be reasonable, since intuitively the response function of CCD might be similar for stars with similar brightness.
 However, Kepler is a complicated system.
-Systematics like rolling bands may affect only some of the stars.
-Chances are that "bad predictors" may be included into the set of predictor stars to distort the \name\ prediction or \name\ might miss some of the "good predictors", in which case, it can not capture some of the systematics signature.
-Although we also want to mention that in \name\, a huge set of predictors (4000 pixels from other stars) are used, which somehow ensures the model perform well in general, it still remains an unsolved issue for \name.
-In this paper, we did not purse the optimized selection algorithm, because we want to make the model as simple as possible.
-But in order to get an optimized performance for \name, how to select and rank the predictor stars is an important and unavoidable issue.}
+Systematics like rolling bands \citep{handbook} may affect only some of the stars.
+Chances are that ``bad predictors" may be included into the set of predictor stars to distort the \name\ prediction or \name\ might miss some of the ``good predictors", in which case, it can not capture some of the systematics signature.
+In the current implementation, the \name\ uses a huge set of predictors (4000 pixels from other stars), which ensures that the model will perform well in general, but pixel selection still remains an unsolved issue for the \name.
+In this paper, we did not purse optimized selection algorithms, because we want to make the model as simple as possible.
+But in order to get optimized performance for \name, how to select and rank the predictor stars is an important and unavoidable issue.}
 
-\revise{As we have mentioned before in this paper,  since \name\ needs to make prediction for every data points in the light curve, it is quite time-cosuming to process the complete Kepler data set with \name.
-Here we presents an \name\ runtime estimation based on our experience.
-For a light curve of duration three months (one quarter), \name\ took about 7 hours on a single core (Ivy Bridge x86 64 3.0GHz).}
+\revise{As we have mentioned before in this paper,  since the \name\ needs to make predictions for every data point in the light curve, it is quite time-consuming to process the complete Kepler data set with \name.
+Here we present \name\ runtime estimation based on our experience: For a light curve of duration three months (one quarter), the \name\ takes about 7 hours on a single core (Ivy Bridge x86 64 3.0GHz).}
 
-However, despite all the problems mentioned in the \name,
-  we expect that data-driven model like our method will enable astronomical discoveries 
-  at higher sensitivity on the existing \Kepler\ data as well as on future missions.  
-As we know, \Kepler\ \project{K2} \citep{k2} data are suffering from the broken-down of reaction wheels, 
-  which makes the \remove{satellite}\revise{space craft} hard to control and introduce significant systematics. 
-Flexible data-driven model \citep{dfm} has already shown the power on the \project{K2} data 
-  and find new planets.
-Moreover, in 2017, NASA is planning the launch of another space telescope---
-  \project{TESS} (Transiting Exoplanet Survey \remove{satellite}\revise{space craft}, \cite{tess}), 
+However, despite all \remove{the problems mentioned in the \name}\revise{these issues}, we expect that a data-driven model like our method will enable astronomical discoveries at higher sensitivity on the existing \Kepler\ data as well as on future missions.
+As we know, \Kepler\ \project{K2} \citep{k2} data are suffering from the \remove{broken-down}\revise{failure} of reaction wheels,  which makes the \remove{satellite}\revise{space craft} hard to control and introduces significant systematics.
+Flexible data-driven model \citep{dfm} has already shown \remove{the}\revise{its} power on the \project{K2} data \remove{and}\revise{to} find new planets.
+Moreover, in 2017, NASA is planning the launch of another space telescope---\project{TESS} (Transiting Exoplanet Survey Satellite, \citealt{tess}), 
   which will perform an all-sky survey for small (earth-like) planets of nearby M stars. 

### 2016-02-23 documents/ms/ms.tex
revise caption of figures and fix a paragraph in discussion

@@
   the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.} 
-\revise{We find that \name\ can consistently produce low-noise light-curves.
+\revise{We find that \name\ can consistently produce low-noise light curves.
 In this paper, we demonstrate that pixel-level de-trending is possible while retaining transit signals and we think that methods like \name\ are generally applicable and might be useful for  K2, TESS, etc, where the data aren't clean postage stamps like \Kepler.}
@@
   these can effectively transfer variability from one source to another.
-There are additional electronics effects like ``rolling bands'' that put additional features into light-curves \revise{\citep{handbook}}.
+There are additional electronics effects like ``rolling bands'' that put additional features into light curves \revise{\citep{handbook}}.
 There are also \remove{probably} changes to the detector sensitivity with temperature and time,
@@
 
-\remove{We propose and advise dealing with}\revise{We propose to mitigate} these variations in \Kepler\ light-curves by \emph{modeling} them.
+\remove{We propose and advise dealing with}\revise{We propose to mitigate} these variations in \Kepler\ light curves by \emph{modeling} them.
 In this context, a model is \remove{(at least)} a parameterized function that can predict data, given parameter settings,
@@
 The model we propose here is in the non-physical, effective category.
-The \Kepler\ community is familiar with these kinds of models;
-  to our knowledge, \emph{all} successful light-curve ``de-trending'' methods
-  are flexible, effective models.
+The \Kepler\ community is familiar with these kinds of models; to our knowledge, \emph{all} successful light curve ``de-trending'' methods are flexible, effective models.
 
@@
 
-\revise{In the most recent version of PDC (PDC-MAP, \citealt{pdc2,pdc3}), filtered light-curves of other stars are used. Using a set of relatively quiet stars on each detector, the
+\revise{In the most recent version of PDC (PDC-MAP, \citealt{pdc2,pdc3}), filtered light curves of other stars are used. Using a set of relatively quiet stars on each detector, the
 top 8 principal components are computed for every quarter of Kepler
@@
 
-PDC \remove{``de-trends''}\revise{``co-trends'' or calibrates} the \Kepler\ light-curves by removing those parts that are explained by the basis light-curves
-  generated from a principal components analysis (PCA) of filtered light-curves.
+PDC \remove{``de-trends''}\revise{``co-trends'' or calibrates} the \Kepler\ light curves by removing those parts that are explained by the basis light curves generated from a principal components analysis (PCA) of filtered light curves.
 That is, it exploits statistical dependences between different time series, regularizing the fit (and avoiding over-fitting) 
@@
 \item
-\name\ works in the pixel domain, not the light-curve domain, so it has access to more fine-grained information
+\name\ works in the pixel domain, not the light curve domain, so it has access to more fine-grained information
 \item
 \name\ has far more freedom (far more parameters) than the PDC
-  but it strictly avoids over-fitting the light-curves on exoplanet-transit time-scales
+  but it strictly avoids over-fitting the light curves on exoplanet-transit time-scales
   through strong regularization and a train-and-test framework. 
@@
 \item 
-\name\ uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion, while PDC works with time series (light-curves) of the other stars.
+\name\ uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion, while PDC works with time series (light curves) of the other stars.
 \end{enumerate}
@@
 The two methods (\name\ and PDC) are similar however,
-  in that they both make the \remove{(implicit or explicit)} assumption that whatever spacecraft effects are imprinting variability on a stellar light-curve
-  must also be imprinting similar or related variability on other light-curves.
+  in that they both make the \remove{(implicit or explicit)} assumption that whatever spacecraft effects are imprinting variability on a stellar light curve must also be imprinting similar or related variability on other light curves.
 \remove{In their current versions, they also assume that the relationships can be captured with linear models (although we have also used nonlinear predictions methods for \name, which would be harder to do in PDC).}
-By going to the pixel level (unlike the PDC, which works at the stellar-photometry level),
-  \name\ makes it easier for the model to capture variability
-  that is coming through variations in the centroids and point-spread function
-  from spacecraft pointing, roll, and temperature.
+By going to the pixel level (unlike the PDC, which works at the stellar-photometry level), \name\ makes it easier for the model to capture variability that is coming through variations in the centroids and point-spread function from spacecraft pointing, roll, and temperature.
 
@@
 That is, different assumptions about the physical properties of the data and the data-taking system lead to different structures for the data-driven model.
-In the case of \Kepler\ data, 
-  if we examine two arbitrary stars far away from each other 
-  on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light-curve time series), 
-  we can obviously see that the two stars that are hundreds pixel away from each other do have similar trends. 
+In the case of \Kepler\ data, if we examine two arbitrary stars far away from each other on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light curve time series), we can obviously see that the two stars that are hundreds pixel away from each other do have similar trends.
   If we believe that different stars in the \Kepler\ field vary independently 
@@
 Besides, a model that can predict not just the spacecraft-induced variability,
-  but also variability caused by exoplanet transits of interest,
-  will effectively over-fit and distort the most important information in the light-curves.
+  but also variability caused by exoplanet transits of interest, will effectively over-fit and distort the most important information in the light curves.
 That is, what is considered best for modelling the data depends on the objectives of the user.
@@
   for example, measurements from \revise{any} other device, are needed.
-\remove{Description}\revise{Elaboration} of the method in \remove{the}\revise{a} machine learning context can be found in \citealt{icml2015}
+\remove{Description}\revise{Elaboration} of the method in \remove{the}\revise{a} machine learning context can be found in \citealt{icml2015}.
 
@@
 
-Because of the train-and-test framework,  
-  we expect the \name\ prediction $S_{n}$ to be a prediction of
-  what the star light-curve would have under the influence of the spacecraft but with no exoplanet signal. 
+Because of the train-and-test framework,  we expect the \name\ prediction $S_{n}$ to be a prediction of what the star \remove{light-curve}\revise{light curve} would have under the influence of the spacecraft but with no exoplanet signal.
 Based on this idea, 
@@
 following experiments on \Kepler\ data shown in Fig~\ref{distortion}:
-In the light-curve of \revise{KIC 9822284, simple rectangular box model with different depth (from 100 ppm to 1\%) is injected}\remove{single pixel (1, 2) of KIC 9822284, a 10-hrs fake signal 
+In the light curve of \revise{KIC 9822284, simple rectangular box model with different amplitude (from 100 ppm to 1\%) is injected.
+To do the injection, each pixel light curve of the target star is multiplied by a factor of the amplitude within a timescale of 8 hours.}\remove{single pixel (1, 2) of KIC 9822284, a 10-hrs fake signal
 with amplitude 1.0005 is inserted. To insert the signal, we simply multiply the light-curve 
 by the factor of 1.0005, which makes the little bump in the middle of the SAP light-curve 
-(black points in the first panel).} With the distorted light-curve, both \name\ and ``ordinary fitting" are applied to the data. 
+(black points in the first panel).} With the distorted light curve, both \name\ and ``ordinary fitting" are applied to the data. 
 \revise{By ``ordinary fitting", we mean fitting with all time points,  in comparison with the \name\, in which for each data point the prediction is made without the data in the excluded region.}  
-\remove{In the result, we can see that} Both methods fit the light-curve quite well outside the range of the inserted signal. 
+\remove{In the result, we can see that} Both methods fit the light curve quite well outside the range of the inserted signal. 
 However, \remove{when examine how these two models preserve the signal that we care,} the ``ordinary fitting'' fits out a large portion of the signal, while the \name\ \remove{can} preserves the \remove{whole} original amplitude.
@@
 \revise{But there are issues:
-The \name\ does not predict the light-curve very well around the box model, since in these regions the prediction is under the strong influence of the transit signal. 
+The \name\ does not predict the light curve very well around the box model, since in these regions the prediction is under the strong influence of the transit signal. 
 Thus the \name\ will introduce some distortion around the transit signal, and \revise{we expect that} the distortion increases with the depth of the signal.
@@
 \begin{center}
-\includegraphics[width=0.32\textwidth]{f4a}
-\includegraphics[width=0.32\textwidth]{f4b}
-\includegraphics[width=0.32\textwidth]{f4c}
+\includegraphics[width=0.325\textwidth]{f4a}
+\includegraphics[width=0.325\textwidth]{f4b}
+\includegraphics[width=0.325\textwidth]{f4c}
 \end{center}
@@
   In the top panel, the black points shows the SAP flux of the pixel with the injected signal, the bold grey line is the fitting of the SAP flux, and the thin red line is the \name\ prediction.}
-  \revise{Simple box models with depth from 100 ppm to 1 percent were injected into the light curve of star KIC 9822284.
+  \revise{Simple box models with amplitude from 100 ppm to 1 percent were injected into the light curve of star KIC 9822284. 
   \emph{Left:} An example of light curve with 500 ppm signal injected.
-In the top panel, SAP flux is plotted in black,
-    \name\ prediction is in thin red line, 
-   ``ordinary fitting'' is in bold grey line.} 
-  In the bottom panel, red points and grey cross represent the \name\ flux and the fit flux, while the signal value is indicated by the horizontal line. 
-  \name\ largely preserves the signal while the fitting flux overfit the signal.} \revise{But the \name\ flux is distorted a little around the box model. 
-  And there is more distortion with a strong signal.
-  \emph{Right:} shows the signal depth measured in \name\ and fitting flux relative to the true depth with different box model depth.
-\name\ can consistently preserve more signal than the "ordinary fitting".}
+In the top panel, SAP flux is plotted in black dots, the \name\ prediction is in thin red line, ``ordinary fitting'' is in bold grey line.}
+  In the bottom panel, red points and grey cross represent the \name\ flux and the ``ordinary fitting'' flux, while the signal amplitude is indicated by the horizontal line. 
+  \name\ preserves the original signal amplitude while the ``ordinary fitting'' overfits the signal. \revise{But the \name\ flux is distorted a little around the edge of the box model.
+  \emph{Middle:} The same plot for light curve with 3000 ppm signal injected. There is more distortion with a stronger signal.
+  \emph{Right:} The relative signal amplitude measured in \name\ and ``ordinary fitting'' flux is plotted as a function of the injected signal amplitude.
+The \name\ can consistently preserve more signal than the ``ordinary fitting".}}
 \end{figure}
@@
 The results illustrate that for these quiet stars our approach removes 
-\remove{a major part}\revise{the majority} of the variability present in the PDC light-curves, while preserving the transit signals. 
+\remove{a major part}\revise{the majority} of the variability present in the PDC light curves, while preserving the transit signals. 
 To provide a quantitative comparison, we ran \name\ on 1000 stars from the whole Kepler input catalog 
@@
 \hfill
+\includegraphics[width=0.32\textwidth]{f5b}
+\hfill
+\includegraphics[width=0.32\textwidth]{f5c}
+
+\includegraphics[width=0.32\textwidth]{f5d}
+\hfill
 \includegraphics[width=0.32\textwidth]{f5e}
@@
 \includegraphics[width=0.32\textwidth]{f5i}
-
-\includegraphics[width=0.32\textwidth]{f5j}
-\hfill
-\includegraphics[width=0.32\textwidth]{f5k}
-\hfill
-\includegraphics[width=0.32\textwidth]{f5l}
 \end{center}
@@
   Corrected fluxes using \name, for 9 example stars, spanning the \Kepler\ magnitude (brightness) range \remove{encountered}. 
-  In first column plots, we consider bright stars with magnitude from 9 to 10.5, second column are stars with magnitude from 11 to 12.5, and the third column are faint stars with magnitude above 13. 
+  In first column plots, we consider brighs stars with magnitude from 9 to 10.5, second column are stars with magnitude from 11 to 12.5, and the third column are faint stars with magnitude above 13. 
   In the first row, we present some quiet stars. 
@@
   \label{cdpp} 
-  Comparison of the \revise{\name\ } \remove{proposed method (\name) }to the \Kepler\ Pre-search Data Conditioning (PDC) method 
-    in terms of Combined Differential Photometric Precision (CDPP).
-  \revise{Row 1-4 shows the CDPP estimation throgh quarter 5 to quarter 8. In each row:} 
-  \emph{Left} \remove{Plot (a)} shows our performance (red) vs.\ the PDC performance (black) in a scatter plot, as a function of star magnitude (note that larger magnitude means fainter stars, and smaller values of CDPP indicate higher quality as measured by CDPP.)
+  Comparison of the \revise{\name\ }\remove{proposed method (\name) }to the \Kepler\ Presearch Data Conditioning (PDC) method in terms of Combined Differential Photometric Precision (CDPP, calculated with equations 6-8 of section 3.3 in \citealt{cdpp1}).
+  \revise{Row 1-4 shows the CDPP estimation of 900 stars (500 chosen randomly from the whole \Kepler\ input catalog, and 500 random G-type sun-like stars, the 100 most variable stars are removed) throgh quarter 5 to quarter 8.
+In each row:}
+  \emph{Left} \remove{Plot (a)} shows our performance (red) vs.\ the PDC performance (black) in a scatter plot, as a function of star magnitude (note that larger magnitude means fainter stars, and smaller values of CDPP indicate higher quality.)
   \emph{Middle} bins the same dataset and shows box plots within each bin, indicating median, top quartile and bottom quartile. 
@@
   Note that the red histogram has more mass towards the left, i.e., smaller values of CDPP, 
-    indicating that our method \remove{overall outperforms PDC, the Kepler ``gold standard.'' } \revise{returns the light curves with a lower noise level.}
+    indicating that our method \remove{overall outperforms PDC, the Kepler ``gold standard.'' } \revise{returns the light curves with a lower overall noise level.}
 }
@@
 In the second panel, the signal strength measured from the median filtered light curve is plotted as a function of the filter window size (blue dots), while the red dash line indicates the signal strength retrieved from the \name\ light curve.
-The grey dash line shows the injected signal strength.
+The black solid line shows the injected signal strength.
 Smaller window size reduces the noise level (CDPP) of the median filtered light curve, but distorts the signal more.
@@
 We have presented a simple yet highly effective method---the \name---that works at pixel-level \revise{to remove spacecraft and stellar variability on time-domain imaging.
-It is} based on the causal structure of the \Kepler\ data \remove{to}\revise{; It} calibrates the \Kepler\ light-curves \remove{, which is intended to search exoplanets.} \revise{for the purpose of exoplanet search.}
-In \revise{the} \name, systematics and stellar variabilities are removed by either fitting with other stars' light-curves or auto-regressive components, while transit signals \remove{can still be perfectly preserved} \revise{are preserved with a} \remove{by} train-and-test framework \revise{to control model freedom}.
-Low variable clean light-curves can be produced by \name,  
+It is} based on the causal structure of the \Kepler\ data \remove{to}\revise{; It} calibrates the \Kepler\ light curves \remove{, which is intended to search exoplanets.} \revise{for the purpose of exoplanet search.}
+In \revise{the} \name, systematics and stellar variabilities are removed by either fitting with other stars' light curves or auto-regressive components, while transit signals \remove{can still be perfectly preserved} \revise{are preserved with a} \remove{by} train-and-test framework \revise{to control model freedom}.
+Low variable clean light curves can be produced by \name,  
   which is ideal for \remove{transit} planet search. 
@@
 
-Apart from the \name, \remove{as mentioned in the beginning of the paper,}
-  there exist several other methods that are effective in de-trending \remove{the} light curves.
+Apart from the \name, \remove{as mentioned in the beginning of the paper,}there exist several other methods that are effective in de-trending \remove{the} light curves.
 Methods like \revise{the} median filter are quite successful in smoothing \remove{all the} unwanted features 
@@
 
-As mentioned earlier in this paper, 
-  \name\ is very similar to PDC, 
-  in that they both make use of the correlation between light-curves,
-  which is assumed to be caused by the spacecraft effects (or systematics).
+As mentioned earlier in this paper, \name\ is very similar to PDC, in that they both make use of the correlation between lightcurves, which is assumed to be caused by the spacecraft effects (or systematics).
 \remove{However, in section 4, we show that \name\ performs better than PDC, in that it has a overall low noise level (CDPP).
@@
 variations in the centroids and point-spread function from spacecraft pointing, roll, and temperature.
-The other reason is that, in \revise{the} PDC,  only \revise{the} leading eight principal components of some relative light-curves are used.
+The other reason is that, in \revise{the} PDC,  only \revise{the} leading eight principal components of some relative light curves are used.
 Although restricting the number of components can prevent over-fitting, \remove{we think with this limited number of components,} it is insufficient to capture all the variabilities in the light curves.
-In \revise{the} \name\, hundreds of stars' light-curves (or thousands of pixels) are used to capture relatively complete information of the variability, while strong regularization and train-and-test framework are applied to prevent over-fitting.
+In \revise{the} \name\, hundreds of stars' light curves (or thousands of pixels) are used to capture relatively complete information of the variability, while strong regularization and train-and-test framework are applied to prevent over-fitting.
 Although we present the comparison between \name\ and PDC, 
@@
 However, in fact, we can not preserve the stellar variability just by turning off the auto-regressive components. 
-One possible reason can be that, since our model is so flexible (thousands of parameters), 
-  in principle it can fit any functions. 
-In this sense, 
-  we should run cross-validation with the auto-regressive components turned off 
-  and to find out how many pixels from other stars we need to just remove systematics 
-  while preserve stellar variability, 
-  but in fact we do not have a good criterion to check how well we preserve stellar variability in cross-validation 
-  because we do not have enough knowledge of the true stellar variability. 
-Thus for the time being, we just focus on producing well-calibrated light-curves for searching exoplanets, 
-  but in long term, we are looking forward to find a method to preserve the stellar variability.
+\remove{One possible reason can be that, since our model is so flexible (thousands of parameters), in principle it can fit any functions. 
+In this sense, we should run cross-validation with the auto-regressive components turned off and to find out how many pixels from other stars we need to just remove systematics while preserve stellar variability, but in fact we do not have a good criterion to check how well we preserve stellar variability in cross-validation because we do not have enough knowledge of the true stellar variability.}
+\revise{The reason is that the light curve is always overfitted to some extent, though in the \name, both strong regularization and train-and-test framework are performed to prevent overfitting.
+Train-and-test framework is perfect for preventing overfiting within time-scale $\Delta t$ (size of the excluded region) , but it can do nothing for time-scale larger than $\Delta t$.
+Since there are a lot of long-term trends in the stellar variability, the \name\ must overfit these ``stellar signals'' longer than $\Delta t$.}
+Thus for the time being, we just focus on producing well-calibrated light curves for searching exoplanets, but in long term, we are looking forward to find a method to preserve the stellar variability.
 
@@
 That is,  instead of only modelling the systematics and then subtracting \remove{it}\revise{them} from the raw data to produce \remove{some }de-trended light curves, a comprehensive model for all components in the data (systematics, stellar variabilities and transits)  can be made.
-In this kind of model, there is no need for \revise{the} train-and-test framework, since all transit signals have already been modelled and no de-trended light-curve will be produced.
+In this kind of model, there is no need for \revise{the} train-and-test framework, since all transit signals have already been modelled and no de-trended light curve will be produced.
 Planets will be found directly in the model itself.
